\begin{multicols}{2}
	My soul is athrist for God, yea, even for the \textbf{liv}ing God * when shall I come to appear before the \textbf{pres}ence of God?
	
	My tears have been my bread \textbf{day} and night * while they say unto me every day, \textbf{Where} now is thy God?
	
	Now when I think thereupon, I pour out my heart \textbf{by} myself * for I went with the multitude, and brought them forth in\textbf{to} the house of God.
	
	With the voice of praise and thanks\textbf{giv}ing * among those who \textbf{keep} the holy day.
	
	Why art thou so full of heaviness, \textbf{O} my soul * and why art thou so disquiet\textbf{ed} within me?
	
	Put thy \textbf{trust} in God * for I will yet give him thanks for the help \textbf{of} his countenance.
	
	My God, my soul is vexed with\textbf{in} me * therefore will I remember thee concerning the land of Jordan, and the \textbf{hill} of Hermon.
	
	One deep calleth another, at the noise of the \textbf{flood} gates * all thy waves and storms \textbf{are} gone over me.
	
	The Lord hath granted his loving-kindness in the \textbf{day}time * and in the night season did I sing of him, and made my prayer unto \textbf{the} God of my life.
	
	I will say unto the God of my strength, Why hast thou for\textbf{got}ten me? * why go I thus heavily, while the ene\textbf{my} oppresseth me?
	
	My bones are smitten asunder as \textbf{with} a sword * while mine enemies who trouble me \textbf{cast} me in their teeth.
	
	While they say daily \textbf{un}to me * \textbf{Where} is now thy God?
	
	Why art thou so vexed, \textbf{O} my soul? * and why art thou so disquiet\textbf{ed} within me?
	
	O put thy trust in God, for I will yet \textbf{praise} him * who is the salvation of my coun\textbf{te}nance, and my God.
\end{multicols}