Like as the hart desireth the water brooks * so longeth my soul after thee, O God.

My soul is athrist for God, yea, even for the living God * when shall I come to appear before the presence of God?

My tears have been my bread day and night * while they say unto me every day, Where now is thy God?

Now when I think thereupon, I pour out my heart by myself * for I went with the multitude, and brought them forth into the house of God.

With the voice of praise and thanksgiving * among those who keep the holy day.

Why art thou so full of heaviness, O my soul * and why art thou so disquieted within me?

Put thy trust in God * for I will yet give him thanks for the help of his countenance.

My God, my soul is vexed within me * therefore will I remember thee concerning the land of Jordan, and the hill of Hermon.

One deep calleth another, at the noise of the flood gates * all thy waves and storms are gone over me.

The Lord hath granted his loving-kindness in the daytime * and in the night season did I sing of him, and made my prayer unto the God of my life.

I will say unto the God of my strength, Why hast thou forgotten me? * why go I thus heavily, while the enemy oppresseth me?

My bones are smitten asunder as with a sword * while mine enemies who trouble me cast me in their teeth.

While they day daily unto me * Where is now thy God?

Why art thou so vexed, O my soul? * and why art thou so disquieted within me?

O put thy trust in God, for I will yet praise him * who is the salvation of my countenance, and my God.