\documentclass[17pt,twoside]{extarticle}
\usepackage{moresize}
\usepackage{fontspec}
\usepackage{aeguill}
\usepackage{titlesec}
\usepackage[maxlevel=3]{csquotes}
\usepackage{lettrine}
\usepackage{xifthen}
\usepackage{yfonts}
\usepackage{parskip}
\usepackage[dvipsnames]{xcolor}
\usepackage{fancyhdr}
\usepackage{hanging}
\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage[twoside]{geometry}
\usepackage{multicol}
\usepackage{paracol}
\usepackage[latin,english]{babel}

\setlength{\columnseprule}{0.025pt}
\setlength{\columnsep}{1.25em}
\setlength{\topskip}{7pt}

\makeatletter
\patchcmd{\pcol@buildcolseprule}%
{\hrule\@height\@tempdima\@width\columnseprule}%
{\hrule\@height\dimexpr\@tempdima-0.5ex\@width\columnseprule\@depth-1pt}{}{}
\makeatother

\gredefsizedsymbol{GreCross}{greextra}{Cross}
\gredefsizedsymbol{GreDagger}{greextra}{Dagger}
\gredefsizedsymbol{GreCrossAlt}{greextra}{Cross.alt}
\gredefsizedsymbol{GreStarHeight}{greextra}{StarHeight}
\gredefsizedsymbol{greABar}{greextra}{ABar}
\gredefsizedsymbol{greVBar}{greextra}{VBar}
\gredefsizedsymbol{greRBar}{greextra}{RBar}

\gresetspecial{r}{\textcolor{red}{\Rbar{}.}}
\gresetspecial{v}{\textcolor{red}{\Vbar{}.}}
\gresetspecial{+}{\textcolor{red}{\GreCross{17}}}
\gresetspecial{1}{\textcolor{red}{\GreDagger{17}}}
\gresetspecial{2}{\textcolor{red}{\GreCrossAlt{17}}}
\gresetspecial{*}{\textcolor{red}{\GreStarHeight{17}}}

% legacy support
\gresetspecial{R/}{\textcolor{red}{\Rbar{}}}
\gresetspecial{V/}{\textcolor{red}{\Vbar{}}}

\grechangestaffsize{30}
%\grechangedim{abovelinestextheight}{0.25cm}{fixed}
%\grechangedim{spacebeneathtext}{0.5cm}{fixed}
\grechangedim{annotationseparation}{0.25cm}{fixed}

%%% FORMATTING %%%
\newcommand{\greformat}[1]{\textcolor{red}{\textbf{#1}}}
\newcommand{\skiplines}[1]{\vspace*{#1\baselineskip}}
\newcommand{\scoreskip}[0]{\skiplines{0}}
\newcommand{\instruct}[1]{\textcolor{red}{\textit{#1}}}
\newcommand{\greant}[1]{\greannotation{#1. \color{red}\textbf{Ant.}}}
\newcommand{\breakhere}[0]{}

\newcommand{\whiteribbon}[0]{\textcolor{black}{\textbf{white ribbon}} }%
\newcommand{\greenribbon}[0]{\textcolor{ForestGreen}{\textbf{green ribbon}} }%
\newcommand{\redribbon}[0]{\textcolor{red}{\textbf{red ribbon}} }%
\newcommand{\blueribbon}[0]{\textcolor{blue}{\textbf{blue ribbon}} }%

\let\grescore\gregorioscore
\renewcommand{\gregorioscore}[1]{\scoreskip\grescore{#1}}

\let\gresnip\gabcsnippet
\renewcommand{\gabcsnippet}[1]{\gresetinitiallines{1}\greannotation{\greformat{Chap.}}\greannotation{\greformat{Dir.}}\gresnip{#1}}

%%% DIVISIONS %%%
\makeatletter
\newcommand{\vepart}[1]{%
	\cleardoublepage%
	\vspace*{\fill}
	\centerline{\huge \selectfont \textbf{#1}}%
	\vspace*{\fill}
}%
\makeatother

\makeatletter
\newcommand{\vechapter}[1]{%
	\cleardoublepage
	%\centerline{\Large \selectfont \textbf{#1}}%
	\begin{center}
		\Large \selectfont \textbf{#1}
	\end{center}
	%\skiplines{0.5}
}%
\makeatother

\makeatletter
\newcommand{\vesection}[1]{%
	%\skiplines{0.5}%
	\centerline{\large \selectfont \textbf{#1}}%
	%\skiplines{0.5}%
}%
\makeatother

\makeatletter
\newcommand{\veheading}[1]{%
	\skiplines{0.5}%
	\centerline{\selectfont \textit{#1}}%
	%\skiplines{-0.5}
}%
\makeatother

\makeatletter
\newcommand{\hyheading}[1]{%
	%\skiplines{0.5}
	\veheading{#1}
	%\skiplines{-0.5}
}%
\makeatother

\makeatletter
\newcommand{\vecomment}[1]{%
	%\skiplines{0.5}
	\hfill{\small\selectfont \textit{#1}.}%
	%\skiplines{-0.5}
}%
\makeatother

\begin{document}
	\newgeometry{margin=0pt}
	\begin{titlepage}
		\vspace*{\fill}
		\centerline{\Huge\selectfont LECTIONARY}
		
		\vspace*{0.5\baselineskip}
		
		\centerline{\large\selectfont OF THE}
		
		\vspace*{0.5\baselineskip}
		
		\centerline{\Large\selectfont HOLY ROMAN CHURCH}
		
		\vspace*{\fill}
		
		\centerline{\LARGE\selectfont VOLUME I}
		
		\vspace*{1\baselineskip}
		
		\centerline{\large\selectfont I WINTER}
		
		\vspace*{\fill}
		
		\centerline{\normalsize\selectfont From the First Sunday in Advent until the Eve of the Epiphany}
		
		\vspace*{0.5\baselineskip}
		
		\centerline{\normalsize\selectfont November 27 until January 5}
		
		\vspace*{\fill}
	\end{titlepage}
	
	\newgeometry{top=0.5in,bottom=0.5in,inner=0.5in,outer=0.5in,includefoot}
	
	\pagenumbering{arabic}
	\gresetinitiallines{0}
	
	\vechapter{Brief Notes on Ceremony}
	
	When the time for the chapter is appointed, the lector should process before the altar, and while facing it, proclaim the lesson. He returns to his place once the people have acclaimed \enquote{Thanks be to God}, unless there is a responsory appointed. In which case, the lector remains standing before the altar and intones the responsory until the asterisk. He also sings the verse standing before the altar. Once the responsory is completed, he returns to his place.
	
	If no other lesson is appointed in the following, this is sung during Advent:
	
	\vecomment{Jeremiah xxiii, 6}
	
	\gabcsnippet{(c3) In(h) his(h) days(h) shall(h) Ju(h)dah(h) be(h) saved,(h) and(h) Is(h)ra(h)el(h) shall(h) dwell(h) safe(h)ly:(f.) (;) and(h) this(h) is(h) his(h) name(h) where(h)by(h) he(h) shall(h) be(h) called:(f.) (;) the(h) Lord(h) our(h) right(h)eous(h)ness(d.)}
	
	But if desirable, the chapter of Sunday's second vespers may be used in its place, and the corresponding responsory should be omitted on feria.
	
	\vepart{Temporale}
	
	\vechapter{First Week in Advent}
	
	\veheading{Sunday at First Vespers}
	
	\vecomment{Isaiah ii, 2}
	
	\gabcsnippet{(c3) It(h) shall(h) come(h) to(h) pass(h) in(h) the(h) last(h) days,(h) that(h) the(h) moun(h)tain(h) of(h) the(h) Lord's(h) house(h) shall(h) be(h) es(h)tab(h)lished(h) in(h) the(h) top(h) of(h) the(h) moun(h)tains,(h) and(h) shall(h) be(h) ex(h)alt(h)ed(h) a(h)bove(h) the(h) hills;(f.) (;) and(h) all(h) na(h)tions(h) shall(h) flow(h) un(h)to(d) it.(d.)}
	
	\gresetinitiallines{1}
	\greannotation{\greformat{Resp.}}
	\greannotation{\greformat{viii.}}
	\vecomment{Ecce dies veniunt}
	
	\gregorioscore{resp/ecce_dies_veniunt.gabc}
	
	\clearpage
	
	\veheading{Sunday at Second Vespers}
	
	\vecomment{Romans xiii, 11}
	
	\gabcsnippet{(c3) Now(h) it(h) is(h) high(h) time(h) to(h) a(h)wake(h) out(h) of(h) sleep:(f.) (;) for(h) now(h) is(h) our(h) sal(h)va(h)tion(h) near(h)er(h) than(h) when(h) we(h) be(h)lieved.(d.)}
	
	\vecomment{Tu exurgens Domine}
	
	\greannotation{\greformat{Resp.}}
	\greannotation{\greformat{iv.}}
	\gregorioscore{resp/tu_exurgens_domine.gabc}
	
	\vechapter{Second Week in Advent}
	
	\veheading{Sunday at First Vespers}
	
	\vecomment{Isaiah iv, 2}
	
	\gabcsnippet{(c3) In(h) that(h) day(h) shall(h) the(h) branch(h) of(h) the(h) Lord(h) be(h) beau(h)ti(h)ful(h) and(h) glo(h)ri(h)ous,(h) and(h) the(h) fruit(h) of(h) the(h) earth(h) shall(h) be(h) ex(h)cel(h)lent(h) and(h) come(h)ly(h) for(h) them(h) that(h) are(h) es(h)caped(h) of(h) Is(h)ra(h)el.(d.)}
	
	\vecomment{Docebit nos Dominus}
	
	\greannotation{\greformat{Resp.}}
	\greannotation{\greformat{ii.}}
	\gregorioscore{resp/docebit_nos_domine.gabc}
	
	\clearpage
	
	\veheading{Sunday at Second Vespers}
		
	\vecomment{Romans xv, 4}
	
	\gabcsnippet{(c3) What(h)ev(h)er(h) things(h) were(h) writ(h)ten(h) a(h)fore(h)time(h) were(h) writ(h)ten(h) for(h) our(h) learn(h)ing:(f.) (;) that(h) we(h) through(h) pa(h)tience(h) and(h) com(h)fort(h) of(h) the(h) scrip(h)tures(h) might(h) have(h) hope.(d.)}
	
	\vecomment{Tu exurgens Domine}
	
	\greannotation{\greformat{Resp.}}
	\greannotation{\greformat{iv.}}
	
	\gregorioscore{resp/tu_exurgens_domine.gabc}
	
	
	\vechapter{Third Week in Advent}
	
	\veheading{Sunday at First Vespers}
	
	\vecomment{Genesis xlix, 10}
	
	\gabcsnippet{(c3) The(h) scep(h)ter(h) shall(h) not(h) de(h)part(h) from(h) Ju(h)dah,(h) nor(h) a(h) law(h)giv(h)er(h) from(h) be(h)tween(h) his(h) feet,(h) un(h)til(h) Shi(h)loh(h) come;(f.) (;) and(h) un(h)to(h) him(h) shall(h) the(h) gath(h)er(h)ing(h) of(h) the(h) peo(h)ple(h) be.(d.)}
	
	\greannotation{\greformat{Resp.}}
	\greannotation{\greformat{vi.}}
	\vecomment{Qui venturus est}
	
	\gregorioscore{resp/qui_venturus_est.gabc}
	
	\clearpage
	
	\veheading{Sunday at Second Vespers}
	
	\vecomment{1 Corinthians iv, 1-2}
	
	\gabcsnippet{(c3) Let(h) a(h) man(h) so(h) ac(h)count(h) of(h) us,(h) as(h) of(h) the(h) min(h)is(h)ters(h) of(h) Christ,(h) and(h) stew(h)ards(h) of(h) the(h) mys(h)ter(h)ies(h) of(h) God:(f.) (;) more(h)o(h)ver,(h) it(h) is(h) re(h)quired(h) in(h) stew(h)ards(h) that(h) a(h) man(h) be(h) found(h) faith(h)ful.(d.)}
	
	\instruct{Sing this responsory if the date is December 17 or later:}
	
	\greannotation{\greformat{Resp.}}
	\greannotation{\greformat{ii.}}
	\vecomment{Festina ne taraveris}
	
	\gregorioscore{resp/festina_ne_taraveris.gabc}
	
	\instruct{If the date is earlier:}
	
	\greannotation{\greformat{Resp.}}
	\greannotation{\greformat{iv.}}
	\vecomment{Tu exurgens Domine}	
	
	\gregorioscore{resp/tu_exurgens_domine.gabc}
	
	\vechapter{Fourth Week in Advent}
	
	\veheading{Sunday at First Vespers}
	
	\vecomment{Isaiah xxviii, 16}
	
	\gabcsnippet{(c3) Be(h)hold,(h) I(h) lay(h) in(h) Zi(h)on(h) for(h) a(h) foun(h)da(h)tion(h) a(h) stone,(h) a(h) tried(h) stone,(h) a(h) pre(h)cious(h) cor(h)ner(h)stone,(h) a(h) sure(h) foun(h)da(h)tion:(f.) (;) and(h) who(h)so(h)ev(h)er(h) believeth(h) on(h) him(h) shall(h) not(h) be(h) a(h)shamed.(d.)}
	
	\vecomment{Non auferetur sceptrum}
	
	\greannotation{\greformat{Resp.}}
	\greannotation{\greformat{ii.}}
	\gregorioscore{resp/non_auferetur_sceptrum.gabc}
	
	\clearpage\veheading{Sunday at Second Vespers}
	
	\vecomment{Philippians iv, 4-5}
	
	\gabcsnippet{(c3) Re(h)joice(h) in(h) the(h) Lord(h) al(h)ways:(f.) (;) and(h) a(h)gain(h) I(h) say,(h) Re(h)joice.(f.) (:) Let(h) your(h) mod(h)er(h)a(h)tion(h) be(h) known(h) un(h)to(h) all(h) men.(f.) (:) The(h) Lord(h) is(h) at(h) hand.(d.)}
	
	\greannotation{\greformat{Resp.}}
	\greannotation{\greformat{ii.}}
	\vecomment{Festina ne taraveris}
	
	\gregorioscore{resp/festina_ne_taraveris.gabc}
	
	\vechapter{Nativity of the Lord}
	
	\veheading{At First Vespers}
	
	\vecomment{Isaiah ix, 2}
	
	\gabcsnippet{(c3) The(h) peo(h)ple(h) that(h) walked(h) in(h) dark(h)ness(h) have(h) seen(h) a(h) great(f) light:(fh..) (,) they(g) that(g) dwell(g) in(g) the(g) land(g) of(g) the(g) shad(g)ow(g) of(g) death,(g) up(g)on(g) them(g) hath(g) the(g) light(g) shined.(gh..)}
	
	\vecomment{Judea et Hierusalem}
	
	\greannotation{\greformat{Resp.}}
	\greannotation{\greformat{iv.}}
	
	\gregorioscore{resp/judea_et_hierusalem.gabc}
	
	
	\clearpage
	
	\veheading{At Second Vespers}
	
	\vecomment{Hebrews i, 1-2}
	\gabcsnippet{(c3) God,(g) who(g) at(g) sun(g)dry(g) times(g) and(g) in(g) di(g)verse(g) man(g)ners(g) spake(g) in(g) time(g) past(g) un(g)to(g) the(g) fa(g)thers(g) by(g) the(g) proph(g)ets,(g) hath(g) in(g) these(g) last(g) days(g) spo(g)ken(g) un(g)to(g) us(g) by(g) his(g) Son.(gh..)}
	
	\vecomment{Verbum caro factum}
	
	\greannotation{\greformat{Resp.}}
	\greannotation{\greformat{viii.}}
	
	\gregorioscore{resp/verbum_caro_factum.gabc}
	
	
	
	\vechapter{Saint Stephen, Protomartyr}
	
	\vecomment{Acts vi, 8}
	
	\gabcsnippet{(c3) Ste(h)phen,(h) full(h) of(h) faith(h) and(h) pow(h)er,(h) did(h) great(h) won(h)ders(h) and(h) mir(h)a(h)cles(h) a(h)mong(h) the(h) peo(h)ple.(d.)}
	
	\vecomment{Impetum fecerunt}
	
	\greannotation{\greformat{Resp.}}
	\greannotation{\greformat{i.}}
	
	\gregorioscore{resp/impetum_fecerunt.gabc}
	
	\vechapter{Saint John, Apostle and Evangelist}
	
	\vecomment{Ecclesiasticus xv, 1-2}
	
	\gabcsnippet{(c3) He(h) that(h) feareth(h) the(h) Lord(h) will(h) do(h) good,(h) and(h) he(h) that(h) hath(h) the(h) knowl(h)edge(h) of(h) the(h) law(h) shall(h) ob(h)tain(f) wis(fh)dom;(h.) (,) and(g) as(g) an(g) hon(g)ored(g) moth(g)er(g) shall(g) she(g) meet(g) him.(gh..)}
	
	\vecomment{Iste est Johannes}
	
	\greannotation{\greformat{Resp.}}
	\greannotation{\greformat{i.}}
	
	\gregorioscore{resp/iste_est_johannes.gabc}
	
	\vechapter{Holy Innocents}
	\instruct{A responsry is appointed in the antiphonary.}
	
	\vecomment{Revelation xiv, 1}
	
	\gabcsnippet{(c3) I(g) looked,(g) and(g) lo,(g) a(g) Lamb(g) stood(g) on(g) the(g) mount(g) Zi(g)on,(g) and(g) with(g) him(g) a(g) hun(g)dred(g) for(g)ty(g) and(g) four(g) thou(g)sand,(g) hav(g)ing(g) his(g) Father's(g) name(g) writ(g)ten(g) in(g) their(g) fore(gh)heads.(h.)}
	
	
	
	\vechapter{Saint Thomas Becket, Martyr}
	\instruct{A responsory is appointed in the antiphonary.}
	
	\vecomment{Hebrews v, 1}
	
	\gabcsnippet{(c3) Eve(g)ry(g) high(g) priest(g) tak(g)en(g) from(g) a(g)mong(g) men(g) is(g) or(g)dained(g) for(g) me(g) in(g) things(g) per(g)tain(g)ing(g) to(g) God,(g) that(g) he(g) may(g) of(g)fer(g) both(g) gifts(g) and(g) sac(g)ri(g)fices(g) for(g) sin.(gh..)}
	
	
	
	\vechapter{Days within the Octave of the Nativity}
	
	\vecomment{Galatians iv, 1}
	
	\gabcsnippet{(c3) The(h) heir,(h) as(h) long(h) as(h) he(h) is(h) a(h) child,(h) differeth(h) noth(h)ing(h) from(h) a(h) ser(h)vant,(h) though(h) he(h) be(h) lord(h) of(f) all.(fh..) (:) But(g) is(g) un(g)der(g) tu(g)tors(g) and(g) gov(g)er(g)nors(g) un(g)til(g) the(g) time(g) ap(g)pointed(g) of(g) the(g) fa(gh)ther.(h.)}
	
	
	
	\vechapter{Saint Sylvester, Pope and Confessor}
	
	\instruct{A responsory is appointed in the antiphonary.}
	
	\vecomment{Ecclesiasticus xliv, 16-17}
	
	\gabcsnippet{(c3) Be(h)hold(h) a(h) great(h) priest(h) who(h) in(h) his(h) time(h) pleased(h) God(h) and(h) was(h) found(f) just;(fh..) (,) and(g) in(g) the(g) time(g) of(g) wrath(g) he(g) was(g) made(g) a(g) reconciliation.(gh..)}
	
	
	
	\vechapter{Circumcision of the Lord}
	
	\instruct{The same chapter is read at first and second vespers, but a different responsory is appointed in the antiphonary for each.}
	
	\vecomment{Titus ii, 11-12}
	
	\gabcsnippet{(c3) The(h) grace(h) of(h) God(h) that(h) bringeth(h) sal(h)va(h)tion(h) hath(h) ap(h)peared(h) to(h) all(h) men,(h) teach(h)ing(h) us(h) that,(h) de(h)ny(h)ing(h) un(h)god(h)li(h)ness(h) and(h) world(h)ly(h) lust,(h) we(h) should(h) live(h) so(h)ber(h)ly,(h) right(h)eous(h)ly,(h) and(h) god(h)ly,(h) in(h) this(h) pre(h)sent(h) world.(d.)}
	
	\instruct{On the following days until the eve of the Epiphany are again the services of Saint Stephen, Saint John, and the Holy Innocents, but any responsories are not sung.}
	
	
	
	\vepart{Sanctorale}
	
	\vechapter{Saint Andrew, Apostle}
	
	\instruct{If falling within Advent, no eve is said.}
	
	\instruct{The same chapter is read vespers on the eve and on the day, but a different responsory is appointed in the antiphonary for each.}
	
	\vecomment{Romans x, 10}
	
	\gabcsnippet{(c3) With(h) the(h) heart(h) man(h) believeth(h) un(h)to(h) right(h)eous(h)ness:(f.) (;) and(h) with(h) the(h) mouth(h) con(h)fes(h)sion(h) is(h) made(h) un(h)to(h) sal(h)va(h)tion.(f.) (:) For(h) the(h) scrip(h)ture(h) saith,(h) Who(h)so(h)ev(h)er(h) believeth(h) in(h) him(h) shall(h) not(h) be(h) a(h)shamed.(d.)}
	
	
	
	\vechapter{Saint Nicholas, Bishop and Confessor}
	
	\instruct{A responsory is appointed in the antiphonary.}
	
	\vecomment{Ecclesiasticus xliv, 16-17}
	
	\gabcsnippet{(c3) Be(h)hold(h) a(h) great(h) priest(h) who(h) in(h) his(h) time(h) pleased(h) God(h) and(h) was(h) found(f) just;(fh..) (,) and(g) in(g) the(g) time(g) of(g) wrath(g) he(g) was(g) made(g) a(g) reconciliation.(gh..)}
	

	
	\vechapter{Immaculate Conception of Blessed Virgin Mary}
	
	\instruct{The same chapter is read at first and second vespers, but a different responsory is appointed in the antiphonary for each.}
	
	\vecomment{Ecclesiasticus xxiv, 17}
	
	\gabcsnippet{(c3) As(h) the(h) vine(h) I(h) brought(h) forth(h) pleas(h)ant(h) sa(h)vor,(h) and(h) my(h) flow(h)ers(h) are(h) the(h) fruit(h) of(h) hon(h)or(h) and(h) rich(h)es.(d.)}
	
	
	
	\vechapter{Saint Lucy, Virgin and Martyr}
	
	\instruct{The same chapter is read at first and second vespers, but a different responsory is appointed in the antiphonary for each.}
	
	\vecomment{Ecclesiasticus li, 13}
	
	\gabcsnippet{(c3) O(h) Lord(h) my(h) God,(h) thou(h) hast(h) ex(h)alt(h)ed(h) my(h) dwell(h)ing(h) place(h) up(h)on(h) the(h) earth,(h) and(h) I(h) have(h) prayed(h) for(h) de(h)liv(h)er(h)ance(h) from(h) death.(d.)}
	
	
	
	\vechapter{Saint Thomas, Apostle}
	
	\instruct{The same chapter is read at first and second vespers, but a different responsory is appointed in the antiphonary for each.}
		
	\vecomment{Ephesians ii, 19}
	
	\gabcsnippet{(c3) Now(h) ye(h) are(h) no(h) more(h) stran(h)gers(h) and(h) for(h)eign(h)ers,(h) but(h) fel(h)low-(h)cit(h)i(h)zens(h) with(h) the(h) saints,(h) of(h) the(h) house(h)hold(h) of(h) God;(f.) (;) and(h) are(h) built(h) up(h)on(h) the(h) foun(h)da(h)tion(h) of(h) the(h) a(h)pos(h)tles(h) and(h) proph(h)ets.(d.)
	}
\end{document}