\begin{multicols}{2}
	Which faith except everyone do keep whole and unde\textbf{fi}led * without doubt he shall perish \textbf{ev}er\textbf{last}ingly.
	
	And the catholic \textbf{faith} is this * that we worship one God in Trinity, and Trini\textbf{ty} in \textbf{U}nity.
	
	Neither confounding the \textbf{Per}sons * nor di\textbf{vi}ding the \textbf{Sub}stance.
	
	For there is one Person of the Father, another \textbf{of} the Son * and another of the \textbf{Ho}ly \textbf{Spir}it.
	
	But the Godhead of the Father, of the Son, and of the Holy Spirit, is \textbf{all} one * the Glory equal, the Majesty \textbf{co}-e\textbf{ter}nal.
	
	Such the Father is, such \textbf{is} the Son * and such is the \textbf{Ho}ly \textbf{Spir}it.
	
	The Father uncreate, the Son \textbf{un}create * and the Holy \textbf{Spir}it \textbf{un}create.
	
	The Father incomprehensible, the Son incompre\textbf{hen}sible * and the Holy Spirit \textbf{in}compre\textbf{hen}sible.
	
	The Father eternal, the Son e\textbf{ter}nal * and the Holy \textbf{Spir}it e\textbf{ter}nal.
	
	And yet they are not three e\textbf{ter}nals * but \textbf{one} e\textbf{ter}nal.
	
	As also there are not three incomprehensibles, nor three uncre\textbf{a}ted * but one uncreated, and one \textbf{in}compre\textbf{hen}sible.
	
	So likewise the Father is Almighty, the Son Al\textbf{migh}ty * and the Holy \textbf{Spir}it Al\textbf{migh}ty.
	
	And yet there are not three Al\textbf{migh}ties * but \textbf{one} Al\textbf{migh}ty.
	
	So the Father is God, the \textbf{Son} is God * and the Holy \textbf{Spir}it \textbf{is} God.
	
	And yet they are not \textbf{three} Gods * \textbf{---} but \textbf{one} God.
	
	So likewise the Father is Lord, the \textbf{Son} Lord * and the \textbf{Ho}ly \textbf{Spir}it Lord.
	
	And yet there are not \textbf{three} Lords * \textbf{---} but \textbf{one} Lord.
	
	For like as we are compelled by the \textbf{Chris}tian truth * to acknowledge every Person by himself to \textbf{be} both \textbf{God} and Lord.
	
	So are we forbidden by the catholic re\textbf{li}gion * to say There be \textbf{three} Gods or \textbf{three} Lords. 
	
	The Father is \textbf{made} of none * neither created, \textbf{nor} be\textbf{got}ten.
	
	The Son is of the Father \textbf{a}lone * not made, nor created, \textbf{but} be\textbf{got}ten.
	
	The Holy Spirit is of the Father and \textbf{of} the Son * neither made, nor created, nor begotten, \textbf{but} pro\textbf{cee}ding.
	
	So there is one Father, not three Fathers, one Son, not \textbf{three} Sons * one Holy Spirit, not three \textbf{Ho}ly \textbf{Spir}its.
	
	And in this Trinity none is afore or after the \textbf{o}thers * none is greater, or \textbf{less} than a\textbf{no}ther.
	
	But the whole three Persons are co-eternal to\textbf{ge}ther * \textbf{---} and co-\textbf{e}qual.
	
	So that in all things, as is a\textbf{fore}said * the Unity in Trinity, and the Trinity in Unity \textbf{is} to be \textbf{wor}shiped.
	
	He therefore who \textbf{will} be saved * must think thus \textbf{of} the \textbf{Trin}ity.
	
	Furthermore, it is necessary to everlasting sal\textbf{va}tion * that he also believe rightly the Incarnation \textbf{of} our Lord \textbf{Je}sus Christ.
	
	For the right faith is that we believe \textbf{and} confess * that our Lord Jesus Christ, the Son of \textbf{God}, is \textbf{God} and Man.
	
	God, of the Substance of the Father, begotten be\textbf{fore} the worlds * and Man, of the Substance of his mother, \textbf{born} in \textbf{this} world.
	
	Perfect God, and \textbf{per}fect Man * of a reasonable soul and human \textbf{flesh} sub\textbf{sis}ting.
	
	Equal to the Father, as touching his \textbf{God}head * and inferior to the Father, as \textbf{touch}ing his \textbf{Man}hood.
	
	Who although he be \textbf{God} and Man * yet he is not \textbf{two}, but \textbf{one} Christ.
	
	One, not by the conversion of the Godhead \textbf{in}to flesh * but by taking of the \textbf{Man}hood \textbf{in}to God.
	
	One altogether, not by the confusion of \textbf{Sub}stance * but by the uni\textbf{ty} of a \textbf{Per}son.
	
	For as the reasonable soul and flesh is \textbf{one} man * so God and \textbf{Man} is \textbf{one} Christ.
	
	Who suffered for our sal\textbf{va}tion * descended into hell, rose again the \textbf{third} day \textbf{from} the dead.
	
	He ascended into heaven, he sitteth on the right hand of the Father, God Al\textbf{migh}ty * from whence he shall come to judge the \textbf{liv}ing \textbf{and} the dead.
	
	At whose coming all men will rise again with their \textbf{bo}dies * and shall give ac\textbf{count} for their \textbf{own} works.
	
	And they that have done good shall go into life ever\textbf{last}ing * and they that have done evil into ever\textbf{last}ing \textbf{fi}re.
	
	This is the \textbf{cath}olic faith * which except a man believe faithfully, he \textbf{can}not \textbf{be} saved.
	
	Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}it.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}