\begin{multicols}{2}
	Lest he devour my soul, like a lion, and tear it in \textbf{pie}ces * while there is no \textbf{one} to help me.
	
	O Lord my God, if I have \textbf{done} this thing * or if there be any wick\textbf{ed}ness in my hands.
	
	If I have rewarded evil unto him who was at \textbf{peace} with me * then let mine enemy persecute my \textbf{soul}, and take me.
	
	Yea, let him tread my life down u\textbf{pon} the earth * and lay mine \textbf{ho}nor in the dust.
	
	Stand up, O Lord, in thy wrath, and lift up thyself, because of the indignation of mine \textbf{en}emies * arise up for me in the judgment that thou \textbf{hast} commanded.
	
	And so shall the congregation of the people come a\textbf{bout} thee * for their sakes therefore lift \textbf{up} thyself again.
	
	The Lord shall judge the \textbf{peo}ple * judge me, O Lord according to my righteousness, and according to the innocence \textbf{that} is in me.
	
	O let the wickedness of the ungodly come \textbf{to} an end * \textbf{but} guide thou the just.
	
	For the \textbf{right}eous God * trieth the \textbf{ve}ry hearts and reins.
	
	My help cometh \textbf{of} God * who preserveth them \textbf{who} are true of heart.
	
	God is a righteous judge, strong and \textbf{pa}tient * shall he be \textbf{pro}voked every day?
	
	If a man will not turn, he will \textbf{whet} his sword * he hath bent his bow, and \textbf{made} it ready.
	
	He hath prepared for him the instruments \textbf{of} death * he ordaineth his arrows against the \textbf{per}secutors.
	
	Behold, he that travaileth with in\textbf{just}ice * he hath conceived sorrow, and brought \textbf{forth} ungodliness.
	
	He hath graven and dug \textbf{up} a pit * and is fallen himself into the destruction that he made \textbf{for} another.
	
	For his travail shall come upon his \textbf{own} head * and his wickedness shall fall \textbf{on} his own crown.
	
	I will give thanks unto the Lord, according to his \textbf{right}eousness * and I will praise the name \textbf{of} the Lord most High.
\end{multicols}