O Lord my God, in thee have I put my trust * save me from all them who persecute me, and deliver me.

Lest he devour my soul, like a lion, and tear it in pieces * while there is no one to help me.

O Lord my God, if I have done this thing * or if there be any wickedness in my hands.

If I have rewarded evil unto him who was at peace with me * then let mine enemy persecute my soul, and take me.

Yea, let him tread my life down upon the earth * and lay mine honor in the dust.

Stand up, O Lord, in thy wrath, and lift up thyself, because of the indignation of mine enemies * arise up for me in the judgment that thou hast commanded.

And so shall the congregation of the people come about thee * for their sakes therefore lift up thyself again.

The Lord shall judge the people * judge me, O Lord according to my righteousness, and according to the innocence that is in me.

O let the wickedness of the ungodly come to an end * but guide thou the just.

For the righteous God * trieth the very hearts and reins.

My help cometh of God * who preserveth them who are true of heart.

God is a righteous judge, strong and patient * shall he be provoked every day?

If a man will not turn, he will whet his sword * he hath bent his bow, and made it ready.

He hath prepared for him the instruments of death * he ordaineth his arrows against the persecutors.

Behold, he that travaileth with injustice * he hath conceived sorrow, and brought forth ungodliness.

He hath graven and dug up a pit * and is fallen himself into the destruction that he made for another.

For his travail shall come upon his own head * and his wickedness shall fall on his own crown.

I will give thanks unto the Lord, according to his righteousness * and I will praise the name of the Lord most High.