\vechapter{Liturgical Calendar}
	\skiplines{-1}\vesectionp{August}
		\begin{enumerate}[noitemsep, nolistsep]
			\item \footnote{This volume can begin as early as July 27, but no feast days occur between then and this date.} % 1
			\item % 2
			\item % 3
			\item % 4
			\item % 5
			\item \red{Transfiguration of the Lord.} Major feast.
			\item Saint Sixtus, Pope and Martyr. \red{3 lect. duplex.}
			\item % 8
			\item % 9
			\item Saint Laurence, Deacon and Martyr. \red{9 lect. duplex.}
			\item % 11
			\item % 12
			\item % 13
			\item \textcolor{purple}{Eve of the Assumption of Blessed Virgin Mary.}
			\item \red{\textbf{Assumption of Blessed Virgin Mary.}} Solemnity.
			\item % 16
			\item % 17
			\item % 18
			\item % 19
			\item % 20
			\item % 21
			\item % 22
			\item \textcolor{purple}{Eve of Saint Bartholomew, Apostle.}
			\item \red{Saint Bartholomew, Apostle.} Minor feast.
			\item % 25
			\item % 26
			\item % 27
			\item Saint Augustine, Bishop and Doctor. \red{9 lect. triplex.}
			\item Beheading of Saint John, Baptist. \red{9 lect. triplex.}
			\item % 30
			\item % 31
		\end{enumerate}

	\vesectionp{September}
	
		\begin{enumerate}[noitemsep, nolistsep]
			\item % 1
			\item % 2
			\item % 3
			\item % 4
			\item % 5
			\item % 6
			\item % 7
			\item \red{\textbf{Nativity of Blessed Virgin Mary.}} Principle feast.
			\item % 9
			\item % 10
			\item % 11
			\item % 12
			\item % 13
			\item \red{Exaltation of the Holy Cross.} Major feast.
			\item % 15
			\item Saints Cornelius and Cyprian, Bishops and Martyrs. \red{3 lect. duplex.}
			\item % 17
			\item % 18
			\item % 19
			\item \textcolor{purple}{Eve of Saint Matthew, Apostle and Evangelist.}
			\item \red{Saint Matthew, Apostle and Evangelist.} Minor feast.
			\item % 22
			\item Saint Linus, Pope and Martyr. \red{3 lect. duplex.}
			\item % 24
			\item % 25
			\item Saints Cosmas and Damian, Martyrs. \red{3 lect. duplex.}
			\item % 27
			\item % 28
			\item \red{Saint Michael, Archangel.} Minor feast.
			\item Saint Jerome, Priest and Doctor. \red{9 lect. triplex.}
		\end{enumerate}

	\vesectionp{October}

		\begin{enumerate}[noitemsep, nolistsep]
			\item % 1
			\item % 2
			\item % 3
			\item % 4
			\item % 5
			\item % 6
			\item % 7
			\item % 8
			\item \red{\textbf{Saint John Henry Newman, Patron.}} Solemnity.
			\item % 10
			\item % 11
			\item % 12
			\item % 13
			\item % 14
			\item % 15
			\item % 16
			\item Saint Ignatius of Antioch, Bishop and Martyr. \red{3 lect. duplex.}
			\item \red{Saint Luke, Evangelist.} Minor feast.
			\item % 19
			\item % 20
			\item % 21
			\item % 22
			\item % 23
			\item % 24
			\item % 25
			\item % 26
			\item \textcolor{purple}{Eve of Saints Simon and Jude, Apostles.}
			\item \red{Saints Simon and Jude, Apostles.} Minor feast.
			\item % 29
			\item % 30
			\item \textcolor{purple}{Eve of the Communion of All Saints.}
		\end{enumerate}
	
	\vesectionp{November}
	
		\begin{enumerate}[noitemsep, nolistsep]
			\item \red{\textbf{Communion of All Saints.}} Principle feast.
			\item Synaxis of the Holy Souls. \red{9 lect. triplex.}
			\item % 3
			\item % 4
			\item % 5
			\item % 6
			\item % 7
			\item % 8
			\item % 9
			\item % 10
			\item % 11
			\item % 12
			\item % 13
			\item % 14
			\item % 15
			\item % 16
			\item % 17
			\item % 18
			\item % 19
			\item % 20
			\item % 21
			\item Saint Cecilia, Virgin and Martyr. \red{9 lect duplex.}
			\item Saint Clement, Pope and Martyr. \red{9 lect. duplex.}
			\item Saint Chrysogonus, Martyr. \red{3 lect. simplex.}
			\item Saint Catherine, Virgin and Martyr. \red{3 lect. duplex.}
			\item % 26
			\item % 27
			\item % 28
			\item \textcolor{purple}{Eve of Saint Andrew, Apostle.}
			\item \red{Saint Andrew, Apostle.} Minor feast.
		\end{enumerate}