\vechapter{Liturgical Calendar}
	\skiplines{-1}\vesectionp{January}
	\begin{enumerate}[noitemsep,nolistsep]
		\item \red{Circumcision of the Lord.} Major feast.
		\item Octave of Saint Stephen. \red{9 lect. triplex.}
		\item Octave of Saint John. \red{9 lect. triplex.}
		\item Octave of the Innocents. \red{9 lect. triplex.}
		\item \textcolor{purple}{Eve of the Epiphany.} \red{9 lect. duplex}
		\item \red{\textbf{Epiphany of the Lord.}} Solemnity. \textit{With octave.}
		\item Of the Octave. \red{9 lect. duplex.}
		\item Of the Octave. \red{9 lect. duplex.}
		\item Of the Octave. \red{9 lect. duplex.}
		\item Of the Octave. \red{9 lect. duplex.}
		\item Of the Octave. \red{9 lect. duplex.}
		\item Of the Octave. \red{9 lect. duplex.}
		\item Octave of the Epiphany. \red{9 lect. triplex.}
		\item Felix, Priest and Martyr. \red{3 lect. simplex.}
		\item Paul, Hermit. \red{3 lect. simplex.}
		\item Marcellus, Pope and Martyr. \red{3 lect. simplex.}
		\item Anthony of Egypt,Abbot. \red{3 lect. simplex.}
		\item Prisca, Virgin and Martyr. \red{3 lect. simplex.}
		\item Marius, Martha, Audifax, and Abachum, Martyrs. \red{3 lect. simplex.}
		\item Fabian and Sebastian, Martyrs. \red{9 lect. duplex.}
		\item Agnes, Virgin and Martyr. \red{9 lect. duplex.}
		\item Vincent and Anastasius, Martyrs. \red{9 lect. duplex.}
		\item Emerentiana, Virgin and Martyr. \red{3 lect. simplex.}
		\item Timothy, Bishop and Martyr. \red{3 lect. simplex.}
		\item Conversion of Saint Paul, Apostle. \red{9 lect. triplex.}
		\item Polycarp, Bishop and Martyr. \red{3 lect. simplex.}
		\item John Chrysostom, Bishop and Doctor. \red{9 lect. duplex.}
		\item Thomas Aquinas, Priest and Doctor. \red{9 lect. duplex.}
		\item % 29
		\item Gregory Nazianzus,  Bishop and Doctor. \red{9 lect. duplex.}
		\item % 31
	\end{enumerate}

\vesectionp{February}	
	
	\begin{enumerate}[nolistsep,noitemsep]
		
		\item Ignatius, Bishop and Martyr. \red{3 lect. duplex.}
		\item \red{Purification of the Blessed Virgin Mary.} Principle feast.
		\item Blase, Bishop and Martyr. \red{3 lect. simplex.}
		\item % 4
		\item Agatha, Virgin and Martyr. \red{9 lect. duplex.}
		\item Dorothy, Virgin and Martyr.\red{3 lect. simplex.}
		\item % 7
		\item % 8
		\item Apollonia, Virgin and Martyr.\red{3 lect. simplex.}
		\item Scholastica, Virgin. \red{3 lect. simplex.}
		\item % 11
		\item % 12
		\item % 13
		\item Valentine, Priest and Martyr. \red{3 lect. simplex.}
		\item Faustinus and Jovita, Martyrs.
		\item % 16
		\item % 17
		\item Simeon, Bishop and Martyr. \red{3 lect. simplex.}
		\item % 19
		\item % 20
		\item % 21
		\item Cathedra of Saint Peter, Apostle. \red{9 lect. triplex.}
		\item % 23
		\item % 24
		\item % 25
		\item % 26
		\item % 27
		\item % 28
	\end{enumerate}
	
	\vesectionp{March}
	
	\begin{enumerate}[nolistsep,noitemsep]
		\item % 1
		\item % 2
		\item % 3
		\item % 4
		\item % 5
		\item % 6
		\item Perpetua and Felicity, Martyrs. \red{3 lect. simplex.}
		\item % 8
		\item Forty Saints of Sebaste, Martyrs. \red{3 lect. simplex.}
		\item % 10
		\item % 11
		\item \red{Gregory, Pope and Doctor.} Minor feast.
		\item % 13
		\item % 14
		\item % 15
		\item % 16
		\item Patrick, Bishop and Confessor. \red{9 lect. duplex.}
		\item % 18
		\item \red{Joseph, Spouse of the Blessed Virgin Mary. } Minor feast.
		\item % 20
		\item Benedict of Nursia, Abbot. \red{9 lect. duplex.}
		\item % 22
		\item % 23
		\item % 24
		\item \red{Annunciation of the Blessed Virgin Mary.} Major feast.
		\item % 26
		\item % 27
		\item % 28
		\item % 29
		\item % 30
		\item % 31
		
	\end{enumerate}