\vechapter{Liturgical Calendar}
	\skiplines{-1}\vesectionp{November}
		\begin{enumerate}[noitemsep, nolistsep]
			\setcounter{enumi}{26}
			\item {\textit{\small Earliest day for Advent.}}
			\item % 28
			\item \footnote{Outside of Advent, here is celebrated the Eve of Saint Andrew.}
			\item \red{Saint Andrew, Apostle.} Minor feast.
		\end{enumerate}
	\vesectionp{December}
		\begin{enumerate}[noitemsep, nolistsep]
			\item %\textit{\small Saint Nahum, Prophet.} % 1
			\item %\textit{\small Saint Habakkuk, Prophet.}  % 2
			\item \textit{\small Latest day for Advent.} %\textit{\small Saint Zephaniah, Prophet.}  % 3
			\item  % 4
			\item % 5
			\item Saint Nicholas, Bishop. \red{9 lect. duplex.}
			\item Saint Ambrose, Bishop and Doctor. \red{9 lect. triplex.}
			\item \red{Conception of the Blessed Virgin Mary.} Major feast.
			\item % 9
			\item % 10
			\item % 11
			\item  % 12
			\item Saint Lucy, Virgin and Martyr. \red{9 lect. duplex.}
			\item  % 14
			\item % 15
			\item %\textit{\small Saint Haggai, Prophet.}  % 16
			\item {\textit{\small O Wisdom.}} % 17
			\item  % 18
			\item  % 19
			\item  % 20
			\item %\textit{\small Saint Micah, Prophet.}  % 21
			\item  % 22
			\item  % 23
			\item \textcolor{purple}{\textbf{Eve of the Nativity.}}
			\item \textbf{\red{Nativity of the Lord.}} Solemnity. \textit{With octave.}
			\item \red{Saint Stephen, Protomartyr.} Major feast.
			\item \red{Saint John, Apostle and Evangelist.} Major feast.
			\item \red{Holy Innocents, Martyrs.} Major feast.
			\item \red{Saint Thomas Becket, Martyr.} Major feast.
			\item Of the Octave of the Nativity. % 30
			\item Of the Octave of the Nativity.
		\end{enumerate}
	\vesectionp{January}
		\begin{enumerate}[noitemsep, nolistsep]
			\item \red{Circumcision of the Lord.} Principle feast.
			\item Octave of Saint Stephen. \red{9 lect. triplex.}
			\item Octave of Saint John. \red{9 lect. triplex.}
			\item Octave of the Innocents. \red{9 lect. triplex.}
			\item \textcolor{purple}{\textbf{Eve of the Epiphany.}}
			\item \red{\textbf{Epiphany of the Lord.}} Solemnity.\footnote{On the following days, until the Sunday after Epiphany, its office is continued.}
		\end{enumerate}