\input{conf}

\begin{document}
	\newgeometry{margin=0pt}
	\begin{titlepage}
		\vspace*{\fill}
		
		\begin{center}
			
			\textbf{\Huge\color{red} VESPERALE}
			
			ACCORDING TO THE RITE OF THE
			
			\textbf{\LARGE HOLY ROMAN CHURCH}
			
			\vspace*{\fill}
			
			\textbf{\Large\color{red} VOLUME I}
			
			Seasons of Advent and Christmas\\Until the Epiphany of the Lord
			
		\end{center}
		
		\vspace*{\fill}
	\end{titlepage}
	
	\newgeometry{top=0.75in,bottom=0.75in,inner=0.75in,outer=0.75in,includefoot}
	
	\pagenumbering{arabic}
	\gresetinitiallines{0}
	
	\raggedbottom
	
	%\tableofcontents
	
	
	%%% COPY ABOVE %%%
	
	\input{noclune_calendar}
	
	
	\gresetinitiallines{1}
	
	\vepart{Ordinary}
	
		\vechapter{The Order of Vespers}
			\skiplines{-1}\vesectionp{Introduction}\label{vespers:introduction}
			
				\instruct{Before the service begins, kneel and make these prayers quietly.}
				
				Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
					
				Hail Mary, full of grace, the Lord is with thee. Blessed art thou among women and blessed is the fruit of thy womb, Jesus. Holy Mary, Mother of God, pray for us sinners now and at the hour of our death. Amen.
				
				\instruct{Stand as the minister begins from his place:}
				
				\gresetinitiallines{0}
				\skiplines{0.5}\gabcsnippet{(c3) <sp>v</sp> O(fv) God,(hv) make(hv) speed(iv) to(h) save(g) me.(hv) <sp>r</sp>(::) O(hv) Lord,(hv) make(hv) haste(hv) to(hv) help(g) me.(hv)}
				
				\instruct{The congregation continues together, turning toward the altar, making a profound bow, and crossing themselves at the invocation of the Holy Trinity here and whenever else:}
				
				\skiplines{0.5}\gabcsnippet{(c3) Glor(h)y(h) be(h) to(h) the(h) Fa(h)ther,(h) and(h) to(h) the(h) Son,(h) (,) and(h) to(h) the(h) Ho(h)ly(h) Spir(g)it.(hv) (:) As(h) it(h) was(h) in(h) the(h) be(h)gin(h)ning,(h) is(h) now(h) and(h) ev(h)er(h) shall(g) be:(hv) (,) world(hv) with(hv)out(hv) end.(hv) A(g)men.(hv) (::) A(hv)le(hi)lu(h)ia.(hg)}
				
			\vesectionp{Psalmody}\label{vespers:psalmody}
			
				\instruct{Turn to the \greenribbon and sing the psalms with their antiphons prescribed there in this manner.}
				
				\instruct{The minister intones all antiphons until the asterisk, when he is then joined by the whole choir. Once the antiphon has been intoned, all psalms are sung to its tone until another antiphon is began.}
				
				\instruct{Psalms themselves are sung in this manner: the precentor or succentor sings the verse until the asterisk, when he is then joined by that entire side of the congregation. The other then begins the next verse, and that side of the congregation joins after the asterisk.}
				
				\instruct{Once a psalm is complete, if another antiphon is to be sung, first the previous antiphon is repeated. This is usually after every psalm. that is, each antiphon has one psalm under it, but on occasions multiple psalms are sung to the same antiphon. In this case, the antiphon is only repeated once all its psalms have been sung.}
				
			\vesection{Chapter}\label{vespers:chapter}
			
				\instruct{Once the psalmody is finished, the lector will read the chapter from his place. This is a short reading of Scripture, no more than three verses in length. The congregation responds:}
				
				\skiplines{0.5}\gabcsnippet{(c3) Thanks(h) be(h) to(h) God.(h)}
				
				\instruct{There is usually a responsory to accompany the chapter, which is sung in this manner.}
				
				\instruct{The lector will sing the responsory until the asterisk, when he is joined by the whole choir. Finishing this, the lector will sing any verses to which the whole congregation sings the prescribed response.}
				
				\instruct{Even when the \enquote{Glory be} is sung, the lector sings it alone, but all the congregation turns toward the altar, makes a profound bow, and crosses themselves as it is sung.}
				
				\instruct{After the responsory is the hymn. One of the cantors will intone the first line of the hymn when he is joined by the whole congregation.}
				
				\instruct{After the hymn is a versicle which the minister proclaims the verse and the whole congregation gives the response.}
				
				\instruct{Turn to the \redribbon and sing the responsory, if any, hymn, and versicle.}
				
			\vesection{Magnificat}\label{vespers:magnificat}
			
				\instruct{After the versicle has been sung, the minister proceeds to stand before the altar and intones the antiphon to the Canticle of Mary until the asterisk, when he is joined by the whole choir. The precentor, succentor, and congregation sings the verses of the canticle in like manner as the psalms.}
				
				\instruct{While the canticle is sung, where possible, the minister incenses the altar.}
				
			\vesectionp{Preces}\label{vespers:preces}
			
				\instruct{The preces are said on feria, that is, days besides Sunday when no feast day occurs. But they are not said from December 17 until after the Epiphany. The whole congregation kneels.}
				
				\instruct{The precentor and succentor alternate singing \enquote{Kyrie, eleison} to this melody. Each invocation is sung thrice.}
				
				\skiplines{0.5}\gregorioscore{common/preces/kyrie.gabc}
				
				\instruct{The first invocation and the last are sung by the precentor.}
				
				\instruct{Make this prayer quietly:}
				
				Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
				
				\instruct{Then the petitions are said:}
				
				\skiplines{0.5}\gregorioscore{common/preces/petitions.gabc}
				
				\instruct{This psalm is then recited by the congregation in a low voice:}
				
				\veheading{Psalm l: Miserere mei Deus}
				\input{psalter/50/text}
				
				\instruct{The priest alone stands and proceeds to stand before the altar, where he proclaims this peition:}
				
				\skiplines{0.5}\gregorioscore{common/preces/conclusion.gabc}
				
			\vesection{Conclusion}\label{vespers:conclusion}
			
				\instruct{The minister proceeds again to stand before the altar and says this versicle:}
				
				\skiplines{0.5}\gabcsnippet{(c3) <sp>v</sp> O(h) Lord,(h) hear(h) my(f) prayer.(g) <sp>r</sp>(::) And(h) let(h) my(h) cry(h) come(h) un(h)to(f) thee.(f)}
				
				\instruct{He will then proclaim the invocation \enquote{Let us pray}, after which he will genuflect. If the preces have been said, the congregation kneels during the collect; otherwise they remain standing.}
				
				\instruct{The minister will then pray the collect of the day. The congregation responds:}
				
				\skiplines{0.5}\gabcsnippet{(c3) A(gh)men.(h)}
				
				\instruct{This petition concludes the office:}
				
				\skiplines{0.5}\gregorioscore{common/conclusion.gabc}
				
				\instruct{Then kneel and make this prayer quietly:}
				
				Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
			
		\vechapter{The Order of Compline}
	
	
	\gresetinitiallines{1}
	
	\vepart{Psalter}
	
		\vechapter{Sunday at First Vespers}
		
			\veant{1}{vi}
			\skiplines{1}\gregorioscore{ant/benedictus_dominus.gabc}
			
			\greannotation{\veformat{Ps. 143}}
			\greannotation{\veformat{vi. i.}}
			\skiplines{1}\gabcsnippet{(c3) Bles(hv)ed(iv) (:?) be(jrv) the() Lord(jv) my(i) strength(jv) <sp>*</sp>(:) who(jrv) teacheth() my() hands() to() war,() and() my(jr) <b>fin</b>(h)gers(ij) to(i) (hr) fight.(h)}
			
			\input{psalter/143/6} % tone 6 has only the one ending
		
			\instruct{Turn to the \whiteribbon at the chapter rite, pp. \pageref{vespers:chapter}.}
	
	\vepart{Propers}
	
		\vechapter{First Sunday in Advent}
			
			\skiplines{-1}\vesectionp{At First Vespers}
				
				\resp{Ecce dies veniunt}{viii}
				\gregorioscore{resp/ecce_dies_veniunt.gabc}
					
				\instruct{Turn to the \blueribbon and sing the hymn and versicle.}
				
				\skiplines{1}
				\veant{M}{I. i}
				\gregorioscore{ant/ecce_nomen_domini.gabc}
				
				\input{psalter/magnificat/1}
			
				\instruct{Turn to the \whiteribbon at the conclusion rite, pp. \pageref{vespers:conclusion}.}
			
			\vesection{At Compline}
			
			\vesection{At Second Vespers}
	
	\vepart{Commons}
	
		\vechapter{Common of Advent I}
		
			\skiplines{-1}\resp{Tu exurgens Domine}{iv}
			\gregorioscore{resp/tu_exurgens_domine.gabc}
			
			\input{hymn/conditor_alme_siderum}
			
			\gresetinitiallines{0}\gabcsnippet{
				<sp>v</sp> Drop(hv) down,(hv) ye(hv) hea(hv)vens,(hv) from(hv) a(hv)bove.(ghGFEfhGF) <sp>r</sp>(::) And(hv) let(hv) the(hv) skies(hv) pour(hv) down(hv) right(hv)eous(f)ness:(gv) (;) let(hv) the(hv) earth(hv) o(hv)pen,(hv) and(hv) let(hv) it(hv) bring(hv) forth(hv) sal(hv)va(f)tion.(f)
			}\gresetinitiallines{1}
				
			\instruct{The Magnificat is always proper on all days in Advent; turn to the \redribbon and sing as appointed there.}
			
		\vechapter{Common of Advent II}
		
			\skiplines{-1}\resp{Festina ne taraveris}{ii}
			\gregorioscore{resp/festina_ne_taraveris.gabc}
		
			\clearpage\input{hymn/conditor_alme_siderum}
			
			\gresetinitiallines{0}\gabcsnippet{
				<sp>v</sp> Drop(hv) down,(hv) ye(hv) hea(hv)vens,(hv) from(hv) a(hv)bove.(ghGFEfhGF) <sp>r</sp>(::) And(hv) let(hv) the(hv) skies(hv) pour(hv) down(hv) right(hv)eous(f)ness:(gv) (;) let(hv) the(hv) earth(hv) o(hv)pen,(hv) and(hv) let(hv) it(hv) bring(hv) forth(hv) sal(hv)va(f)tion.(f)
			}\gresetinitiallines{1}
			
			\instruct{The Magnificat is always proper on all days in Advent; turn to the \redribbon and sing as appointed there.}
			
\end{document}