\begin{multicols}{2}
	Blessed are they who keep his testi\textbf{mo}nies * and seek him \textbf{with} their whole heart.
	
	For they do no wick\textbf{ed}ness * \textbf{who} walk in his ways.
	
	Thou hast \textbf{charged} us * that we shall diligently keep \textbf{thy} commandments.
	
	O that my ways were made so \textbf{di}rect * that I might \textbf{keep} thy statutes.
	
	So shall I not be con\textbf{found}ed * while I have respect unto all \textbf{thy} commandments.
	
	I will thank thee with an un\textbf{feigned} heart * when I shall have learned the judgments \textbf{of} thy righteousness.
	
	I will keep thy cere\textbf{mo}nies * O forsake \textbf{me} not utterly.
	
	Wherewithal shall a young man cleanse \textbf{his} way * even by ruling him\textbf{self} after thy word.
	
	With my whole heart have I \textbf{sought} thee * O let me not go wrong out of \textbf{thy} commandments.
	
	Thy words have I hid within \textbf{my} heart * that I should not \textbf{sin} against thee.
	
	Blessed art thou, \textbf{O} Lord * O teach \textbf{me} thy statutes.
	
	With my lips have I been \textbf{tell}ing * of all the \textbf{judg}ments of thy mouth.
	
	I have had as great delight in the way of thy testi\textbf{mo}nies * as in all man\textbf{ner} of riches.
	
	I will talk of thy com\textbf{mand}ments * and have re\textbf{spect} unto thy ways.
	
	My delight shall be in thy \textbf{stat}utes * and I will \textbf{not} forget thy word.
	
	Glory be to the Father, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}