\begin{multicols}{2}
	Blessed are they that keep his \textbf{tes}timonies * and seek \textbf{him} with their whole heart.
	
	For they who \textbf{do} no wickedness * \textbf{who} walk in his eyes.
	
	\textbf{Thou} hast charged us * that we shall diligently \textbf{keep} thy commandments.
	
	O that my ways \textbf{were} made so direct * that I \textbf{might} keep thy statutes.
		
	So shall I not \textbf{be} confounded * while I have respect unto \textbf{all} thy commandments.
	
	I will thank thee \textbf{with} an unfeigned heart * when I shall have learned the judg\textbf{ments} of thy righteousness.
	
	I will keep thy \textbf{cer}emonies * O for\textbf{sake} me not utterly.
	
	Wherewithal shall a \textbf{young} man cleanse his way * even by ruling him\textbf{self} after thy word.
	
	With my whole heart \textbf{have} I sought thee * O let me not go wrong out \textbf{of} thy commandments.
	
	Thy words have I \textbf{hid} within my heart * that I should \textbf{not} sin against thee.
	
	Bles\textbf{sed} art thou, O Lord * O \textbf{teach} me thy statutes.
	
	With my lips have \textbf{I} been telling * of all \textbf{the} judgments of thy mouth.
	
	I have had as great delight in the way of thy \textbf{tes}timonies * as in all \textbf{man}ner of riches.
	
	I will talk of \textbf{thy} commandments * and have \textbf{res}pect unto thy ways.
	
	My delight shall be \textbf{in} thy statutes * and I \textbf{will} not forget thy word.
	
	Glory be to the Fa\textbf{ther}, and to the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er shall be * world \textbf{with}out end. Amen.
\end{multicols}