\begin{multicols}{2}
	Blessed are they that keep his testi\textbf{mo}nies * and seek him \textbf{with} their whole heart.
	
	For they who do no \textbf{wick}edness * who \textbf{walk} in his ways.
	
	Thou hast \textbf{charged} us * that we shall diligently keep \textbf{thy} commandments.
	
	O that my ways were made \textbf{so} direct * that I might \textbf{keep} thy statutes.
	
	So shall I not be con\textbf{found}ed * while I have respect unto all \textbf{thy} commandments.
	
	I will thank thee with an \textbf{un}feigned heart * when I shall have learned the judgments \textbf{of} thy righteousness.
	
	I will keep thy cere\textbf{mo}nies * O forsake \textbf{me} not utterly.
	
	Wherewithal shall a young man \textbf{cleanse} his way * even by ruling himself \textbf{af}ter thy word.
	
	With my whole heart have I \textbf{sought} thee * O let me not go wrong out of \textbf{thy} commandments.
	
	Thy words have I hid with\textbf{in} my heart * that I should not \textbf{sin} against thee.
	
	Blessed art \textbf{thou}, O Lord * O teach \textbf{me} thy statutes.
	
	With my lips have I been \textbf{tel}ling * of all the \textbf{judg}ments of thy mouth.
	
	I have had as great delight in the way of thy testi\textbf{mon}ies * as in all man\textbf{ner} of riches.
	
	I will talk of thy com\textbf{mand}ments * and have res\textbf{pect} unto thy ways.
	
	My delight shall be in thy \textbf{stat}utes * and I will \textbf{not} forget thy word.
	
	Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}