\begin{multicols}{2}
	I will say unto the Lord, Thou art my hope, and my \textbf{strong}hold * my God, \textbf{in} him will I trust.
	
	For he shall deliver thee from the snare of the \textbf{hunt}er * and from the \textbf{noi}some pestilence.
	
	He shall defend thee under his wings, and thou shalt be safe under his \textbf{fea}thers * his faithfulness and truth shall be thy \textbf{shield} and buckler.
	
	Thou shalt not be afraid for any terror \textbf{by} night * nor for the arrow that \textbf{fli}eth by day.
	
	For the pestilence that walketh in \textbf{dark}ness * nor for the sickness that destroyeth \textbf{in} the noonday.
	
	A thousand shall fall beside thee, and ten thousand at thy \textbf{right} hand * but it shall \textbf{not} come nigh thee.
	
	Yea, with thine eyes shalt \textbf{thou} behold * and see the reward of \textbf{the} ungodly.
	
	For thou, Lord, \textbf{art} my hope * thou hast set thine house of \textbf{de}fense very high.
	
	There shall no evil happen \textbf{un}to thee * neither shall any plague come \textbf{nigh} thy dwelling.
	
	For he shall give his angels charge \textbf{ov}er thee * to keep \textbf{thee} in all thy ways.
	
	They shall bear thee \textbf{in} their hands * that thou hurt not thy \textbf{foot} against a stone.
	
	Thou shalt go upon the lion and \textbf{ad}der * the young lion and the dragon shalt thou tread \textbf{un}der thy feet.
	
	Because he hath set his love upon me, therefore will I de\textbf{liv}er him * I will set him up, because \textbf{he} hath known my Name.
	
	He shall call upon me, and I will \textbf{hear} him * yea, I am with him in trouble; I will deliver him, and bring \textbf{him} to honor.
	
	With long life will I satis\textbf{fy} him * and shew him \textbf{my} salvation.
	
	Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}