\begin{multicols}{2}
	To tell of thy loving-kindness early in the \textbf{morn}ing * and of thy truth in \textbf{the} night-season.
	
	Upon an instrument of ten strings, and u\textbf{pon} the lute * upon a loud instrument, \textbf{and} upon the harp.
	
	For thou, Lord, hast made me glad \textbf{through} thy works * and I will rejoice in giving praise for \textbf{the} works of thy hands.
	
	O Lord, how glorious \textbf{are} thy works * thy \textbf{thoughts} are very deep.
	
	An unwise man doth not well con\textbf{si}der this * and a fool doth not \textbf{un}derstand it.
	
	When the ungodly are green as the grass, when all the workers of wickedness do \textbf{flour}ish * then shall they be destroyed forever, but thou, Lord, art the High\textbf{est} forevermore.
	
	For lo, thine enemies, O Lord, lo, thine enemies shall \textbf{per}ish * and all the workers of wicked\textbf{ness} shall be destroyed.
	
	But mine horn shall be exalted like the horn of a \textbf{u}nicorn * for I am anointed \textbf{with} fresh oil.
	
	Mine eyes also shall look down upon mine \textbf{en}emies * and mine ear shall hear the desire of the wicked that rise \textbf{up} against me.
	
	The righteous shall flourish like a \textbf{palm}-tree * and shall spread abroad like a ce\textbf{dar} in Lebanon.
	
	Such as are planted in the house \textbf{of} the Lord * shall flourish in the courts of \textbf{the} house of our God.
	
	They also shall bring forth more fruit \textbf{in} their age * and shall be fat \textbf{and} well-liking.
	
	That they may shew how true the Lord my \textbf{strength} is * and that there is no unright\textbf{eous}ness in him.
	
	Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}