\begin{multicols}{2}
	O Lord, revive thy work in the midst of the years, in the midst \textbf{of} the years make known * and in wrath \textbf{re}member mercy.
	
	God \textbf{came} from Teman * and the Holy \textbf{One} from mount Paran.
	
	His glory co\textbf{vered} the heavens * and the \textbf{earth} was full of his praise.
	
	And his brightness was as the light; he had horns com\textbf{ing} out of his hand * and there was the hi\textbf{ding} of his power.
	
	Before him \textbf{went} the pestilence * and burning coals \textbf{went} forth at his feet.
	
	He stood, and measured the earth; he beheld, and drove asun\textbf{der} the nations * and the everlasting \textbf{moun}tains were scattered.
	
	The perpe\textbf{tu}al hills did bow * his ways \textbf{are} everlasting.
	
	I saw the tents of Cushan \textbf{in} affliction * and the curtains of the land of Mi\textbf{di}an did tremble.
	
	Was the Lord displeased a\textbf{gainst} the rivers? * was thine anger \textbf{a}gainst the rivers?
	
	Was thy \textbf{wrath} against the sea? * that thou didst ride upon thy horses and thy char\textbf{iots} of salvation?
	
	Thy bow was \textbf{made} quite naked * according to the oaths of the \textbf{tribes}, even thy word.
	
	Thou didst cleave the \textbf{earth} with rivers * the mountains saw \textbf{thee}, and they trembled.
	
	The overflowing of \textbf{the} water passed by * the deep uttered his voice, and lif\textbf{ted} up his hands on high.
	
	The sun and moon stood still in their \textbf{ha}bitation * at the light of thine arrows they sent, and at the shining of \textbf{thy} glittering spear.
	
	Thou didst march through the land in \textbf{in}dignation * thou didst thresh the \textbf{hea}then in anger.
	
	Thou wentest forth for the salvation \textbf{of} the people * even for salvation \textbf{with} thine anointed\footnote{The Latin reads \textit{Christo tuo.}}.
	
	Thou woundest the head out of the house \textbf{of} the wicked * by discovering the foun\textbf{da}tion unto the neck.
	
	Thou didst strike through with his staves the head \textbf{of} his villages * they came out as a whirlwind to scatter me; their rejoicing was to devo\textbf{ur} the poor secretly.
	
	Thou didst walk through the seas \textbf{with} thine horses * through the \textbf{heap} of great waters.
	
	When I heard, my \textbf{bel}ly trembled * my \textbf{lips} quivered at the voice.
	
	Rottenness entered into my bones, and I \textbf{trem}bled in myself * that I might rest in \textbf{the} day of trouble.
	
	When he cometh up un\textbf{to} the people * he will invade \textbf{them} with his soldiers.
	
	Although the fig-tree \textbf{shall} not blossom * neither \textbf{shall} fruit be in the vines.
	
	The labor of the \textbf{o}live shall fail * and \textbf{the} field shall yield no meat.
	
	The flock shall be \textbf{cut} off from the fold * and there shall \textbf{be} no herd in the stalls.
	
	Yet I will \textbf{re}joice in the Lord * I will joy in the God \textbf{of} my salvation.
	
	The Lord God is my strength, and he will make my \textbf{feet} like hinds' feet * and he will make me to walk u\textbf{pon} mine high places.
	
	Glory be to the Fa\textbf{ther}, and to the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er shall be * world \textbf{with}out end. Amen.
\end{multicols}