O Lord, I have heard thy speech * and was afraid.

O Lord, revive thy work in the midst of the years, in the midst of the years make known * and in wrath remember mercy.

God came from Teman * and the Holy One from mount Paran.

His glory covered the heavens * and the earth was full of his praise.

And his brightness was as the light; he had horns coming out of his hand * and there was the hiding of his power.

Before him went the pestilence * and burning coals went forth at his feet.

He stood, and measured the earth; he beheld, and drove asunder the nations * and the everlasting mountains were scattered.

The perpetual hills did bow * his ways are everlasting.

I saw the tents of Cushan in affliction * and the curtains of the land of Midian did tremble.

Was the Lord displeased against the rivers? * was thine anger against the rivers?

Was thy wrath against the sea? * that thou didst ride upon thy horses and thy chariots of salvation?

Thy bow was made quite naked * according to the oaths of the tribes, even thy word.

Thou didst cleave the earth with rivers * the mountains saw thee, and they trembled.

The overflowing of the water passed by * the deep uttered his voice, and lifted up his hands on high.

The sun and moon stood still in their habitation * at the light of thine arrows they sent, and at the shining of thy glittering spear.

Thou didst march through the land in indignation * thou didst thresh the heathen in anger.

Thou wentest forth for the salvation of the people * even for salvation with thine anointed\footnote{The Latin reads \textit{Christo tuo.}}.

Thou woundest the head out of the house of the wicked * by discovering the foundation unto the neck.

Thou didst strike through with his staves the head of his villages * they came out as a whirlwind to scatter me; their rejoicing was to devour the poor secretly.

Thou didst walk through the seas with thine horses * through the heap of great waters.

When I heard, my belly trembled * my lips quivered at the voice.

Rottenness entered into my bones, and I trembled in myself * that I might rest in the day of trouble.

When he cometh up unto the people * he will invade them with his soldiers.

Although the fig-tree shall not blossom * neither shall fruit be in the vines.

The labor of the olive shall fail * and the field shall yield no meat.

The flock shall be cut off from the fold * and there shall be no herd in the stalls.

Yet I will rejoice in the Lord * I will joy in the God of my salvation.

The Lord God is my strength, and he will make my feet like hinds' feet * and he will make me to walk upon mine high places.