\veant{1}{v. i}
\gregorioscore{ant/in_conspectu_angelorum.gabc}

\greannotation{\veformat{Ps. 137}}
\greannotation{\veformat{v. i.}}
\skiplines{1}\gabcsnippet{
	(c4) I(f) will(h) (:?) give(jr) thanks() unto() thee,() O() Lord,() with() my(j) <b>whole</b>(k) heart(jr j) <sp>*</sp>(:) e(jr)ven() before() the() gods() will() I() sing(jr) <b>praise</b>(k) un(ir i)<b>to</b>(j) thee.(hr h) 
}

\input{psalter/137/5}

\repant{ant/in_conspectu_angelorum.gabc}

\pagebreak[0]

\veant{2}{iii. vi}
\skiplines{1}\gregorioscore{ant/domine_probasti.gabc}

\greannotation{\veformat{Ps. 138}}
\greannotation{\veformat{iii. vi.}}
\skiplines{1}\gabcsnippet{
	(c4) O(g) Lord,(h) (:?) thou(jr) hast() searched() me(j) <b>out</b>,(k) and(jr) <b>known</b>(i) me(jr j) <sp>*</sp>(:) thou(jr) knewest() my down()-sitting,() and() mine() upraising;() thou un()der()stand(j)<b>est</b>(h) my(j) thoughts(i) long(h) be(gr)fore.(g)
}

\input{psalter/138/3}

\repant{ant/domine_probasti.gabc}

\pagebreak[0]


\veant{3}{iv. vi}
\skiplines{0}\gregorioscore{ant/a_viro_iniquo.gabc}

\greannotation{\veformat{Ps. 139}}
\greannotation{\veformat{iv. vi.}}
\skiplines{1}\gabcsnippet{
	(c4) De(h)li(g:?)ver(hr) me,() O() Lord,(h) <b>from</b>(g) the(h) e(i)vil(hr) man(h) <sp>*</sp>(:) and(hr) preserve() me() from() the() wicked(h) <b>man</b>.(g)
}

\input{psalter/139/4}

\repant{ant/a_viro_iniquo.gabc}

\pagebreak[0]


\veant{4}{viii. ii}
\skiplines{1}\gregorioscore{ant/domine_clamavi.gabc}

\greannotation{\veformat{Ps. 140}}
\greannotation{\veformat{viii. ii.}}
\skiplines{1}\gabcsnippet{
	(c3) Lord,(e) I(f) (:?) call(hr) upon() thee,() haste() thee(h) <b>un</b>(i)to(hr) me(h) <sp>*</sp>(:) and(hr) consider() my() voice() when(h) <b>I</b>(f) cry(h) un(i)to(hr) thee.(h)
}

\input{psalter/140/8}

\repant{ant/domine_clamavi.gabc}


\pagebreak[0]

\veant{5}{viii. ii}
\skiplines{1}\gregorioscore{ant/portio_mea.gabc}

\greannotation{\veformat{Ps. 141}}
\greannotation{\veformat{viii. ii.}}
\skiplines{1}\gabcsnippet{
	(c3) I(e) cried(f) (:?) un(hr)to() the() Lord(h) <b>with</b>(i) my(hr) voice(h) <sp>*</sp>(:) yea,(hr) even() unto() the() Lord() did() I() make() my(h) <b>supp</b>(f)li(h)ca(i)tion.(hr h)
}

\input{psalter/141/8}

\repant{ant/portio_mea.gabc}

\instruct{Turn back to the \whiteribbon for the chapter.}