\vesectionp{Introduction}\label{vespers:introduction}

	\instruct{Before the service begins, kneel and make these prayers quietly.}
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
	
	Hail Mary, full of grace, the Lord is with thee. Blessed art thou among women and blessed is the fruit of thy womb, Jesus. Holy Mary, Mother of God, pray for us sinners now and at the hour of our death. Amen.
	
	\instruct{Stand as the minister begins from his place:}
	
	\gresetinitiallines{0}
	\skiplines{1}\gabcsnippet{(c3) <sp>v</sp> O(fv) God,(hv) make(hv) speed(iv) to(h) save(g) me.(hv) <sp>r</sp>(::) O(hv) Lord,(hv) make(hv) haste(hv) to(hv) help(g) me.(hv)}
	
	\instruct{The congregation continues together, turning toward the altar, making a profound bow, and crossing themselves at the invocation of the Holy Trinity here and whenever else:}
	
	\skiplines{1}\gabcsnippet{(c3) Glor(h)y(h) be(h) to(h) the(h) Fa(h)ther,(h) and(h) to(h) the(h) Son,(h) (,) and(h) to(h) the(h) Ho(h)ly(h) Spir(g)it.(hv) (:) As(h) it(h) was(h) in(h) the(h) be(h)gin(h)ning,(h) is(h) now(h) and(h) ev(h)er(h) shall(g) be:(hv) (,) world(hv) with(hv)out(hv) end.(hv) A(g)men.(hv) (::) A(hv)le(hi)lu(h)ia.(hg)}
	
\vesectionp{Psalmody}\label{vespers:psalmody}

	\instruct{Turn to the \greenribbon and sing the psalms with their antiphons as appointed there.}
	
\vesectionp{Chapter}\label{vespers:chapter}

	\instruct{The lector then proceeds to stand before the altar and reads the chapter. The congregation responds:}
	
	\skiplines{1}\gabcsnippet{(c3) Thanks(h) be(h) to(h) God.(h)}
	
	\instruct{Turn to the \redribbon and sing the responsory if any is appointed or prescribed there, and the hymn and versicle.}
	
\vesection{Magnificat}\label{vespers:magnificat}

	\instruct{The Magnificat is sung in like manner to the psalmody. The minister incenses the altar during its singing.}
	
	\instruct{Cantors, turn back to the \greenribbon and sing the Kyrie as appointed there. All kneel.}
	
	%\instruct{On the feast of Saint Andrew, this is sung:}
	
	%\skiplines{1}\gregorioscore{kyrie/iv.gabc}
	
	%\instruct{On the feast of the Conception of Blessed Virgin Mary, this is sung:}
	
	%\skiplines{1}\gregorioscore{kyrie/ix.gabc}

	
\vesectionp{Preces}\label{vespers:preces}

	\instruct{The preces are said on feria (days other than Sunday) when no feast occurs, but they are omitted from December 17 until after the Epiphany. If the preces are not to be said, skip to the conclusion on pp. \pageref{vespers:conclusion}.}
	
	
	\instruct{After the cantors have sang the Kyrie, make this prayer quietly.}
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
	
	\instruct{Then this petition is made.}
	
	\skiplines{1}\gregorioscore{common/preces/petitions.gabc}
	
	\instruct{This psalm is then recited together by the congregation in a low voice.}
	
	\veheading{\textit{Miserere mei, Deus.} Psalm 50.}
	\input{psalter/50/text}
	
	\instruct{Then this petition is made.}
	
	\skiplines{1}\gregorioscore{common/preces/conclusion.gabc}
	
\vesection{Conclusion}\label{vespers:conclusion}

	\instruct{All stand as the minister begins.}
	
	\skiplines{1}\gabcsnippet{(c3) <sp>v</sp> O(h) Lord,(h) hear(h) my(f) prayer.(g) <sp>r</sp>(::) And(h) let(h) my(h) cry(h) come(h) un(h)to(f) thee.(f)}
	
	\instruct{The minister will then proclaim the collect of the day. The congregation responds:}
	
	\skiplines{1}\gabcsnippet{(c3) A(gh)men.(h)}
	
	\instruct{This petition concludes the office.}
	
	\skiplines{1}\gregorioscore{common/conclusion.gabc}
	
	\instruct{All then kneel and make this prayer quietly.}
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.