\veant{1}{vi}
\gregorioscore{ant/benedictus_dominus.gabc}

\greannotation{\veformat{Ps. 143}}
\greannotation{\veformat{vi. i.}}
\skiplines{1}\gabcsnippet{
	(f3) Bles(hv)ed(iv) (:?) be(jrv) the() Lord(jv) <b>my</b>(i) strength(jv) <sp>*</sp>(:) who(jrv) teacheth() my() hands() to() war,() and() my(jv) <b>fin</b>(h)gers(ij) to(i) (hr) fight.(h)
}

\input{psalter/143/6}

\repant{ant/benedictus_dominus.gabc}

\pagebreak[1]


\veant{2}{viii. iii}
\skiplines{1}\gregorioscore{ant/in_eternum.gabc}

\greannotation{\veformat{Ps. 144}}
\greannotation{\veformat{viii. iii.}}
\skiplines{1}\gabcsnippet{
	(c4) I(g) will(hv) (:?) mag(jrv)nify() thee,() O(jv) <b>God</b>,(kv) my(jr) King() <sp>*</sp>(:) and(jr) I() will() praise() thy() Name() for(j)ev(j)<b>er</b>(i) and(h) ev(jv)er.(jr)
}

\input{psalter/144/8}

\repant{ant/in_eternum.gabc}


\pagebreak[1]

\veant{3}{iv. i}
\skiplines{1}\gregorioscore{ant/laudabo.gabc}

\greannotation{\veformat{Ps. 145}}
\greannotation{\veformat{iv. i.}}
\skiplines{1}\gabcsnippet{
	(c4) Praise(hv) the(g) (:?) Lord,(hrv) O() my() soul;() while() I() live,(hv) <b>will</b>(g) I(hv) praise(iv) the(hr) Lord <sp>*</sp>(:) yea,(hr) as() long() as() I() have() any() being,() I() will() sing(h) <b>prai</b>(g)ses(h) un(ih)to(gvFE) my(er) God.(e)
}

\input{psalter/145/4}

\repant{ant/laudabo.gabc}


\pagebreak[1]

\veant{4}{viii. iii}
\skiplines{1}\gregorioscore{ant/deo_nostro.gabc}

\greannotation{\veformat{Ps. 146}}
\greannotation{\veformat{viii. iii.}}
\skiplines{1}\gabcsnippet{
	(c3) O(e) praise(fv) (:?) the(hrv) Lord,() for() it() is() a() good() thing() to() sing() praises() un(hv)<b>to</b>(iv) our(hr) God(h) <sp>*</sp>(:) yea,(hr) a() joyful() and() pleasant() thing() it() is(h) <b>to</b>(g) be(f) thank(hrv)ful.(hv)
}

\input{psalter/146/8}

\repant{ant/deo_nostro.gabc}


\pagebreak[1]

\veant{5}{iv. vii}
\gregorioscore{ant/lauda_hierusalem.gabc}

\greannotation{\veformat{Ps. 147}}
\greannotation{\veformat{iv. vii.}}
\skiplines{1}\gabcsnippet{
	(c4) Praise(hr) the() Lord,(h) <b>O</b>(g) Je(hv)ru(iv)sa(hr)lem(h) <sp>*</sp>(:) praise(hr) thy() God,() O() <b>Zi</b>(g)on.(hv)
}

\input{psalter/147/4}

\repant{ant/lauda_hierusalem_2.gabc}

\instruct{Turn back to the \whiteribbon.}