\veant{1}{iv. vi}
\gregorioscore{ant/in_domum_domini.gabc}

\greannotation{\veformat{Ps. 121}}
\greannotation{\veformat{iv. vi.}}
\skiplines{1}\gabcsnippet{
	(c4) I(h) was(g) (:?) glad(hr) when(h) <b>they</b>(g) said(h) un(i)to(hr) me(h) <sp>*</sp>(:) We(hr) will() go() into() the() house(h) of(h) the(h) <b>Lord.</b>(g) 
}

\input{psalter/121/4}

\repant{ant/in_domum_domini.gabc}

\pagebreak[0]


\veant{2}{viii. i}
\skiplines{1}\gregorioscore{ant/qui_habitas.gabc}

\greannotation{\veformat{Ps. 122}}
\greannotation{\veformat{viii. i.}}
\skiplines{1}\gabcsnippet{
	(c4) Un(g)to(h) (:?) thee(jr) I() lift(j) <b>up</b>(k) mine(jr) eyes(j) <sp>*</sp>(:) O(jr) thou() that() dwellest(j) <b>in</b>(i) the(j) hea(h)vens.(gr g)
}

\input{psalter/122/8}

\repant{ant/qui_habitas.gabc}


\pagebreak[0]



\veant{3}{i. iii}
\skiplines{1}\gregorioscore{ant/adjutorium_nostrum.gabc}

\greannotation{\veformat{Ps. 123}}
\greannotation{\veformat{i. iii.}}
\skiplines{1}\gabcsnippet{
	(c4) If(f) the(g) (:?) Lord(hr) had() not() been() on() our() side,() now() let() Is()ra(h)<b>el</b>(g) say(h) <sp>*</sp>(:) if(hr) the() Lord() himself() had() not() been() on() our() side,() when() men() rose(h) <b>up</b>(g) a(f)gainst(g gr) us.(ghg)
}

\input{psalter/123/1}

\repant{ant/adjutorium_nostrum.gabc}


\pagebreak[0]


\veant{4}{viii. ii}
\skiplines{1}\gregorioscore{ant/benefac_domine.gabc}

\greannotation{\veformat{Ps. 124}}
\greannotation{\veformat{viii. ii.}}
\skiplines{1}\gabcsnippet{
	(c3) They(e) that(f) (:?) put(hr) their() trust() in() the() Lord() shall() be() even() as() the() mount(h) <b>Zi</b>(i)on(hr h) <sp>*</sp>(:) which(hr) may() not() be() removed,() but stand()eth(h) <b>fast</b>(f) for(h)ev(i)er.(hr h)
}

\input{psalter/124/8}

\repant{ant/benefac_domine.gabc}

\pagebreak[0]



\veant{5}{i. iv}
\skiplines{1}\gregorioscore{ant/facti_sumus.gabc}

\greannotation{\veformat{Ps. 125}}
\greannotation{\veformat{i. iv.}}
\skiplines{1}\gabcsnippet{
	(c4) When(f) the(g) (:?) Lord(hr) turned() again() the() captivity() of(h) <b>Zi</b>(g)on(h) <sp>*</sp>(:) then(hr) were() we() like(h) <b>un</b>(g)to(f) them(g) that(gr) dream.(h)
}

\input{psalter/125/1}

\repant{ant/facti_sumus.gabc}

\instruct{Turn back to the \whiteribbon.}