\begin{multicols}{2}
	O my God, I cry in the daytime, \textbf{but} thou hearest not * and in the night season \textbf{al}so I take no rest.
	
	And thou contin\textbf{u}est holy * O thou \textbf{wor}ship of Israel.
	
	Our \textbf{fa}thers hoped in thee * they trusted in thee, and \textbf{thou} didst deliver them.
	
	They called upon thee, \textbf{and} were holpen * they put their trust in thee, and \textbf{were} not confounded.
	
	But as for me, I am a \textbf{worm} and no man * a very scorn of men, and the out\textbf{cast} of the people.
	
	All they that see me \textbf{laugh} me to scorn * they shoot out their lips, and \textbf{shake} their heads, saying:
	
	He trusted in God, that he \textbf{would} deliver him * let him deliver him, \textbf{if} he will have him.
	
	But thou art he that took me out \textbf{of} my mother's womb * thou wast my hope, when I hanged yet \textbf{up}on my mother's breasts.
	
	I have been left unto thee ev\textbf{er} since I was born * thou art my God ev\textbf{en} from my mother's womb.
	
	O go not from me, for trou\textbf{ble} is hard at hand * and there \textbf{is} none to help me.
	
	Many oxen are \textbf{come} about me * fat bulls of Basan close \textbf{me} in on every side.
	
	They gape u\textbf{pon} me with their mouths * as it were a ramping and \textbf{a} roaring lion.
	
	I am poured out like water and all my \textbf{bones} are out of joint * my heart also in the midst of my body is \textbf{ev}en like melting wax.
	
	My strength is dried up like a potsherd and my tongue \textbf{cleav}eth to my gums * and thou bringest me \textbf{in}to the dust of death.
	
	For many dogs are \textbf{come} about me * and the council of the wicked lay\textbf{eth} siege against me.
	
	They pierced my hands and my feet, I \textbf{may} tell all my bones * they stand staring and \textbf{look}ing upon me.
	
	They part my gar\textbf{ments} among them * and cast lots \textbf{up}on my vesture.
	
	But be not thou \textbf{far} from me, O Lord * thou art my succor, \textbf{haste} thee to help me.
	
	Deliver \textbf{my} soul from the sword * my only one from \textbf{the} power of the dog.
	
	Save me \textbf{from} the lion's mouth * thou hast heard me also from among the \textbf{horns} of the unicorns.
	
	I will declare thy Name un\textbf{to} my brethren * in the midst of the congrega\textbf{tion} will I praise thee.
	
	O praise the Lord, \textbf{ye} that fear him * magnify him, all ye of the seed of Jacob, and fear him, all \textbf{ye} seed of Israel.
	
	For he hath not despised nor abhorred the low \textbf{es}tate of the poor * he hath not hid his face from him, but when he called un\textbf{to} him he heard him.
	
	My praise is of thee in the great \textbf{con}gregation * my vows will I perform in the sight \textbf{of} them that fear him.
	
	The poor shall eat \textbf{and} be satisfied * they that seek after the Lord shall praise him, your heart \textbf{shall} live forever.
	
	All the ends of the world shall remember themselves, and be \textbf{turned} unto the Lord * and all the kindreds of the nations shall \textbf{wor}ship before him.
	
	For the \textbf{king}dom is the Lord's * and he is the governor \textbf{a}mong the people.
	
	All such as be \textbf{fat} upon earth * have \textbf{eat}en, and worshiped.
	
	All they that go down into the dust shall \textbf{kneel} before him * and no man \textbf{hath} quickened his own soul.
	
	My \textbf{seed} shall serve him * they shall be counted unto the Lord for \textbf{a} generation.
	
	They shall come, and shall de\textbf{clare} his righteousness * unto a people that shall be \textbf{born}, whom the Lord hath made.
\end{multicols}