\begin{multicols}{2}
	O my God, I cry in the daytime, but thou \textbf{hear}est not * and in the night season al\textbf{so} I take no rest.
	
	And thou continuest \textbf{ho}ly * O thou wor\textbf{ship} of Israel.
	
	Our fathers \textbf{hoped} in thee * they trusted in thee, and thou \textbf{didst} deliver them.
	
	They called upon thee, and were \textbf{hol}pen * they put their trust in thee, and were \textbf{not} confounded.
	
	But as for me, I am a worm and \textbf{no} man * a very scorn of men, and the outcast \textbf{of} the people.
	
	All they that see me laugh \textbf{me} to scorn * they shoot out their lips, and shake \textbf{their} heads, saying:
	
	He trusted in God, that he would de\textbf{liv}er him * let him deliver him, if \textbf{he} will have him.
	
	But thou art he that took me out of my \textbf{mo}ther's womb * thou wast my hope, when I hanged yet u\textbf{pon} my mother's breasts.
	
	I have been left unto thee ever since \textbf{I} was born * thou art my God even \textbf{from} my mother's womb.
	
	O go not from me, for trouble is \textbf{hard} at hand * and there is \textbf{none} to help me.
	
	Many oxen are come a\textbf{bout} me * fat bulls of Basan close me \textbf{in} on every side.
	
	They gape upon me \textbf{with} their mouths * as it were a ramping and \textbf{roar}ing lion.
	
	I am poured out like water and all my bones are \textbf{out} of joint * my heart also in the midst of my body is ev\textbf{en} like melting wax.
	
	My strength is dried up like a potsherd and my tongue cleaveth \textbf{to} my gums * and thou bringest me in\textbf{to} the dust of death.
	
	For many dogs are come a\textbf{bout} me * and the council of the wicked layeth \textbf{siege} against me.
	
	They pierced my hands and my feet, I may tell \textbf{all} my bones * they stand staring and look\textbf{ing} upon me.
	
	They part my garments a\textbf{mong} them * and cast lots u\textbf{pon} my vesture.
	
	But be not thou far from me, \textbf{O} Lord * thou art my succor, haste \textbf{thee} to help me.
	
	Deliver my soul \textbf{from} the sword * my only one from the \textbf{po}wer of the dog.
	
	Save me from the \textbf{li}on's mouth * thou hast heard me also from among the horns \textbf{of} the unicorns.
	
	I will declare thy Name unto my \textbf{bre}thren * in the midst of the congregation \textbf{will} I praise thee.
	
	O praise the Lord, ye that \textbf{fear} him * magnify him, all ye of the seed of Jacob, and fear him, all ye \textbf{seed} of Israel.
	
	For he hath not despised nor abhorred the low estate \textbf{of} the poor * he hath not hid his face from him, but when he called unto \textbf{him} he heard him.
	
	My praise is of thee in the great congre\textbf{ga}tion * my vows will I perform in the sight of \textbf{them} that fear him.
	
	The poor shall eat and be \textbf{sat}isfied * they that seek after the Lord shall praise him, your heart shall \textbf{live} forever.
	
	All the ends of the world shall remember themselves, and be turned un\textbf{to} the Lord * and all the kindreds of the nations shall wor\textbf{ship} before him.
	
	For the kingdom \textbf{is} the Lord's * and he is the governor a\textbf{mong} the people.
	
	All such as be fat u\textbf{pon} earth * have eat\textbf{en}, and worshiped.
	
	All they that go down into the dust shall kneel be\textbf{fore} him * and no man hath quick\textbf{ened} his own soul.
	
	My seed shall \textbf{serve} him * they shall be counted unto the Lord for a \textbf{gen}eration.
	
	They shall come, and shall declare his \textbf{right}eousness * unto a people that shall be born, \textbf{whom} the Lord hath made.
\end{multicols}