My God, my God, look upon me, why hast thou forsaken me? * and art so far from my health, and from the words of my complaint?

O my God, I cry in the daytime, but thou hearest not * and in the night season also I take no rest.

And thou continuest holy * O thou worship of Israel.

Our fathers hoped in thee * they trusted in thee, and thou didst deliver them.

They called upon thee, and were holpen * they put their trust in thee, and were not confounded.

But as for me, I am a worm and no man * a very scorn of men, and the outcast of the people.

All they who see me laugh me to scorn * they shoot out their lips, and shake their heads, saying:

He trusted in God, that he would deliver him * let him deliver him, if he will have him.

But thou art he who took me out of my mother's womb * thou wast my hope, when I hanged yet upon my mother's breasts.

I have been left unto thee ever since I was born * thou art my God even from my mother's womb.

O go not from me, for trouble is hard at hand * and there is no one to help me.

Many oxen are come about me * fat bulls of Basan close me in on every side.

They gape upon me with their mouths * as it were a ramping and roaring lion.

I am poured out like water and all my bones are out of joint * my heart also in the midst of my body is even like melting wax.

My strength is dried up like a potsherd and my tongue cleaveth to my gums * and thou bringest me into the dust of death.

For many dogs are come about me * and the council of the wicked layeth siege against me.

They pierced my hands and my feet, I may tell all my bones * they stand staring and looking upon me.

They part my garments among them * and cast lots upon my vesture.

But be not thou far from me, O Lord * thou art my succor, haste thee to help me.

Deliver my soul from the sword * my only one from the power of the dog.

Save me from the lion's mouth * thou hast heard me also from among the horns of the unicorns.

I will declare thy Name unto my brethren * in the midst of the congregation will I praise thee.

O praise the Lord, ye who fear him * magnify him, all ye of the seed of Jacob, and fear him, all ye seed of Israel.

For he hath not despised nor abhorred the low estate of the poor * he hath not hid his face from him, but when he called unto him he heard him.

My praise is of thee in the great congregation * my vows will I perform in the sight of them who fear him.

The poor shall eat and be satisfied * they who seek after the Lord shall praise him, your heart shall live forever.

All the ends of the world shall remember themselves, and be turned unto the Lord * and all the kindreds of the nations shall worship before him.

For the kingdom is the Lord's * and he is ruler among the people.

All such as be fat upon earth * have eaten, and worshipped.

All they who go down into the dust shall kneel before him * and no man hath quickened his own soul.

My seed shall serve him * they shall be counted unto the Lord for a generation.

They shall come, and shall declare his righteousness * unto a people who shall be born, whom the Lord hath made.