\begin{multicols}{2}
	They are corrupt, and become abominable in their \textbf{do}ings * there are none who doeth \textbf{good}, not even one.
	
	The Lord looked down from heaven upon the children \textbf{of} men * to see if there were any who would understand, \textbf{and} seek after God.
	
	But they are all gone off the way, they are altogether become a\textbf{bomin}able * there are none who doeth \textbf{good}, not even one.
	
	Their throat is an open sepulcher, with their tongues they \textbf{have} deceived * the poison of asps \textbf{is} under their lips.
	
	Their mouth is full of cursing and \textbf{bit}terness * their feet are \textbf{swift} to shed blood.
	
	Destruction and unhappiness is in their ways, and the way of peace have they \textbf{not} known * there is no fear of \textbf{God} before their eyes.
	
	Have they no knowledge, that they are all such workers of \textbf{e}vil * eating up my people as they were bread, and call \textbf{not} upon the Lord?
	
	There were they brought in great fear, even where no \textbf{fear} was * for God is in the generation \textbf{of} the righteous.
	
	As for you, ye have made a mock at the counsel \textbf{of} the poor * because he putteth \textbf{his} trust in the Lord.
	
	Who shall give salvation unto Israel out of Zion? when the Lord turneth the captivity of his \textbf{peo}ple * then shall Jacob rejoice, and Is\textbf{ra}el shall be glad.
	
	Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}