\begin{multicols}{2}
	Ye that stand in the \textbf{house} of \textbf{the} Lord * in the courts \textbf{of} the house of our God.
	
	O praise the Lord, for the \textbf{Lord} is \textbf{gra}cious * O sing praises unto his Name, \textbf{for} it is lovely.
	
	For why? the Lord hath chosen \textbf{Ja}cob un\textbf{to} himself * and Israel for \textbf{his} own possession.
	
	For I \textbf{know} that the \textbf{Lord} is great * and that our \textbf{Lord} is above all gods.
	
	Whatsoever the Lord pleased, that did he in \textbf{hea}ven, and \textbf{in} earth * and in the sea, and \textbf{in} all deep places.
	
	He bringeth forth the clouds from the \textbf{ends} of \textbf{the} world * and sendeth forth lightnings with the rain, bringing the winds \textbf{out} of his treasures.
	
	He smote the \textbf{first}born of \textbf{E}gypt * from man \textbf{ev}en unto the beasts.
	
	He hath sent tokens and wonders into the midst of thee, O thou \textbf{land} of \textbf{E}gypt * upon Pharaoh, \textbf{and} all his servants.
	
	He smote \textbf{di}verse \textbf{na}tions * \textbf{and} slew mighty kings.
	
	Sehon king of the Amorites; and Og the \textbf{king} of \textbf{Ba}san * and all the \textbf{king}doms of Canaan.
	
	And gave their land to \textbf{be} a \textbf{her}itage * even a heritage unto Is\textbf{ra}el his people.
	
	Thy Name, O Lord, en\textbf{dur}eth for \textbf{ev}er * so doth thy memorial, O Lord, from one genera\textbf{tion} to another.
	
	For the Lord will a\textbf{venge} his \textbf{peo}ple * and be gracious \textbf{un}to his servants.
	
	As for the images of the heathen, they are but \textbf{sil}ver \textbf{and} gold * \textbf{the} work of men's hands.
	
	They have \textbf{mouths}, and \textbf{speak} not * eyes have \textbf{they}, but they see not.
	
	They have ears, and \textbf{yet} they \textbf{hear} not * neither is there \textbf{a}ny breath in their mouths.
	
	They that make them are \textbf{like} un\textbf{to} them * and so are all they \textbf{that} put their trust in them.
	
	Praise the Lord, ye \textbf{house} of \textbf{Is}rael * praise the Lord, \textbf{ye} house of Aaron.
	
	Praise the Lord, ye \textbf{house} of \textbf{Le}vi * ye that \textbf{fear} the Lord, praise the Lord.
	
	Praised be the Lord \textbf{out} of \textbf{Zi}on * who dwel\textbf{leth} at Jerusalem.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world \textbf{with}out end. Amen.
\end{multicols}