\begin{multicols}{2}
	Before the mountains were brought forth, or ever the earth and the world \textbf{were} made * thou art God from everlasting, and \textbf{world} without end.
	
	Thou turnest man to des\textbf{truc}tion * again thou sayest, Come again, ye \textbf{child}ren of men.
	
	For a thousand years in thy sight are but as yes\textbf{ter}day * that is past as \textbf{a} watch in the night.
	
	As soon as thou scatterest them they are even as \textbf{a}sleep * and fade away sud\textbf{den}ly like the grass.
	
	In the morning it is green, and grow\textbf{eth} up * but in the evening is cut down, dried \textbf{up}, and withered.
	
	For we consume away in thy dis\textbf{plea}sure * and are afraid at thy wrathful \textbf{in}dignation.
	
	Thou hast set our misdeeds be\textbf{fore} thee * and our secret sins in the light \textbf{of} thy countenance.
	
	For when thou art angry all our days \textbf{are} gone * we bring our years to an end, as it were \textbf{a} tale that is old.
	
	The days of our age are threescore and ten, and though men be so strong they come to four\textbf{score} years * yet  is their strength then but labor and sorrow, so soon passeth it a\textbf{way} and we are gone.
	
	But who regardeth the power of \textbf{thy} wrath * for even thereafter as a man feareth, so is \textbf{thy} displeasure.
	
	So teach us to number \textbf{our} days * that we may apply our hearts \textbf{un}to wisdom.
	
	Turn thee again, O Lord, at \textbf{the} last * and be gracious un\textbf{to} thy servants.
	
	O satisfy us soon with thy \textbf{mer}cy * so shall we rejoice and be glad all \textbf{the} days of our life.
	
	Comfort us again now, after the time that thou hast \textbf{plagued} us * and for the years wherein we have suf\textbf{fered} adversity.
	
	Shew thy servants \textbf{thy} work * and their chil\textbf{dren} thy glory.
	
	And the glorious majesty of the Lord our God be u\textbf{pon} us * prosper thou the work of our hands, O prosper \textbf{thou} our handiwork.
	
	Glory be to the Father, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out}end. Amen.
\end{multicols}