Lord, thou hast been our refuge * from one generation to another.

Before the mountains were brought forth, or ever the earth and the world were made * thou art God from everlasting, and world without end.

Thou turnest man to destruction * again thou sayest, Come again, ye children of men.

For a thousand years in thy sight are but as yesterday * seeing that is past as a watch in the night.

As soon as thou scatterest them they are even as a sleep * and fade away suddenly like the grass.

In the morning it is green, and groweth up * but in the evening is cut down, dried up, and withered.

For we consume away in thy displeasure * and are afraid at thy wrathful indignation.

Thou hast set our misdeeds before thee * and our secret sins in the light of thy countenance.

For when thou art angry all our days are gone * we bring our years to an end, as it were a tale that is old.

The days of our age are threescore and ten, and though men be so strong they come to fourscore years * yet it is their strength then but labor and sorrow, so soon passeth it away and we are gone.

But who regardeth the power of thy wrath * for even thereafter as a man feareth, so is thy displeasure.

So teach us to number our days * that we may apply our hearts unto wisdom.

Turn thee again, O Lord, at the last * and be gracious unto thy servants.

O satisfy us soon with thy mercy * so shall we rejoice and be glad al the days of our life.

Comfort us again now, after the time that thou hast plagued us * and for the years wherein we have suffered adversity.

Shew thy servants thy work * and their children thy glory.

And the glorious majesty of the Lord our God be upon us * prosper thou the work of our hands, O prosper thou our handiwork.