\begin{multicols}{2}
	My doctrine shall drop as the rain, my speech shall \textbf{dis}till as the dew * as the small rain upon the tender herb, and as the \textbf{show}ers upon the grass.
	
	Because I will proclaim \textbf{the} Name of the Lord * ascribe ye \textbf{great}ness unto our God.
	
	He is the Rock, his \textbf{work} is perfect * for all \textbf{his} ways are judgment.
	
	A God of truth and with\textbf{out} iniquity * \textbf{just} and right is he.
	
	They have corrupted themselves and \textbf{are} not his children * they are a perverse and croo\textbf{ked} generation.
	
	Do ye thus requite the Lord, O foolish \textbf{peo}ple and unwise? * is he not thy Fa\textbf{ther} that hath bought thee?
	
	Hath \textbf{he} not made thee? * \textbf{and} established thee?
	
	Remember the days of old, consider the years of many \textbf{gen}erations * ask thy father, and he will shew thee; thy elders, \textbf{and} they will tell thee.
	
	When the most High divided to the nations \textbf{their} inheritance * when he separated \textbf{the} sons of Adam.
	
	He set the bounds \textbf{of} the people * according to the number of the \textbf{child}ren of Israel.
	
	For the Lord's portion \textbf{is} his people * Jacob is the lot \textbf{of} his inheritance.
	
	He found him in a desert land, and in the waste \textbf{how}ling wilderness * he led him about, he instructed him, he kept him as \textbf{the} apple of his eye.
	
	As an eagle stirreth up her nest, fluttereth over her young, spread\textbf{eth} abroad her wings * taketh them, \textbf{bear}eth them on her wings.
	
	So the Lord a\textbf{lone} did lead him * and there \textbf{was} no strange god with him.
	
	He made him ride on the high places of the earth, that he might eat the \textbf{in}crease of the fields * and he made him to suck honey out of the rock, and oil \textbf{out} of the flinty rock.
	
	Butter of \textbf{kine}, and milk of sheep * with fat of lambs, and rams of \textbf{the} breed of Basan.
	
	And goats, with the fat of \textbf{kid}neys of wheat * and thou didst drink \textbf{the} pure blood of the grape.
	
	But Isra\textbf{el} waxed fat, and kicked * thou art waxen fat, thou art grown thick, thou art \textbf{co}vered with fatness.
	
	Then he forsook \textbf{God} who made him * and lightly esteemed the Rock \textbf{of} his salvation.
	
	They provoked him to jealou\textbf{sy} with strange gods * with abominations provoked \textbf{they} him to anger.
	
	They sacrificed unto \textbf{de}vils, not to God * to \textbf{gods} whom they knew not.
	
	To new gods \textbf{that} came newly up * whom \textbf{your} fathers feared not.
	
	Of the Rock that begat thee thou \textbf{art} unmindful * and hast forgot\textbf{ten} God who formed thee.
	
	And when the Lord saw it, \textbf{he} abhorred them * because of the provoking of his sons, \textbf{and} of his daughters.
	
	And he said, I will hide my face from them, I will see \textbf{what} their end shall be * for they are a very perverse generation, chil\textbf{dren} in whom is no faith.
	
	They have moved me to jealousy with that \textbf{which} is not God * they have provoked me to an an\textbf{ger} with their vanities.
	
	And I will move them to jealousy with those which are \textbf{not} a people * I will provoke them to anger with \textbf{a} foolish nation.
	
	For a fire is kindled in mine anger, and shall burn un\textbf{to} the lowest hell * and shall consume the earth with her increase, and set on fire the \textbf{foun}dations of the earth.
	
	I will heap mis\textbf{chiefs} upon them * I will spend mine \textbf{ar}rows upon them.
	
	They shall be \textbf{burnt} with hunger * and devoured with burning heart, and with \textbf{bit}ter destruction.
	
	I will also send the teeth of \textbf{beasts} upon them * with the poison \textbf{of} serpents of the dust.
	
	The sword without, and terror within, shall destroy both the young man \textbf{and} the virgin * the child also with \textbf{the} man of grey hairs.
	
	I said, I would scatter them \textbf{in}to corners * I would make the remembrance of them to \textbf{cease} from among men.
	
	Were it not that I feared the wrath \textbf{of} the enemy * lest their adversaries should be\textbf{have} themselves proudly.
	
	And lest they should \textbf{say}, Our hand is high * and the Lord \textbf{hath} not done all this.
	
	For they are a nation \textbf{void} of counsel * neither is there any un\textbf{der}standing in them.
	
	O that they were wise, that they \textbf{un}derstood this * that they would con\textbf{si}der their latter end.
	
	How should one chase a thousand, and two \textbf{thou}sand put to flight * except their Rock had sold them, and \textbf{the} Lord had shut them up?
	
	For their rock \textbf{is} not as our Rock * even our enemies them\textbf{selves} being judges.
	
	For their vine is of the \textbf{vine} of Sodom * and of the \textbf{fields} of Gomorrah.
	
	Their \textbf{grapes} are grapes of gall * their \textbf{clus}ters are bitter.
	
	Their wine is the poi\textbf{son} of dragons * and the \textbf{cruel} venom of asps.
	
	Is not this laid up in store with me, and sealed up a\textbf{mong} my treasures *  to me belongeth \textbf{ven}geance and recompense.
	
	Their foot shall slide in due time, for the day of their cala\textbf{mi}ty is at hand * and the things that shall come \textbf{up}on them make haste.
	
	For the Lord shall judge his people, and repent himself \textbf{for} his servants * when he seeth that their power is gone, and there \textbf{is} none shut up or left.
	
	And he shall say, Where are their gods, their rock in \textbf{whom} they trusted? * which did eat of the fat of their sacrifices, and drank the \textbf{wine} of their offerings.
	
	Let them \textbf{rise} and help you * and \textbf{be} your protection.
	
	See now that I, \textbf{ev}en I, am he * and there \textbf{is} no god with me.
	
	I kill, and I make alive; \textbf{I} wound and I heal * neither is there any who can de\textbf{li}ver out of my hand.
	
	For I lift up my \textbf{hand} to heaven * and say, \textbf{I} live forever.
	
	If I whet my glittering sword, and mine hand take \textbf{hold} on judgment * I will render vengeance to mine enemies, and I will re\textbf{ward} them who hate me.
	
	I will make mine \textbf{ar}rows drunk with blood * and my \textbf{sword} shall devour flesh.
	
	And that with the blood of the slain and \textbf{of} the captives * from the beginning of revenges \textbf{up}on the enemy.
	
	Rejoice, O ye nations, \textbf{with} his people * for he will avenge the \textbf{blood} of his servants.
	
	And will render vengeance to his \textbf{ad}versaries * and will be merciful unto his land \textbf{and} to his people.
	
	Glory be to the Fa\textbf{ther}, and to the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er shall be * world \textbf{with}out end. Amen.
\end{multicols}