Give ear, O ye heavens, and I will speak * and hear, O earth, the words of my mouth.

My doctrine shall drop as the rain, my speech shall distill as the dew * as the small rain upon the tender herb, and as the showers upon the grass.

Because I will proclaim the Name of the Lord * ascribe ye greatness unto our God.

He is the Rock, his work is perfect * for all his ways are judgment.

A God of truth and without iniquity * just and right is he.

They have corrupted themselves and are not his children * they are a perverse and crooked generation.

Do ye thus requite the Lord, O foolish people and unwise? * is he not thy Father that hath bought thee?

Hath he not made thee? * and established thee?

Remember the days of old, consider the years of many generations * ask thy father, and he will shew thee; thy elders, and they will tell thee.

When the most High divided to the nations their inheritance * when he separated the sons of Adam.

He set the bounds of the people * according to the number of the children of Israel.

For the Lord's portion is his people * Jacob is the lot of his inheritance.

He found him in a desert land, and in the waste howling wilderness * he led him about, he instructed him, he kept him as the apple of his eye.

As an eagle stirreth up her nest, fluttereth over her young, spreadeth abroad her wings * taketh them, beareth them on her wings.

So the Lord alone did lead him * and there was no strange god with him.

He made him ride on the high places of the earth, that he might eat the increase of the fields * and he made him to suck honey out of the rock, and oil out of the flinty rock.

Butter of kine, and milk of sheep * with fat of lambs, and rams of the breed of Basan.

And goats, with the fat of kidneys of wheat * and thou didst drink the pure blood of the grape.

But Israel waxed fat, and kicked * thou art waxen fat, thou art grown thick, thou art covered with fatness.

Then he forsook God who made him * and lightly esteemed the Rock of his salvation.

They provoked him to jealousy with strange gods * with abominations provoked they him to anger.

They sacrificed unto devils, not to God * to gods whom they knew not.

To new gods that came newly up * whom your fathers feared not.

Of the Rock that begat thee thou art unmindful * and hast forgotten God who formed thee.

And when the Lord saw it, he abhorred them * because of the provoking of his sons, and of his daughters.

And he said, I will hide my face from them, I will see what their end shall be * for they are a very froward generation, children in whom is no faith.

They have moved me to jealousy with that which is not God * they have provoked me to an anger with their vanities.

And I will move them to jealousy with those which are not a people * I will provoke them to anger with a foolish nation.

For a fire is kindled in mine anger, and shall burn unto the lowest hell * and shall consume the earth with her increase, and set on fire the foundations of the earth.

I will heap mischiefs upon them * I will spend mine arrows upon them.

They shall be burnt with hunger * and devoured with burning heart, and with bitter destruction.

I will also send the teeth of beasts upon them * with the poison of serpents of the dust.

The sword without, and terror within, shall destroy both the young man and the virgin * the child also with the man of grey hairs.

I said, I would scatter them into corners * I would make the remembrance of them to cease from among men.

Were it not that I feared the wrath of the enemy * lest their adversaries should behave themselves strangely.

And lest they should say, Our hand is high * and the Lord hath not done all this.

For they are a nation void of counsel * neither is there any understanding in them.

O that they were wise, that they understood this * that they would consider their latter end.

How should one chase a thousand, and two thousand put to flight * except their Rock had sold them, and the Lord had shut them up?

For their rock is not as our Rock * even our enemies themselves being judges.

For their vine is of the vine of Sodom * and of the fields of Gomorrah.

Their grapes are grapes of gall * their clusters are bitter.

Their wine is the poison of dragons * and the cruel venom of asps.

Is not this laid up in store with me, and sealed up among my treasures *  to me belongeth vengeance and recompense.

Their foot shall slide in due time, for the day of their calamity is at hand * and the things that shall come upon them make haste.

For the Lord shall judge his people, and repent himself for his servants * when he seeth that their power is gone, and there is none shut up or left.

And he shall say, Where are their gods, their rock in whom they trusted? * which did eat of the fat of their sacrifices, and drank the wine of their offerings.

Let them rise and help you * and be your protection.

See now that I, even I, am he * and there is no god with me.

I kill, and I make alive; I wound and I heal * neither is there any who can deliver out of my hand.

For I lift up my hand to heaven * and say, I live forever.

If I whet my glittering sword, and mine hand take hold on judgment * I will render vengeance to mine enemies, and I will reward them who hate me.

I will make mine arrows drunk with blood * and my sword shall devour flesh.

And that with the blood of the slain and of the captives * from the beginning of revenges upon the enemy.

Rejoice, O ye nations, with his people * for he will avenge the blood of his servants.

And will render vengeance to his adversaries * and will be merciful unto his land and to his people.