\begin{multicols}{2}
	O hearken thou unto the voice of my calling, my \textbf{King} and \textbf{my} God * for unto thee \textbf{will} I make \textbf{my} prayer.
	
	My voice shalt thou \textbf{hear} be\textbf{times}, O Lord * early in the morning will I direct my prayer unto thee, \textbf{and} will \textbf{look} up.
	
	For thou art the God that hast no \textbf{plea}sure in \textbf{wick}edness * neither shall any \textbf{ev}il \textbf{dwell} with thee.
	
	Such as be foolish shall not \textbf{stand} in \textbf{thy} sight * for thou hatest all them \textbf{that} work \textbf{van}ity.
	
	Thou shalt destroy them \textbf{that} speak \textbf{ly}ing * the Lord will abhor both the blood-thirsty \textbf{and} de\textbf{ceit}ful man.
	
	But as for me, I will come into thine house, even upon the multitude \textbf{of} thy \textbf{mer}cy * and in thy fear will I worship toward thy \textbf{ho}ly \textbf{tem}ple.
	
	Lead me, O Lord, in thy righteousness, be\textbf{cause} of mine \textbf{en}emies * make thy way \textbf{plain} before \textbf{my} face.
	
	For there is no \textbf{faith}fulness \textbf{in} his mouth * their inward parts are \textbf{ve}ry \textbf{wick}edness.
	
	Their throat is an \textbf{op}en \textbf{se}pulcher * they \textbf{flat}ter \textbf{with} their tongue.
	
	Destroy thou them, O God, let them perish through their own i\textbf{ma}gi\textbf{na}tions * cast them out in the multitude of their ungodliness, for they have re\textbf{belled} a\textbf{gainst} thee.
	
	And let all them that put their \textbf{trust} in \textbf{thee} rejoice * they shall ever be giving of thanks, because thou defendest them, they that love thy Name shall be \textbf{joy}ful \textbf{in} thee.
	
	For thou, Lord, wilt give thy blessing un\textbf{to} the \textbf{right}eous * and with thy favorable kindness wilt thou de\textbf{fend} him as \textbf{with} a shield.
\end{multicols}