\begin{multicols}{2}
	O hearken thou unto the voice of my calling, my King \textbf{and} my God * for unto thee \textbf{will} I make my prayer.
	
	My voice shalt thou hear be\textbf{times}, O Lord * early in the morning will I direct my prayer unto thee, \textbf{and} will look up.
	
	For thou art the God that hast no pleasure in \textbf{wick}edness * neither shall any \textbf{e}vil dwell with thee.
	
	Such as be foolish shall not stand \textbf{in} thy sight * for thou hatest all them \textbf{that} work vanity.
	
	Thou shalt destroy them that speak \textbf{ly}ing * the Lord will abhor both the blood-thirsty \textbf{and} deceitful man.
	
	But as for me, I will come into thine house, even upon the multitude of thy \textbf{mer}cy * and in thy fear will I worship toward thy \textbf{ho}ly temple.
	
	Lead me, O Lord, in thy righteousness, because of mine \textbf{en}emies * make thy way \textbf{plain} before my face.
	
	For there is no faithfulness \textbf{in} his mouth * their inward parts are \textbf{ve}ry wickedness.
	
	Their throat is an open \textbf{se}pulcher * they \textbf{flat}ter with their tongue.
	
	Destroy thou them, O God, let them perish through their own imagi\textbf{na}tions * cast them out in the multitude of their ungodliness, for they have rebel\textbf{led} against thee.
	
	And let all them that put their trust in \textbf{thee} rejoice * they shall ever be giving of thanks, because thou defendest them, they that love thy Name shall be \textbf{joy}ful in thee.
	
	For thou, Lord, wilt give thy blessing unto the \textbf{righ}teous * and with thy favorable kindness wilt thou defend \textbf{him} as with a shield.
	
	Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}