\begin{multicols}{2}
	O do well unto thy \textbf{ser}vant * that I may \textbf{live} and keep thy word.
	
	Open thou \textbf{mine} eyes * that I may see the wond\textbf{rous} things of thy law.
	
	I am a stranger u\textbf{pon} earth * O hide not thy com\textbf{mand}ments from me.
	
	My soul breaketh out for the very fervent \textbf{de}sire * that it hath always un\textbf{to} thy judgments.
	
	Thou hast rebuked \textbf{the} proud * and cursed are they that do err from \textbf{thy} commandments.
	
	O turn from me shame and \textbf{re}buke * for I have kept thy \textbf{tes}timonies.
	
	Princes also did sit and speak a\textbf{gainst} me * but thy servant is occupied \textbf{in} thy statutes.
	
	For thy testimonies are my \textbf{de}light * \textbf{and} my counselors.
	
	My soul cleaveth to \textbf{the} dust * O quicken thou me, ac\textbf{cord}ing to thy word.
	
	I have acknowledged my ways, and thou heard\textbf{est} me * O teach \textbf{me} thy statutes.
	
	Make me to understand the way of thy com\textbf{mand}ments * and so shall I talk \textbf{of} thy wondrous works.
	
	My soul melteth away for very hea\textbf{vi}ness * comfort thou me ac\textbf{cord}ing to thy word.
	
	Take from me the way of \textbf{ly}ing * and cause thou me to \textbf{make} much of thy law.
	
	I have chosen the way \textbf{of} truth * and thy judgments have I \textbf{laid} before me.
	
	I have stuck unto thy testi\textbf{mo}nies * O \textbf{Lord}, confound me not.
	
	I will run the way of thy com\textbf{mand}ments * when thou hast set my \textbf{heart} at liberty.
	
	Glory be to the Father, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}