\begin{multicols}{2}
	\textbf{Open} thou mine eyes * that I may see the \textbf{won}drous things of thy law.
	
	I am a stran\textbf{ger} upon earth * O hide not thy \textbf{com}mandments from me.
	
	My soul breaketh out for the very \textbf{fer}vent desire * that it hath always \textbf{un}to thy judgments.
	
	Thou \textbf{hast} rebuked the proud * and cursed are they that do err \textbf{from} thy commandments.
	
	O turn from me \textbf{shame} and rebuke * for I have kept \textbf{thy} testimonies.
	
	Princes also did sit and \textbf{speak} against me * but thy servant is occu\textbf{pied} in thy statutes.
	
	For thy testimo\textbf{nies} are my delight * \textbf{and} my counselors.
	
	My soul \textbf{clea}veth to the dust * O quicken thou me, \textbf{ac}cording to thy word.
	
	I have acknowledged my ways, \textbf{and} thou heardest me * O \textbf{teach} me thy statutes.
	
	Make me to understand the way of \textbf{thy} commandments * and so shall I \textbf{talk} of thy wondrous works.
	
	My soul melteth away for \textbf{ve}ry heaviness * comfort thou me ac\textbf{cord}ing to thy word.
	
	Take from me the \textbf{way} of lying * and cause thou me \textbf{to} make much of thy law.
	
	I have cho\textbf{sen} the way of truth * and thy judgments have \textbf{I} laid before me.
	
	I have stuck unto thy \textbf{tes}timonies * \textbf{O} Lord, confound me not.
	
	I will run the way of \textbf{thy} commandments * when thou hast set \textbf{my} heart at liberty.
	
	Glory be to the Fa\textbf{ther}, and to the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er shall be * world \textbf{with}out end. Amen.
\end{multicols}