\begin{multicols}{2}
	O do well un\textbf{to} thy servant * that I may live and keep \textbf{thy} word.
	
	\textbf{---} Open thou mine eyes * that I may see the wondrous things of \textbf{thy} law.
	
	I am a stran\textbf{ger} upon earth * O hide not thy commandments from me.
	
	My soul breaketh out for the very fer\textbf{vent} desire * that it hath always unto thy judg\textbf{ments}.
	
	Thou \textbf{hast} rebuked the proud * and cursed are they who do err from thy command\textbf{ments}.
	
	O turn from \textbf{me} shame and rebuke * for I have kept thy testimon\textbf{ies}.
	
	Princes also did sit and \textbf{speak} against me * but thy servant is occupied in thy stat\textbf{utes}.
	
	For thy testimon\textbf{ies} are my delight * and my coun\textbf{se}lors.
	
	My soul \textbf{cleav}eth to the dust * O quicken thou me, according to \textbf{thy} word.
	
	I have acknowledged my ways, \textbf{and} thou heardest me * O teach me thy stat\textbf{utes}.
	
	Make me to understand the way of \textbf{thy} commandments * and so shall I talk of thy wond\textbf{rous} works.
	
	My soul melteth away for \textbf{ve}ry heaviness * comfort thou me according to \textbf{thy} word.
	
	Take from me the \textbf{way} of lying * and cause thou me to make much of \textbf{thy} law.
	
	I have cho\textbf{sen} the way of truth * and thy judgments have I laid before \textbf{me}.
	
	I have stuck unto thy \textbf{tes}timonies * O Lord, confound \textbf{me} not.
	
	I will run the way of \textbf{thy} commandments * when thou hast set my heart at lib\textbf{er}ty.
\end{multicols}