\greannotation{\veformat{Hymn.}}
\greannotation{\veformat{i.}}

\vecomment{Eterne rerum Conditor}

\gregorioscore{hymn/eterne_rerum_conditor.gabc}

\begin{multicols}{1}
	Now the shrill cock proclaims the day,\\
	And calls the sun's awak'ning ray,\\
	The wand'ring pilgrim's guiding light,\\
	That marks the watches night by night.
	
	Roused at the note, the morning star,\\
	Heav'n's dusky veil uplifts a far:\\
	Night's vagrant bands no longer roam,\\
	But from their dark ways hie them home.
	
	Th'encouraged sailor's fears are o'er;\\
	The foaming billows rage no more:\\
	Lo! e'en the very Church's Rock\\
	Melts at the crowing of the cock.
	
	O let us then all ardent rise;\\
	The cock rebukes our slumb'ring eyes,\\
	Bestirs who still in sleep would lie,\\
	And shames who would their Lord deny.
	
	New hope his clar'on note awakes,\\
	Sickness the feeble frame forsakes,\\
	The robber sheathes his lawless sword,\\
	Faith to the fallen is restored.
	
	Look on us, Jesus, when we fall,\\
	And with thy look our souls recall:\\
	If thou but look, our sins are gone,\\
	And with due tears our pardon won.
	
	Shed through our hearts thy piercing ray,\\
	Our souls' dull slumber drive away:\\
	Thy name be first on every tongue,\\
	To thee our earl'est praises sung.
	
	All laud to God the Father be,\\
	All praise, Eternal Son, to thee;\\
	All glory, as is ever meet,\\
	To God the Holy Paraclete.
	
	\skiplines{1}\gresetinitiallines{0}\gabcsnippet{(cb4) A(de)men.(dcd)}\gresetinitiallines{1}
\end{multicols}

\gresetinitiallines{0}
\skiplines{1}\gabcsnippet{
	(c4) <sp>v</sp> The(h) Lord(h) is(f) King.(g)
	<sp>r</sp>(::) He(h) hath(h) put(h) on(h) glor(h)i(h)ous(h) ap(h)par(h)el,(h) a(h)le(h)lu(f)ia.(f)
}
\gresetinitiallines{1}