\begin{multicols}{2}
	Yea, even unto thee \textbf{do} I call * help me, and I shall keep thy tes\textbf{ti}monies.
	
	Early in the morning do I cry \textbf{un}to thee * for in thy \textbf{word} is my trust.
	
	Mine eyes prevent the night \textbf{watch}es * that I might be occu\textbf{pied} in thy word.
	
	Hear my voice, O Lord, according unto thy loving-\textbf{kind}ness * quicken me, according to \textbf{thy} judgments.
	
	They draw nigh that of malice perse\textbf{cute} me * and are \textbf{far} from thy law.
	
	Be thou nigh at \textbf{hand}, O Lord * for all thy command\textbf{ments} are true.
	
	As concerning thy testimonies, I have \textbf{known} long since * that thou hast grounded them \textbf{for}ever.
	
	O consider mine adversity, and de\textbf{li}ver me * for I do not \textbf{for}get thy law.
	
	Avenge thou my cause, and de\textbf{li}ver me * quicken me accord\textbf{ing} to thy word.
	
	Salvation is far from the un\textbf{god}ly * for they regard not \textbf{thy} statutes.
	
	Great is thy mercy, \textbf{O} Lord * quicken me, \textbf{as} thou art wont.
	
	Many there are that trouble me and perse\textbf{cute} me * yet I do not swerve from thy tes\textbf{ti}monies.
	
	It grieveth me when I see the trans\textbf{gres}sors * because they \textbf{keep} not thy law.
	
	Consider, O Lord, how I love thy com\textbf{mand}ments * O quicken me, according to thy lov\textbf{ing}-kindness.
	
	Thy word is true from ever\textbf{last}ing * all the judgments of thy righteousness endure \textbf{for}evermore.
	
	Glory be to the Father, and \textbf{to} the Son * and to the Ho\textbf{ly} Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world without \textbf{end}. Amen.
\end{multicols}