\begin{multicols}{2}
	Yea, even unto \textbf{thee} do \textbf{I} call * help me, and I shall keep thy tes\textbf{ti}monies.
	
	Early in the morning do \textbf{I} cry \textbf{un}to thee * for in thy word \textbf{is} my trust.
	
	Mine eyes prevent \textbf{the} night \textbf{watch}es * that I might be occupied \textbf{in} thy word.
	
	Hear my voice, O Lord, according unto thy \textbf{lov}ing-\textbf{kind}ness * quicken me, according to \textbf{thy} judgments.
	
	They draw nigh who of malice \textbf{per}se\textbf{cute} me * and are far \textbf{from} thy law.
	
	Be thou \textbf{nigh} at hand, \textbf{O} Lord * for all thy command\textbf{ments} are true.
	
	As concerning thy testimonies, \textbf{I} have \textbf{known} long since * that thou hast grounded them \textbf{for}ever.
	
	O consider mine adversi\textbf{ty}, and de\textbf{li}ver me * for I do not \textbf{for}get thy law.
	
	Avenge thou my \textbf{cause}, and de\textbf{liv}er me * quicken me accord\textbf{ing} to thy word.
	
	Salvation is far \textbf{from} the un\textbf{god}ly * for they regard not \textbf{thy} statutes.
	
	Great is thy \textbf{mer}cy, \textbf{O} Lord * quicken me, \textbf{as} thou art wont.
	
	Many there are who trouble me and \textbf{per}se\textbf{cute} me * yet I do not swerve from thy tes\textbf{ti}monies.
	
	It grieveth me when I \textbf{see} the trans\textbf{gres}sors * because they \textbf{keep} not thy law.
	
	Consider, O Lord, how I love \textbf{thy} com\textbf{mand}ments * O quicken me, according to thy lo\textbf{ving}-kindness.
	
	Thy word is true from \textbf{ev}er\textbf{last}ing * all the judgments of thy righteousness endure \textbf{for}evermore.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the Ho\textbf{ly} Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world without \textbf{end}. Amen.
\end{multicols}