\begin{multicols}{2}
	Yea, even un\textbf{to} thee do I call * help me, and I shall keep \textbf{thy} testimonies.
	
	Early in the morning do I \textbf{cry} unto thee * for \textbf{in} thy word is my trust.
	
	Mine eyes prevent \textbf{the} night watches * that I might be \textbf{oc}cupied in thy word.
	
	Hear my voice, O Lord, according unto thy \textbf{lov}ing-kindness * quicken me, accor\textbf{ding} to thy judgments.
	
	They draw nigh that of malice \textbf{per}secute me * \textbf{and} are far from thy law.
	
	Be thou \textbf{nigh} at hand, O Lord * for all thy \textbf{com}mandments are true.
	
	As concerning thy testimonies, \textbf{I} have known long since * that thou hast ground\textbf{ed} them forever.
	
	O consider mine adversity, \textbf{and} deliver me * for I \textbf{do} not forget thy law.
	
	Avenge thou my cause, \textbf{and} deliver me * quicken me \textbf{ac}cording to thy word.
	
	Salvation is far from \textbf{the} ungodly * for they re\textbf{gard} not thy statutes.
	
	Great is thy \textbf{mer}cy, O Lord * qui\textbf{cken} me, as thou art wont.
	
	Many there are that trouble me and \textbf{per}secute me * yet I do not swerve from \textbf{thy} testimonies.
	
	It grieveth me when I see \textbf{the} transgressors * be\textbf{cause} they keep not thy law.
	
	Consider, O Lord, how I love \textbf{thy} commandments * O quicken me, according to \textbf{thy} loving-kindness.
	
	Thy word is true from \textbf{ev}erlasting * all the judgments of thy righteousness \textbf{en}dure forevermore.
	
	Glory be to the Fath\textbf{er}, and to the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now and \textbf{ev}er shall be * world \textbf{with}out end. Amen.
\end{multicols}