\begin{multicols}{2}
	Yea, even unto \textbf{thee} do \textbf{I} call * help me, and I shall keep thy \textbf{tes}ti\textbf{mon}ies.
	
	Early in the morning do I \textbf{cry} un\textbf{to} thee * for in thy \textbf{word} is \textbf{my} trust.
	
	Mine eyes pre\textbf{vent} the night \textbf{wat}ches * that I might be occu\textbf{pied} in \textbf{thy} word.
	
	Hear my voice, O Lord, according unto thy \textbf{lov}ing-\textbf{kind}ness * quicken me, according \textbf{to} thy \textbf{judg}ments.
	
	They draw nigh who of malice \textbf{per}se\textbf{cute} me * and are \textbf{far} from \textbf{thy} law.
	
	Be thou \textbf{nigh} at hand, \textbf{O} Lord * for all thy com\textbf{mand}ments \textbf{are} true.
	
	As concerning thy testimonies, \textbf{I} have known \textbf{long} since * that thou hast grounded \textbf{them} for\textbf{ev}er.
	
	O consider mine adversity, and \textbf{de}li\textbf{ver} me * for I do \textbf{not} for\textbf{get} thy law.
	
	Avenge thou my cause, \textbf{and} de\textbf{li}ver me * quicken me ac\textbf{cord}ing \textbf{to} thy word.
	
	Salvation is far from \textbf{the} un\textbf{god}ly * for they re\textbf{gard} not thy \textbf{stat}utes.
	
	Great is thy \textbf{mer}cy, \textbf{O} Lord * quicken \textbf{me}, as thou \textbf{art} wont.
	
	Many there are who trouble me and \textbf{per}se\textbf{cute} me * yet I do not swerve from thy \textbf{tes}ti\textbf{mo}nies.
	
	It grieveth me when I \textbf{see} the trans\textbf{gres}sors * because they \textbf{keep} not \textbf{thy} law.
	
	Consider, O Lord, how I \textbf{love} thy com\textbf{mand}ments * O quicken me, according to thy \textbf{lov}ing-\textbf{kind}ness.
	
	Thy word is true from \textbf{ev}er\textbf{last}ing * all the judgments of thy righteousness en\textbf{dure} fore\textbf{ver}more.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}rit.
	
	As it was in the beginning, is now and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}