\begin{multicols}{2}
	I call \textbf{with} my whole heart * hear me, O Lord, I will keep thy stat\textbf{utes}.
	
	Yea, even un\textbf{to} thee do I call * help me, and I shall keep thy testimon\textbf{ies}.
	
	Early in the morning do \textbf{I} cry unto thee * for in thy word is \textbf{my} trust.
	
	Mine eyes prevent \textbf{the} night watches * that I might be occupied in \textbf{thy} word.
	
	Hear my voice, O Lord, according unto thy \textbf{lov}ing-kindness * quicken me, according to thy judg\textbf{ments}.
	
	They draw nigh who of malice \textbf{per}secute me * and are far from \textbf{thy} law.
	
	Be thou \textbf{nigh} at hand, O Lord * for all thy commandments are \textbf{true}.
	
	As concerning thy testimonies, I \textbf{have} known long since * that thou hast grounded them forev\textbf{er}.
	
	O consider mine adversity, \textbf{and} deliver me * for I do not forget \textbf{thy} law.
	
	Avenge thou my cause, \textbf{and} deliver me * quicken me according to \textbf{thy} word.
	
	Salvation is far from \textbf{the} ungodly * for they regard not thy stat\textbf{utes}.
	
	Great is thy \textbf{mer}cy, O Lord * quicken me, as thou \textbf{art} wont.
	
	Many there are who trouble me and \textbf{per}secute me * yet I do not swerve from thy testimo\textbf{nies}.
	
	It grieveth me when I see \textbf{the} transgressors * because they keep not \textbf{thy} law.
	
	Consider, O Lord, how I love \textbf{thy} commandments * O quicken me, according to thy loving-kind\textbf{ness}.
	
	Thy word is true from \textbf{ev}erlasting * all the judgments of thy righteousness endure forev\textbf{er}more.
\end{multicols}