\begin{multicols}{2}
	Wash me thoroughly from my wick\textbf{ed}ness * and \textbf{cleanse} me from my sin.
	
	For I acknowledge \textbf{my} faults * and my sin is e\textbf{ver} before me.
	
	Against thee only have I sinned, and done this evil in \textbf{thy} sight * that thou mightest be justified in thy saying, and \textbf{clear} when thou art judged.
	
	Behold, I was shapen in wick\textbf{ed}ness * and with sin hath my mo\textbf{ther} conceived me.
	
	But lo, thou requirest truth in the in\textbf{ward} parts * and shalt make me to understand \textbf{wis}dom secretly.
	
	Thou shalt purge me with hyssop, and I shall \textbf{be} clean * thou shalt wash me and I shall be \textbf{whi}ter than the snow.
	
	Thou shalt make me hear of joy and \textbf{glad}ness * that the bones which thou hast \textbf{bro}ken may rejoice.
	
	Turn thy face from \textbf{my} sins * and put \textbf{out} all my misdeeds.
	
	Make me a clean heart, \textbf{O} God * and renew a right spi\textbf{rit} within me.
	
	Cast me not away from thy \textbf{pres}ence * and take not thy Holy \textbf{Spir}it from me.
	
	O give me the comfort of thy help \textbf{a}gain * and establish me with \textbf{thy} free Spirit.
	
	Then shall I teach thy ways unto the \textbf{wick}ed * and sinners shall be con\textbf{ver}ted unto thee.
	
	Deliver me from blood-guiltiness, O God, thou that art the God of my sal\textbf{va}tion * and my tongue shall sing \textbf{of} thy righteousness.
	
	Thou shalt open my lips, \textbf{O} Lord * and my \textbf{mouth} shall shew thy praise.
	
	For thou desirest no sacrifice, else would I give \textbf{it} thee * but thou delightest not \textbf{in} burnt-offerings.
	
	The sacrifice of God is a troubled \textbf{spir}it * a broken and contrite heart, O God, \textbf{shalt} thou not despise.
	
	O be favorable and gracious unto \textbf{Zi}on * build thou the walls \textbf{of} Jerusalem.
	
	Then shalt thou be pleased with the sacrifice of righteousness, with the burnt-offerings and ob\textbf{la}tions * then shall they offer young bullocks u\textbf{pon} thine altar.
	
	Glory be to the Father, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}