\begin{multicols}{2}
	Wash me thoroughly \textbf{from} my wickedness * \textbf{and} cleanse me from my sin.
	
	For I acknowledge \textbf{my} faults * and my sin is \textbf{ev}er before me.
	
	Against thee only have I sinned, and done this \textbf{e}vil in thy sight * that thou mightest be justified in thy saying, \textbf{and} clear when thou art judged.
	
	Behold, I was shap\textbf{en} in wickedness * and with sin hath my mo\textbf{ther} conceived me.
	
	But lo, thou requirest truth \textbf{in} the inward parts * and shalt make me to under\textbf{stand} wisdom secretly.
	
	Thou shalt purge me with hyssop, \textbf{and} I shall be clean * thou shalt wash me and I shall \textbf{be} whiter than the snow.
	
	Thou shalt make me hear of \textbf{joy} and gladness * that the bones which thou \textbf{hast} broken may rejoice.
	
	Turn \textbf{thy} face from my sins * and \textbf{put} out all my misdeeds.
	
	Make me \textbf{a} clean heart, O God * and renew a right \textbf{spir}it within me.
	
	Cast me not away \textbf{from} thy presence * and take not thy Ho\textbf{ly} Spirit from me.
	
	O give me the comfort \textbf{of} thy help again * and establish me \textbf{with} thy free Spirit.
	
	Then shall I teach thy ways un\textbf{to} the wicked * and sinners shall be \textbf{con}verted unto thee.
	
	Deliver me from blood-guiltiness, O God, thou that art the God of \textbf{my} salvation * and my tongue shall \textbf{sing} of thy righteousness.
	
	Thou shalt o\textbf{pen} my lips, O Lord * and \textbf{my} mouth shall shew thy praise.
	
	For thou desirest no sacrifice, else \textbf{would} I give it thee * but thou delightest \textbf{not} in burnt-offerings.
	
	The sacrifice of God is a \textbf{trou}bled spirit * a broken and contrite heart, O \textbf{God}, shalt thou not despise.
	
	O be favorable and gracious \textbf{un}to Zion * build thou the \textbf{walls} of Jerusalem.
	
	Then shalt thou be pleased with the sacrifice of righteousness, with the burnt-offerings \textbf{and} oblations * then shall they offer young bullocks \textbf{up}on thine altar.
	
	Glory be to the Fa\textbf{ther}, and to the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er shall be * world \textbf{with}out end. Amen.
\end{multicols}