\begin{multicols}{2}
	He brought me also out of the pit of misery, out of the mire \textbf{and} clay * and set my feet upon the rock, and ordered \textbf{my} goings.
	
	And he hath put a new song \textbf{in} my mouth * even a thanksgiving \textbf{un}to our God.
	
	Many shall see \textbf{it}, and fear * and shall put their \textbf{trust} in the Lord.
	
	Blessed is the man who hath set his hope \textbf{in} the Lord * and turned not unto the proud, and to such as go \textbf{a}bout with lies.
	
	Thou hast multiplied thy wonderful works, O Lord my God, and there is no one like \textbf{un}to thee * I will proclaim that they are multiplied a\textbf{bove} number.
	
	If I should declare them, and \textbf{speak} of them * they should be more than I am ab\textbf{le} to express.
	
	Sacrifice, and meat-offering, thou \textbf{would}est not * but mine ears hast \textbf{thou} opened.
	
	Burnt-offerings, and sacrifice for sin, hast thou not re\textbf{qui}red * then said \textbf{I}, Lo, I come.
	
	In the book it is written of me, that I should fulfill thy will, \textbf{O} my God * I am content to do it; yea, thy law is \textbf{with}in my heart.
	
	I have declared thy righteousness in the great congre\textbf{ga}tion * lo, I will not refrain my lips, O Lord, and that \textbf{thou} knowest.
	
	I have not hid thy righteousness with\textbf{in} my heart * my talk hath been of thy truth, and of thy \textbf{sal}vation.
	
	I have not kept back thy loving-mercy \textbf{and} truth * from the great con\textbf{gre}gation.
	
	Withdraw not thou thy mercy from \textbf{me}, O Lord * let thy loving-kindness and truth always \textbf{pre}serve me.
	
	For innumerable troubles are come about me, my sins have taken such hold upon me that I can\textbf{not} look up * yea, they are more in number than the hairs of my head, and my heart \textbf{hath} failed me.
	
	Be pleased, O Lord, to de\textbf{li}ver me * make haste, O Lord, \textbf{to} help me.
	
	Let them be ashamed and confounded together who seek after my soul to des\textbf{troy} it * let them be driven backward, and put to rebuke, who wish \textbf{me} evil.
	
	Let them be desolate, and rewarded \textbf{with} shame * who say unto me, Good, well done, at my \textbf{mis}fortune.
	
	Let all those who seek thee be joyful and \textbf{glad} in thee * and let such as love thy salvation say always, \textbf{The} Lord be praised.
	
	As for me, I am poor and \textbf{need}y * but the Lord car\textbf{eth} for me.
	
	Thou art my helper and re\textbf{deem}er * make no long tarry\textbf{ing}, O my God.
\end{multicols}