I waited patiently for the Lord * and he inclined unto me, and heard my calling.

He brought me also out of the pit of misery, out of the mire and clay * and set my feet upon the rock, and ordered my goings.

And he hath put a new song in my mouth * even a thanksgiving unto our God.

Many shall see it, and fear * and shall put their trust in the Lord.

Blessed is the man who hath set his hope in the Lord * and turned not unto the proud, and to such as go about with lies.

Thou hast multiplied thy wonderful works, O Lord my God, and there is no one like unto thee * I will proclaim that they are multiplied above number.

If I should declare them, and speak of them * they should be more than I am able to express.

Sacrifice, and meat-offering, thou wouldest not * but mine ears hast thou opened.

Burnt-offerings, and sacrifice for sin, hast thou not required * then said I, Lo, I come.

In the book it is written of me, that I should fulfill thy will, O my God * I am content to do it; yea, thy law is within my heart.

I have declared thy righteousness in the great congregation * lo, I will not refrain my lips, O Lord, and that thou knowest.

I have not hid thy righteousness within my heart * my talk hath been of thy truth, and of thy salvation.

I have not kept back thy loving-mercy and truth * from the great congregation.

Withdraw not thou thy mercy from me, O Lord * let thy loving-kindness and truth always preserve me.

For innumerable troubles are come about me, my sins have taken such hold upon me that I cannot look up * yea, they are more in number than the hairs of my head, and my heart hath failed me.

Be pleased, O Lord, to deliver me * make haste, O Lord, to help me.

Let them be ashamed and confounded together who seek after my soul to destroy it * let them be driven backward, and put to rebuke, who wish me evil.

Let them be desolate, and rewarded with shame * who say unto me, Good, well done, at my misfortune.

Let all those who seek thee be joyful and glad in thee * and let such as love thy salvation say always, The Lord be praised.

As for me, I am poor and needy * but the Lord careth for me.

Thou art my helper and redeemer * make no long tarrying, O my God.