\begin{multicols}{2}
	O my soul, thou hast said \textbf{un}to \textbf{the} Lord * Thou art my God, my goods are noth\textbf{ing} unto thee.
	
	All my delight is upon the saints who \textbf{are} in \textbf{the} earth * and upon such as excel \textbf{in} virtue.
	
	But they who run af\textbf{ter} a\textbf{noth}er god * shall have \textbf{great} trouble.
	
	The drink-offerings of blood will \textbf{I} not \textbf{off}er * neither make mention of their names \textbf{with}in my lips.
	
	The Lord himself is the portion of mine inheritance \textbf{and} of \textbf{my} cup * and he shall restore my inheri\textbf{tance} unto me.
	
	The lot is fallen unto me \textbf{in} a \textbf{fair} ground * yea, I have a good\textbf{ly} heritage.
	
	I will thank the Lord for giv\textbf{ing} me \textbf{warn}ing * my reins also chasten me in the \textbf{night} season.
	
	I have set God al\textbf{ways} be\textbf{fore} me * for he is on my right hand, therefore I \textbf{shall} not fall.
	
	Wherefore my heart was glad, and my \textbf{glo}ry \textbf{re}joice * my flesh also \textbf{shall} rest in hope.
	
	For why? thou shalt not \textbf{leave} my \textbf{soul} in hell * neither shall thou suffer thy Holy One to see \textbf{cor}ruption.
	
	Thou shall shew me the path of life, in thy presence is the \textbf{full}ness \textbf{of} joy * and at thy right hand there is pleasure \textbf{for}evermore.
	
	Glory be to the \textbf{Fa}ther, and \textbf{t}o the Son * and to the Ho\textbf{ly} Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world without \textbf{end}. Amen.
\end{multicols}