\begin{multicols}{2}
	Let Israel now confess that \textbf{he} is gracious * and that his mercy en\textbf{dur}eth forever.
	
	Let the house of \textbf{Aa}ron now confess * that his mercy en\textbf{dur}eth forever.
	
	Yea, let them now who \textbf{fear} the Lord confess * that his mercy en\textbf{dur}eth forever.
	
	I called upon the \textbf{Lord} in trouble * and \textbf{the} Lord heard me at large.
	
	The \textbf{Lord} is on my side * I will not fear what \textbf{man} doeth unto me.
	
	The Lord taketh my part with \textbf{them} who help me * therefore shall I see my desire \textbf{up}on mine enemies.
	
	It is better \textbf{to} trust in the Lord * than to put a\textbf{ny} confidence in man.
	
	It is better \textbf{to} trust in the Lord * than to put any con\textbf{fi}dence in princes.
	
	All nations com\textbf{passed} me round about * but in the Name of the Lord \textbf{will} I destroy them.
	
	They kept me in on every side, they kept me in, I \textbf{say}, on every side * but in the Name of the Lord \textbf{will} I destroy them.
	
	They came about me like bees, and are extinct even as the fi\textbf{re} among thorns * for in the Name of the Lord \textbf{I} will destroy them.
	
	Thou hast thrust sore at \textbf{me} that I might fall * \textbf{but} the Lord was my help.
	
	The Lord is \textbf{my} strength and my song * and is be\textbf{come} my salvation.
	
	The voice of joy and health is in the dwellings \textbf{of} the righteous * the right hand of the Lord bring\textbf{eth} mighty things to pass.
	
	The right hand of the Lord hath \textbf{the} preeminence * the right hand of the Lord bring\textbf{eth} mighty things to pass.
	
	I \textbf{shall} not die, but live * and de\textbf{clare} the works of the Lord.
	
	The Lord hath chastened \textbf{and} corrected me * but he hath not given \textbf{me} over unto death.
	
	Open me the \textbf{gates} of righteousness * that I may go into them, and \textbf{give} thanks unto the Lord.
	
	This is \textbf{the} gate of the Lord * the righteous \textbf{shall} enter into it.
	
	I will thank thee, for \textbf{thou} hast heard me * and art be\textbf{come} my salvation.
	
	The same stone which \textbf{the} builders refused * is become the head\textbf{stone} in the corner.
	
	This is \textbf{the} Lord's doing * and it is \textbf{mar}velous in our eyes.
	
	This is the day \textbf{which} the Lord hath made * we will re\textbf{joice} and be glad in it.
	
	\textbf{Help} me now, O Lord * O Lord, send \textbf{us} now prosperity.
	
	Blessed be he that cometh in \textbf{the} Name of the Lord * we have wished you good luck, ye that are \textbf{of} the house of the Lord.
	
	God is the Lord \textbf{who} hath shewed us light * bind the sacrifice with cords, yea, even unto the \textbf{horns} of the altar.
	
	Thou art my God, and \textbf{I} will thank thee * thou art my God, \textbf{and} I will praise thee.
	
	O give thanks unto the Lord, for \textbf{he} is gracious * and his mercy en\textbf{dur}eth forever.
\end{multicols}