\begin{multicols}{2}
	Let Israel now confess that he is \textbf{gra}cious * and that his mercy endur\textbf{eth} forever.
	
	Let the house of Aaron \textbf{now} confess * that his mercy endur\textbf{eth} forever.
	
	Yea, let them now who fear the \textbf{Lord} confess * that his mercy endur\textbf{eth} forever.
	
	I called upon the Lord in \textbf{trou}ble * and the \textbf{Lord} heard me at large.
	
	The Lord is \textbf{on} my side * I will not fear what man \textbf{do}eth unto me.
	
	The Lord taketh my part with them who \textbf{help} me * therefore shall I see my desire u\textbf{pon} mine enemies.
	
	It is better to trust \textbf{in} the Lord * than to put any con\textbf{fi}dence in man.
	
	It is better to trust \textbf{in} the Lord * than to put any confi\textbf{dence} in princes.
	
	All nations compassed me \textbf{round} about * but in the Name of the Lord will \textbf{I} destroy them.
	
	They kept me in on every side, they kept me in, I say, on \textbf{ev}ery side * but in the Name of the Lord will \textbf{I} destroy them.
	
	They came about me like bees, and are extinct even as the fire a\textbf{mong} thorns * for in the Name of the Lord I \textbf{will} destroy them.
	
	Thou hast thrust sore at me that \textbf{I} might fall * but \textbf{the} Lord was my help.
	
	The Lord is my strength \textbf{and} my song * and is become \textbf{my} salvation.
	
	The voice of joy and health is in the dwellings of the \textbf{righ}teous * the right hand of the Lord bringeth \textbf{migh}ty things to pass.
	
	The right hand of the Lord hath the pre\textbf{em}inence * the right hand of the Lord bringeth \textbf{migh}ty things to pass.
	
	I shall not die, \textbf{but} live * and declare \textbf{the} works of the Lord.
	
	The Lord hath chastened and cor\textbf{rect}ed me * but he hath not given me \textbf{ov}er unto death.
	
	Open me the gates of \textbf{righ}teousness * that I may go into them, and give \textbf{thanks} unto the Lord.
	
	This is the gate \textbf{of} the Lord * the righteous shall \textbf{en}ter into it.
	
	I will thank thee, for thou hast \textbf{heard} me * and art become \textbf{my} salvation.
	
	The same stone which the builders \textbf{re}fused * is become the headstone \textbf{in} the corner.
	
	This is the Lord's \textbf{do}ing * and it is mar\textbf{ve}lous in our eyes.
	
	This is the day which the \textbf{Lord} hath made * we will rejoice \textbf{and} be glad in it.
	
	Help me \textbf{now}, O Lord * O Lord, send us \textbf{now} prosperity.
	
	Blessed be he who cometh in the Name \textbf{of} the Lord * we have wished you good luck, ye who are of \textbf{the} house of the Lord.
	
	God is the Lord who hath \textbf{shewed} us light * bind the sacrifice with cords, yea, even unto the horns \textbf{of} the altar.
	
	Thou art my God, and I will \textbf{thank} thee * thou art my God, and \textbf{I} will praise thee.
	
	O give thanks unto the Lord, for he is \textbf{gra}cious * and his mercy endur\textbf{eth} forever.
\end{multicols}