O give thanks unto the Lord, for he is gracious * because his mercy endureth forever.

Let Israel now confess that he is gracious * and that his mercy endureth forever.

Let the house of Aaron now confess * that his mercy endureth forever.

Yea, let them now that fear the Lord confess * that his mercy endureth forever.

I called upon the Lord in trouble * and the Lord heard me at large.

The Lord is on my side * I will not fear what man doeth unto me.

The Lord taketh my part with them that help me * therefore shall I see my desire upon mine enemies.

It is better to trust in the Lord * than to put any confidence in man.

It is better to trust in the Lord * than to put any confidence in princes.

All nations compassed me round about * but in the Name of the Lord will I destroy them.

They kept me in on every side, they kept me in, I say, on every side * but in the Name of the Lord will I destroy them.

They came about me like bees, and are extinct even as the fire among thorns * for in the Name of the Lord I will destroy them.

Thou hast thrust sore at me that I might fall * but the Lord was my help.

The Lord is my strength and my song * and is become my salvation.

The voice of joy and health is in the dwellings of the righteous * the right hand of the Lord bringeth mighty things to pass.

The right hand of the Lord hath the preeminence * the right hand of the Lord bringeth mighty things to pass.

I shall not die, but live * and declare the works of the Lord.

The Lord hath chastened and corrected me * but he hath not given me over unto death.

Open me the gates of righteousness * that I may go into them, and give thanks unto the Lord.

This is the gate of the Lord * the righteous shall enter into it.

I will thank thee, for thou hast heard me * and art become my salvation.

The same stone which the builders refused * is become the headstone in the corner.

This is the Lord's doing * and it is marvelous in our eyes.

This is the day which the Lord hath made * we will rejoice and be glad in it.

Help me now, O Lord * O Lord, send us now prosperity.

Blessed be he that cometh in the Name of the Lord * we have wished you good luck, ye that are of the house of the Lord.

God is the Lord who hath shewed us light * bind the sacrifice with cords, yea, even unto the horns of the altar.

Thou art my God, and I will thank thee * thou art my God, and I will praise thee.

O give thanks unto the Lord, for he is gracious * and his mercy endureth forever.