\begin{multicols}{2}
	I will call upon the Lord, who is worthy \textbf{to} be praised * so shall I be safe \textbf{from} mine enemies.
	
	The sorrows of death \textbf{com}passed me * and the overflowings of ungodli\textbf{ness} made me afraid.
	
	The pains of hell came a\textbf{bout} me * the snares of death \textbf{ov}ertook me.
	
	In my trouble I will call u\textbf{pon} the Lord * and com\textbf{plain} unto my God.
	
	So shall he hear my voice out of his holy \textbf{tem}ple * and my complaint shall come before him, it shall enter e\textbf{ven} into his ears.
	
	The earth trembled \textbf{and} quaked * the very foundations of the mountains shook, and were removed, \textbf{be}cause he was wroth.
	
	There went a smoke out in his \textbf{pres}ence * and a consuming fire out of his mouth, so that coals were \textbf{kind}led at it.
	
	He bowed the heavens, and \textbf{came} down * and there was dark\textbf{ness} under his feet.
	
	He rode upon the cherubim, and \textbf{did} fly * he came flying upon \textbf{the} wings of the wind.
	
	He made darkness his \textbf{se}cret place * his pavilion round about him with dark water, and \textbf{clouds} to cover him.
	
	At the brightness of his presence his \textbf{clouds} removed * hail-stones, and \textbf{coals} of fire.
	
	The Lord also thundered out of heaven, and the Highest gave his \textbf{thun}der * hail-stones, and \textbf{coals} of fire.
	
	He sent out his arrows, and \textbf{scat}tered them * he cast forth lightnings, \textbf{and} destroyed them.
	
	The springs of waters were seen, and the foundations of the round world were discovered, at thy chid\textbf{ing}, O Lord * at the blasting of thy breath of \textbf{thy} displeasure.
	
	He shall send down from on high to \textbf{fetch} me * and shall take me out of \textbf{ma}ny waters.
	
	He shall deliver me from my strongest enemy, and from them who \textbf{hate} me * for they are too \textbf{migh}ty for me.
	
	They prevented me in the day of my \textbf{trou}ble * but the Lord was \textbf{my} upholder.
	
	He brought me forth also into a place of \textbf{li}berty * he brought me forth, even because he had a \textbf{fa}vor unto me.
	
	The Lord shall reward me after my righteous \textbf{deal}ing * according to the cleanness of my hands shall he \textbf{re}compense me.
	
	Because I have kept the ways \textbf{of} the Lord * and have not forsaken my God, \textbf{as} the wicked doth.
	
	For I have an eye unto \textbf{all} his laws * and will not cast out his com\textbf{mand}ments from me.
	
	I was also uncorrupt be\textbf{fore} him * and eschewed \textbf{mine} own wickedness.
	
	Therefore the Lord rewarded me after my righteous \textbf{deal}ing * and according unto the cleanness of my hands \textbf{in} his eye-sight.
	
	With the holy thou shalt be \textbf{ho}ly * and with the perfect man thou \textbf{shalt} be perfect.
	
	With the clean thou \textbf{shalt} be clean * and with the froward thou shalt \textbf{learn} frowardness.
	
	For thou shall save the people who are in ad\textbf{ver}sity * and shall bring down the \textbf{high} looks of the proud.
	
	Thou also shall light my \textbf{cand}le * the Lord my God shall make my \textbf{dark}ness to be light.
	
	For in thee I shall discomfit a \textbf{host} of men * and with the help of my God I shall \textbf{leap} over the wall.
	
	The way of God is an unde\textbf{fil}ed way * the word of the Lord is tried in the fire; he is the defender of all them who \textbf{put} their trust in him.
	
	For who is God \textbf{but} the Lord? * or who hath any \textbf{strength}, except our God?
	
	It is God who girdeth me with the \textbf{strength} of war * and maketh \textbf{my} way perfect.
	
	He maketh my feet like \textbf{harts' }feet * and sett\textbf{eth} me up on high.
	
	He teacheth mine \textbf{hands} to fight * and mine arms shall bend e\textbf{ven }a bow of steel.
	
	Thou hast given me the defense of thy sal\textbf{va}tion * thy right hand also shall hold me up, and thy loving correc\textbf{tion} shall make me great.
	
	Thou shall make room enough under me \textbf{for} to go * that my \textbf{foot}steps shall not slide.
	
	I will follow upon mine enemies, and over\textbf{take} them * neither will I turn again until I \textbf{have} destroyed them.
	
	I will smite them, that they shall not be able \textbf{to} stand * but \textbf{fall} under my feet.
	
	Thou hast girded me with strength unto \textbf{bat}tle * thou shall throw down mine en\textbf{e}mies under me.
	
	Thou hast made mine enemies also to turn their backs u\textbf{pon} me * and I shall destroy \textbf{them} who hate me.
	
	They shall cry, but there shall be no one to \textbf{help} them * yea, even unto the Lord shall they cry, but he \textbf{shall} not hear them.
	
	I will beat them as dust be\textbf{fore} the wind * I will cast them out as \textbf{the} clay in the streets.
	
	Thou shalt deliver me from the strivings of the \textbf{peo}ple * and thou shall make me the head \textbf{of} the gentiles.
	
	A people whom I have \textbf{not} known * \textbf{---} shall serve me.
	
	As son as they hear of me, they shall o\textbf{bey} me * but the strange children shall dis\textbf{sem}ble with me.
	
	The strange children \textbf{shall} fail * and be afraid out \textbf{of} their prisons.
	
	The Lord liveth, and blessed by my strong \textbf{hel}per * and praised be the God of \textbf{my} salvation.
	
	Even the God who seeth that I \textbf{be} avenged * and subdueth the \textbf{peo}ple unto me.
	
	It is he who delivereth me from my cruel enemies, and setteth me upon above mine adver\textbf{sar}ies * thou shalt rid me \textbf{from} the wicked man.
	
	For this cause will I give thanks unto thee, O Lord, among the \textbf{gen}tiles * and sing \textbf{praises} unto thy Name.
	
	Great prosperity giveth he un\textbf{to} his King * and sheweth loving-kindness unto David his Anointed, and unto his \textbf{seed} forevermore.
	
	Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}