I will love thee, O Lord, my strength; the Lord is my firmament, and my defense * my Savior, my God, and might, in whom will I trust: my buckler, the horn of my salvation, and my refuge.

I will call upon the Lord, who is worthy to be praised * so shall I be safe from mine enemies.

The sorrows of death compassed me * and the overflowings of ungodliness made me afraid.

The pains of hell came about me * the snares of death overtook me.

In my trouble I will call upon the Lord * and complain unto my God.

So shall he hear my voice out of his holy temple * and my complaint shall come before him, it shall enter even into his ears.

The earth trembled and quaked * the very foundations of the mountains shook, and were removed, because he was wroth.

There went a smoke out in his presence * and a consuming fire out of his mouth, so that coals were kindled at it.

He bowed the heavens, and came down * and there was darkness under his feet.

He rode upon the cherubim, and did fly * he came flying upon the wings of the wind.

He made darkness his secret place * his pavilion round about him with dark water, and clouds to cover him.

At the brightness of his presence his clouds removed * hail-stones, and coals of fire.

The Lord also thundered out of heaven, and the Highest gave his thunder * hail-stones, and coals of fire.

He sent out his arrows, and scattered them * he cast forth lightnings, and destroyed them.

The springs of waters were seen, and the foundations of the round world were discovered, at thy chiding, O Lord * at the blasting of thy breath of thy displeasure.

He shall send down from on high to fetch me * and shall take me out of many waters.

He shall deliver me from my strongest enemy, and from them who hate me * for they are too mighty for me.

They prevented me in the day of my trouble * but the Lord was my upholder.

He brought me forth also into a place of liberty * he brought me forth, even because he had a favor unto me.

The Lord shall reward me after my righteous dealing * according to the cleanness of my hands shall he recompense me.

Because I have kept the ways of the Lord * and have not forsaken my God, as the wicked doth.

For I have an eye unto all his laws * and will not cast out his commandments from me.

I was also uncorrupt before him * and eschewed mine own wickedness.

Therefore the Lord rewarded me after my righteous dealing * and according unto the cleanness of my hands in his eye-sight.

With the holy thou shalt be holy * and with the perfect man thou shalt be perfect.

With the clean thou shalt be clean * and with the froward thou shalt learn frowardness.

For thou shall save the people who are in adversity * and shall bring down the high looks of the proud.

Thou also shall light my candle * the Lord my God shall make my darkness to be light.

For in thee I shall discomfit a host of men * and with the help of my God I shall leap over the wall.

The way of God is an undefiled way * the word of the Lord is tried in the fire; he is the defender of all them who put their trust in him.

For who is God but the Lord? * or who hath any strength, except our God?

It is God who girdeth me with the strength of war * and maketh my way perfect.

He maketh my feet like harts' feet * and setteth me up on high.

He teacheth mine hands to fight * and mine arms shall bend even a bow of steel.

Thou hast given me the defense of thy salvation * thy right hand also shall hold me up, and thy loving correction shall make me great.

Thou shall make room enough under me for to go * that my footsteps shall not slide.

I will follow upon mine enemies, and overtake them * neither will I turn again until I have destroyed them.

I will smite them, that they shall not be able to stand * but fall under my feet.

Thou hast girded me with strength unto battle * thou shall throw down mine enemies under me.

Thou hast made mine enemies also to turn their backs upon me * and I shall destroy them who hate me.

They shall cry, but there shall be no one to help them * yea, even unto the Lord shall they cry, but he shall not hear them.

I will beat them as dust before the wind * I will cast them out as the clay in the streets.

Thou shalt deliver me from the strivings of the people * and thou shall make me the head of the gentiles.

A people whom I have not known * shall serve me.

As son as they hear of me, they shall obey me * but the strange children shall dissemble with me.

The strange children shall fail * and be afraid out of their prisons.

The Lord liveth, and blessed by my strong helper * and praised be the God of my salvation.

Even the God who seeth that I be avenged * and subdueth the people unto me.

It is he who delivereth me from my cruel enemies, and setteth me upon above mine adversaries * thou shalt rid me from the wicked man.

For this cause will I give thanks unto thee, O Lord, among the gentiles * and sing praises unto thy Name.

Great prosperity giveth he unto his King * and sheweth loving-kindness unto David his Anointed, and unto his seed forevermore.