\begin{multicols}{2}
	For all they that hope in thee shall not be \textbf{a}shamed * but such as transgress without a cause shall be put \textbf{to} confusion.
	
	Shew me thy ways, \textbf{O} Lord * and \textbf{teach} me thy paths.
	
	Lead me forth in thy truth and \textbf{learn} me * for thou art the God of my salvation, in thee hath been my hope \textbf{all} the day long.
	
	Call to remembrance, O Lord, thy tender \textbf{mer}cies * and thy loving-kindness, which have been \textbf{ev}er of old.
	
	O remember not the sins and offenses of \textbf{my} youth * but according to thy mercy think thou upon me, O Lord, \textbf{for} thy goodness.
	
	Gracious and righteous is \textbf{the} Lord * therefore will he teach \textbf{sin}ners in the way.
	
	Them that are meek shall he guide in \textbf{judg}ment * and such as are gentle, them \textbf{shall} he learn his way.
	
	All the paths of the Lord are mercy \textbf{and} truth * unto such as keep his covenant and his \textbf{tes}timonies.
	
	For thy Name's sake, \textbf{O} Lord * be merciful unto my \textbf{sin} for it is great.
	
	What man is he that feareth \textbf{the} Lord * him shall he teach in the \textbf{way} that he shall choose.
	
	His soul shall swell \textbf{at} ease * and his seed shall in\textbf{her}it the land.
	
	The secret of the Lord is among them that \textbf{fear} him * and he will shew \textbf{them} his covenant.
	
	Mine eyes are ever looking unto \textbf{the} Lord * for he shall pluck my \textbf{feet} out of the net.
	
	Turn thee unto me, and have mercy u\textbf{pon} me * for I am desolate \textbf{and} in misery.
	
	The sorrows of my heart are \textbf{en}larged * O bring thou me out \textbf{of} my troubles.
	
	Look upon my adversity and mis\textbf{er}y * and for\textbf{give} me all my sin.
	
	Consider mine enemies, how many \textbf{they} are * let me not be confounded, for I have \textbf{put} my trust in thee.
	
	Let perfectness and righteous dealing wait u\textbf{pon} me * for my hope \textbf{hath} been in thee.
	
	Deliver Israel, \textbf{O} God * out of \textbf{all} his troubles.
	
	Glory be to the Father, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}