\begin{multicols}{2}
	For all they that hope in thee \textbf{shall} not be ashamed * but such as transgress without a cause shall be \textbf{put} to confusion.
	
	Shew \textbf{me} thy ways, O Lord * \textbf{and} teach me thy paths.
	
	Lead me forth in thy \textbf{truth} and learn me * for thou art the God of my salvation, in thee hath been my \textbf{hope} all the day long.
	
	Call to remembrance, O Lord, thy \textbf{ten}der mercies * and thy loving-kindness, which have \textbf{been} ever of old.
	
	O remember not the sins and of\textbf{fen}ses of my youth * but according to thy mercy think thou upon me, O \textbf{Lord}, for thy goodness.
	
	Gracious and \textbf{right}eous is the Lord * therefore will he \textbf{teach} sinners in the way.
	
	Them that are meek shall he \textbf{guide} in judgment * and such as are gentle, \textbf{them} shall he learn his way.
	
	All the paths of the Lord are \textbf{mer}cy and truth * unto such as keep his covenant and \textbf{his} testimonies.
	
	For \textbf{thy} Name's sake, O Lord * be merciful unto \textbf{my} sin for it is great.
	
	What man is he that \textbf{fear}eth the Lord * him shall he teach in \textbf{the} way that he shall choose.
	
	His \textbf{soul} shall swell at ease * and his seed shall \textbf{in}herit the land.
	
	The secret of the Lord is among \textbf{them} that fear him * and he will \textbf{shew} them his covenant.
	
	Mine eyes are ever look\textbf{ing} unto the Lord * for he shall pluck \textbf{my} feet out of the net.
	
	Turn thee unto me, and have mer\textbf{cy} upon me * for I am deso\textbf{late }and in misery.
	
	The sorrows of \textbf{my} heart are enlarged * O bring thou me \textbf{out} of my troubles.
	
	Look upon my adversi\textbf{ty} and misery * and \textbf{for}give me all my sin.
	
	Consider mine enemies, how \textbf{man}y they are * let me not be confounded, for I \textbf{have} put my trust in thee.
	
	Let perfectness and righteous dealing \textbf{wait} upon me * for \textbf{my} hope hath been in thee.
	
	Deliver Is\textbf{ra}el, O God * out \textbf{of} all his troubles.
	
	Glory be to the Fa\textbf{ther}, and to the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er shall be * world \textbf{with}out end. Amen.
\end{multicols}