\greannotation{\veformat{Ant.}}
\greannotation{\veformat{iv. iv.}}
\gregorioscore{ant/dominus_regit_me.gabc}

\greannotation{\veformat{Ps. 21}}
\greannotation{\veformat{iv. iv.}}
\skiplines{1}\gabcsnippet{
	(c3) My(i) God,(h) (:?) my(ir) God,() look() upon() me,() why() hast(i) <b>thou</b>(h) for(i)sa(j)ken(ir) me?(i) <sp>*</sp>(:) and(ir) art() so() far() from() my() salvation,() and() from(i) <b>the</b>(h) words(i) of(j) my(h) com(fr)plaint.(f)
}

\input{psalter/21/4}


\pagebreak[1]


\greannotation{\veformat{Ps. 22}}
\greannotation{\veformat{iv. iv.}}
\clearpage\skiplines{0}\gabcsnippet{
	(c3) The(ir) Lord(i) <b>is</b>(h) my(i) shep(j)herd(ir) <sp>*</sp>(:) (ir) <b>there</b>(h)fore(i) I(j) shall(h) not(fr) want.()
}

\input{psalter/22/4} % G.P.


\pagebreak[1]


\greannotation{\veformat{Ps. 23}}
\greannotation{\veformat{iv. iv.}}
\skiplines{1}\gabcsnippet{
	(c3) The(i) earth(h) (:?) is(ir) the() Lord's,() and(i) <b>all</b>(h) that(i) there(j)in(ir) is() <sp>*</sp>(:) the(ir) compass() of() the() world,(i) <b>and</b>(h) they(i) who(j) dwell(h) there(fr)in.(f) 
}

\input{psalter/23/4}


\pagebreak[1]


\greannotation{\veformat{Ps. 24}}
\greannotation{\veformat{iv. iv.}}
\skiplines{1}\gabcsnippet{
	(c3) Un(i)to(h) (:?) thee,(ir) O() Lord,() will() I() lift() up() my soul;() my() God,() I() have(i) <b>put</b>(h) my(i) trust(j) in(ir) thee() <sp>*</sp>(:) O(ir) let() me() not() be() confounded,() neither() let() mine() en--()e(i)<b>mies</b>(h) tri(i)umph(j) o(h)ver(fr) me.()
}

\input{psalter/24/4} % G.P.


\pagebreak[1]


\greannotation{\veformat{Ps. 25}}
\greannotation{\veformat{iv. iv.}}
\skiplines{1}\gabcsnippet{
	(c3) Be(i) thou(h) (:?) my(ir) Judge,() O() Lord,() for() I() have() walked(i) <b>in</b>(h)no(i)cent(j)ly(ir) <sp>*</sp>(:) my(ir) trust() hath() been() also() in() the() Lord,(i) <b>there</b>(h)fore(i) shall(j) I(h) not(fr) fall.(f)
}

\input{psalter/25/4}


\pagebreak[1]


\greannotation{\veformat{Ps. 53}}
\greannotation{\veformat{iv. iv.}}
\clearpage\gabcsnippet{
	(c3) Save(i) me,(h) (:?) O(ir) God,(i) <b>for</b>(h) thy(i) Name's(j) sake(ir) <sp>*</sp>(:) and(ir) <b>a</b>(h)venge(i) me(j) in(h) thy(fr) strength.() 
}

\input{psalter/53/4} % G.P.


\pagebreak[1]


\greannotation{\veformat{Ps. 117}}
\greannotation{\veformat{iv. iv.}}
\skiplines{1}\gabcsnippet{
	(c3) O(i) give(h) (:?) thanks(ir) unto() the() Lord,() for(i) <b>he</b>(h) is(i) gra(j)cious(ir) <sp>*</sp>(:) because(ir) his() mercy() en(i)<b>dur</b>(h)eth(i) for(j)ev(h)er.(fr)
}

\input{psalter/117/4}


\pagebreak[1]


\greannotation{\veformat{Ps. 118A}}
\greannotation{\veformat{iv. iv.}}
\skiplines{1}\gabcsnippet{
	(c3) Bles(i)sed(h) (:?) are(ir) those() who() are() un--()de(i)<b>fi</b>(h)led(i) in(j) the(ir) way() <sp>*</sp>(:) and(ir) walk(i) <b>in</b>(h) the(i) law(j) of(h) the(fr) Lord.()
}

\input{psalter/118-1/4} % G.P.


\pagebreak[1]


\greannotation{\veformat{Ps. 118B}}
\greannotation{\veformat{iv. iv.}}
\skiplines{1}\gabcsnippet{
	(c3) O(i) do(h) (:?) well(ir) un(i)<b>to</b>(h) thy(i) ser(j)vant(ir) <sp>*</sp>(:) that(ir) I(i) <b>may</b>(h) live,(i) and(j) keep(h) thy(fr) word.()
}

\input{psalter/118-2/4} % G.P.

\repant{ant/dominus_regit_me.gabc}


\pagebreak[1]


\greannotation{\veformat{Ant.}}
\greannotation{\veformat{v. i.}}
\skiplines{1}\gregorioscore{ant/te_jure_laudant.gabc}

\greannotation{\veformat{Cant.}}
\greannotation{\veformat{v. i.}}
\skiplines{1}\gabcsnippet{
	(cb3) Who(d)so(f :?)ev(hr)er(h) <b>will</b>(i) be(hr) saved(h) <sp>*</sp>(:) be(hr)fore() all() things() it() is() necessary() that(h) <b>he</b>(i) hold(gr) the(g) <b>cath</b>(h)olic(fr) faith.()
}

\input{psalter/athanasian/5}

\pagebreak[1]

\skiplines{0}\repant{ant/te_jure_laudant.gabc}

\instruct{Turn back to the \whiteribbon for the chapter.}