\begin{multicols}{2}
	O learn me true understanding and \textbf{know}ledge * for I have believed \textbf{thy} commandments.
	
	Before I was troubled, I \textbf{went} wrong * but now have \textbf{I} kept thy word.
	
	Thou art good and \textbf{gra}cious * O teach \textbf{me} thy statutes.
	
	The proud have imagined a lie a\textbf{gainst} me * but I will keep thy commandments \textbf{with} my whole heart.
	
	Their heart is as fat \textbf{as} brawn * but my delight \textbf{hath} been in thy law.
	
	It is good for me that I have been in \textbf{trou}ble * that I may \textbf{learn} thy statutes.
	
	The law of thy mouth is dearer un\textbf{to} me * than thousands of \textbf{gold} and silver.
	
	Thy hands have made me and fa\textbf{shioned} me * O give me understanding, that I may learn \textbf{thy} commandments.
	
	They who fear thee will be glad when they \textbf{see} me * because I have put \textbf{my} trust in thy word.
	
	I know, O Lord, that thy judgments \textbf{are} right * and that thou of very faithfulness hast caused me \textbf{to} be troubled.
	
	O let thy merciful kindness be my \textbf{com}fort * according to thy word un\textbf{to} thy servant.
	
	O let thy loving mercies come unto me that I \textbf{may} live * for thy \textbf{law} is my delight.
	
	Let the proud be confounded, for they go wickedly to des\textbf{troy} me * but I will be occupied in \textbf{thy} commandments.
	
	Let such as fear thee, and have known thy testi\textbf{mo}nies * be \textbf{turned} unto me.
	
	O let my heart be sound in thy \textbf{stat}utes * that I \textbf{be} not ashamed.
	
	Glory be to the Father, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}