\begin{multicols}{2}
	O learn me true understanding and \textbf{know}ledge * for I have believed thy \textbf{com}mandments.
	
	Before I was troubled, \textbf{I} went wrong * but now have \textbf{I} kept thy word.
	
	Thou art good and \textbf{gra}cious * O teach me \textbf{thy} statutes.
	
	The proud have imagined a lie a\textbf{gainst} me * but I will keep thy commandments with \textbf{my} whole heart.
	
	Their heart is as \textbf{fat} as brawn * but my delight hath \textbf{been} in thy law.
	
	It is good for me that I have been in \textbf{trou}ble * that I may learn \textbf{thy} statutes.
	
	The law of thy mouth is dearer \textbf{un}to me * than thousands of gold \textbf{and} silver.
	
	Thy hands have made me and \textbf{fash}ioned me * O give me understanding, that I may learn thy \textbf{com}mandments.
	
	They who fear thee will be glad when they \textbf{see} me * because I have put my \textbf{trust} in thy word.
	
	I know, O Lord, that thy judgments \textbf{are} right * and that thou of very faithfulness hast caused me to \textbf{be} troubled.
	
	O let thy merciful kindness be my \textbf{com}fort * according to thy word unto \textbf{thy} servant.
	
	O let thy loving mercies come unto me that \textbf{I} may live * for thy law \textbf{is} my delight.
	
	Let the proud be confounded, for they go wickedly to des\textbf{troy} me * but I will be occupied in thy \textbf{com}mandments.
	
	Let such as fear thee, and have known thy testi\textbf{mo}nies * be \textbf{turned} unto me.
	
	O let my heart be sound in thy \textbf{stat}utes * that I be \textbf{not} ashamed.
	
	Glory be to the Father, and \textbf{to} the Son * and to the Ho\textbf{ly} Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world without \textbf{end}. Amen.
\end{multicols}