\begin{multicols}{2}
	O learn me true understanding and knowledge * for I have believed thy commandments.
	
	Before I was troubled, I went wrong * but now have I kept thy word.
	
	Thou art good and gracious * O teach me thy statutes.
	
	The proud have imagined a lie against me * but I will keep thy commandments with my whole heart.
	
	Their heart is as fat as brawn * but my delight hath been in thy law.
	
	It is good for me that I have been in trouble * that I may learn thy statutes.
	
	The law of thy mouth is dearer unto me * than thousands of gold and silver.
	
	Thy hands have made me and fashioned me * O give me understanding, that I may learn thy commandments.
	
	They who fear thee will be glad when they see me * because I have put my trust in thy word.
	
	I know, O Lord, that thy judgments are right * and that thou of very faithfulness hast caused me to be troubled.
	
	O let thy merciful kindness be my comfort * according to thy word unto thy servant.
	
	O let thy loving mercies come unto me that I may live * for thy law is my delight.
	
	Let the proud be confounded, for they go wickedly to destroy me * but I will be occupied in thy commandments.
	
	Let such as fear thee, and have known thy testimonies * be turned unto me.
	
	O let my heart be sound in thy statutes * that I be not ashamed.
	
	Glory be to the Fath\textbf{er}, and to the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now and \textbf{ev}er shall be * world \textbf{with}out end. Amen.
\end{multicols}