\begin{multicols}{2}
	O learn me true under\textbf{stand}ing and \textbf{know}ledge * for I have believed \textbf{thy} com\textbf{mand}ments.
	
	Before I was \textbf{troub}led, \textbf{I} went wrong * but \textbf{now} have I \textbf{kept} thy word.
	
	Thou art \textbf{good} and \textbf{gra}cious * O \textbf{teach} me thy \textbf{stat}utes.
	
	The proud have imagined a \textbf{lie} a\textbf{gainst} me * but I will keep thy commandments \textbf{with} my \textbf{whole} heart.
	
	Their \textbf{heart} is as \textbf{fat} as brawn * but my de\textbf{light} hath been \textbf{in} thy law.
	
	It is good for me that I have \textbf{been} in \textbf{trou}ble * that I may \textbf{learn} thy \textbf{stat}utes.
	
	The law of thy mouth is \textbf{dear}er \textbf{un}to me * than thousands of \textbf{gold} and \textbf{sil}ver.
	
	Thy hands have \textbf{made} me and \textbf{fash}ioned me * O give me understanding, that I may learn \textbf{thy} com\textbf{mand}ments.
	
	They who fear thee will be \textbf{glad} when they \textbf{see} me * because I have put my \textbf{trust} in \textbf{thy} word.
	
	I know, O Lord, that thy \textbf{judg}ments \textbf{are} right * and that thou of very faithfulness hast caused me \textbf{to} be \textbf{trou}bled.
	
	O let thy merciful kindness \textbf{be} my \textbf{com}fort * according to thy word un\textbf{to} thy \textbf{ser}vant.
	
	O let thy loving mercies come unto \textbf{me} that \textbf{I} may live * for thy \textbf{law} is \textbf{my} delight.
	
	Let the proud be confounded, for they go wickedly \textbf{to} des\textbf{troy} me * but I will be occupied in \textbf{thy} com\textbf{mand}ments.
	
	Let such as fear thee, and have known thy \textbf{tes}ti\textbf{mo}nies * be \textbf{turned} un\textbf{to} me.
	
	O let my heart be sound \textbf{in} thy \textbf{stat}utes * that \textbf{I} be \textbf{not} ashamed.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}it.
	
	As it was in the beginning is now, and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}