\begin{multicols}{2}
	O learn me true understanding and \textbf{know}ledge * for I have believed \textbf{thy} commandments.
	
	Before I was troubled, \textbf{I} went wrong * but now \textbf{have} I kept thy word.
	
	Thou art good and \textbf{gra}cious * O teach \textbf{me} thy statutes.
	
	The proud have imagined a lie a\textbf{gainst} me * but I will keep thy commandments \textbf{with} my whole heart.
	
	Their heart is as \textbf{fat} as brawn * but my delight \textbf{hath} been in thy law.
	
	It is good for me that I have been in \textbf{trou}ble * that I may \textbf{learn} thy statutes.
	
	The law of thy mouth is dearer \textbf{un}to me * than thousands of \textbf{gold} and silver.
	
	Thy hands have made me and \textbf{fa}shioned me * O give me understanding, that I may learn \textbf{thy} commandments.
	
	They who fear thee will be glad when they \textbf{see} me * because I have put my trust \textbf{in} thy word.
	
	I know, O Lord, that thy judgments \textbf{are} right * and that thou of very faithfulness hast caused me \textbf{to} be troubled.
	
	O let thy merciful kindness be my \textbf{com}fort * according to thy word un\textbf{to} thy servant.
	
	O let thy loving mercies come unto me that \textbf{I} may live * for thy law is \textbf{my} delight.
	
	Let the proud be confounded, for they go wickedly to des\textbf{troy} me * but I will be occupied in \textbf{thy} commandments.
	
	Let such as fear thee, and have known thy testi\textbf{mo}nies * \textbf{be} turned unto me.
	
	O let my heart be sound in thy \textbf{stat}utes * that \textbf{I} be not ashamed.
	
	Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}