\begin{multicols}{2}
	And hath raised up a mighty \textbf{sal}vation \textbf{for} us * in the \textbf{house} of his \textbf{ser}vant David.
	
	As he spake by the mouth of \textbf{his} holy \textbf{Pro}phets * \textbf{--} which have been \textbf{since} the world began.
	
	That we should be \textbf{saved} from our en\textbf{e}mies * \textbf{---} and from the hand of \textbf{all} that hate us.
	
	To perform the mercy promised \textbf{to} our fore\textbf{fa}thers * and to re\textbf{mem}ber his \textbf{ho}ly covenant.
	
	To perform the oath which he sware to our \textbf{fore}father A\textbf{bra}ham * \textbf{---} that \textbf{he} would give us.
	
	That we being delivered out of \textbf{the} hand of our e\textbf{ne}mies * \textbf{---} might serve \textbf{him} without fear.
	
	In holiness and right\textbf{eous}ness be\textbf{fore} him * \textbf{---} all the \textbf{days} of our life.
	
	And thou, child, shalt be called the Pro\textbf{phet} of the \textbf{High}est * for thou shalt \textbf{go} before the face of the Lord \textbf{to} prepare his ways.
	
	To give knowledge of salvation \textbf{un}to his \textbf{peo}ple * \textbf{---} for the remis\textbf{sion} of their sins.
	
	Through the ten\textbf{der} mercy of \textbf{our} God * whereby the \textbf{day}spring from on high hath \textbf{vi}sited us.
	
	To give light to them that sit in darkness and in \textbf{the} shadow \textbf{of} death * and to \textbf{guide} our feet in\textbf{to} the way of peace.
	
	Glory be to \textbf{the} Father, and to \textbf{the} Son * \textbf{---} and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, \textbf{and} ever \textbf{shall} be * \textbf{---} world with\textbf{out} end. Amen.
\end{multicols}