\begin{multicols}{2}
	And hath raised up a mighty \textbf{sa}lvation \textbf{for} us * in the \textbf{house} of his ser\textbf{vant} David.
	
	As he spake by the mouth of \textbf{his} holy \textbf{Pro}phets * \textbf{---} which have been since \textbf{the} world began.
	
	That we should be \textbf{saved} from our \textbf{en}emies * \textbf{---} and from the hand of all \textbf{that} hate us.
	
	To perform the mercy promised \textbf{to} our fore\textbf{fa}thers * and to re\textbf{mem}ber his ho\textbf{ly} covenant.
	
	To perform the oath which he sware to our \textbf{fore}father \textbf{A}braham * \textbf{---} that he \textbf{would} give us.
	
	That we being delivered out of \textbf{the} hand of our \textbf{en}emies * \textbf{---} might serve him \textbf{with}out fear.
	
	In holiness and right\textbf{eou}sness be\textbf{fore} him * \textbf{---} all the days \textbf{of} our life.
	
	And thou, child, shalt be called the Pro\textbf{phet} of the \textbf{High}est * for thou shalt \textbf{go} before the face of the Lord to \textbf{pre}pare his ways.
	
	To give knowledge of salvation \textbf{un}to his \textbf{peo}ple * \textbf{---} for the remission \textbf{of} their sins.
	
	Through the ten\textbf{der} mercy of \textbf{our} God * whereby the \textbf{day}spring from on high hath vi\textbf{si}ted us.
	
	To give light to them that sit in darkness and in \textbf{the} shadow \textbf{of} death * and to \textbf{guide} our feet into \textbf{the} way of peace.
	
	Glory be to \textbf{the} Father, and \textbf{to} the Son * \textbf{---} and to the Ho\textbf{ly} Spirit.
	
	As it was in the beginning, is now, \textbf{and} ever \textbf{shall} be * \textbf{---} world without \textbf{end}. Amen.
\end{multicols}