\begin{multicols}{2}
	And hath raised up a mighty sal\textbf{va}tion \textbf{for} us * in the house of his \textbf{ser}vant David.
	
	As he spake by the mouth of his \textbf{ho}ly \textbf{Pro}phets * which have been since \textbf{the} world began.
	
	That we should be saved \textbf{from} our e\textbf{ne}mies * and from the hand of \textbf{all} that hate us.
	
	To perform the mercy promised to \textbf{our} fore\textbf{fa}thers * and to remember his ho\textbf{ly} covenant.
	
	To perform the oath which he sware to our \textbf{fore}father A\textbf{bra}ham * that \textbf{he} would give us.
	
	That we being delivered out of the \textbf{hand} of our e\textbf{ne}mies * might serve \textbf{him} without fear.
	
	In holiness and righteous\textbf{ness} be\textbf{fore} him * all the \textbf{days} of our life.
	
	And thou, child, shalt be called the Prophet \textbf{of} the \textbf{High}est * for thou shalt go before the face of the Lord to \textbf{pre}pare his ways.
	
	To give knowledge of salvation un\textbf{to} his \textbf{peo}ple * for the remis\textbf{sion} of their sins.
	
	Through the tender \textbf{mer}cy of \textbf{our} God * whereby the dayspring from on high hath \textbf{vis}ited us.
	
	To give light to them that sit in darkness and in the \textbf{sha}dow \textbf{of} death * and to guide our feet into \textbf{the} way of peace.
	
	Glory be to the \textbf{Fa}ther, and to \textbf{the} Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}