\begin{multicols}{2}
	And hath raised up a mighty \textbf{sa}lvation \textbf{for} us * in the \textbf{house} of \textbf{his} servant David.
	
	As he spake by the mouth of \textbf{his} holy \textbf{Pro}phets * \textbf{---} which have \textbf{been} since the world began.
	
	That we should be \textbf{saved} from our \textbf{en}emies * \textbf{---} and from the hand \textbf{of} all that hate us.
	
	To perform the mercy promised \textbf{to} our fore\textbf{fa}thers * and to re\textbf{mem}ber \textbf{his} holy covenant.
	
	To perform the oath which he sware to our \textbf{fore}father \textbf{A}braham * \textbf{---} \textbf{that} he would give us.
	
	That we being delivered out of \textbf{the} hand of our \textbf{en}emies * \textbf{---} might \textbf{serve} him without fear.
	
	In holiness and righ\textbf{teous}ness be\textbf{fore} him * \textbf{---} \textbf{all} the days of our life.
	
	And thou, child, shalt be called the Pro\textbf{phet} of the \textbf{High}est * for thou shalt \textbf{go} before the face of the \textbf{Lord} to prepare his ways.
	
	To give knowledge of salvation \textbf{un}to his \textbf{peo}ple * \textbf{---} for the \textbf{re}mission of their sins.
	
	Through the ten\textbf{der} mercy of \textbf{our} God * whereby the \textbf{day}spring from on high \textbf{hath} visited us.
	
	To give light to them that sit in darkness and in \textbf{the} shadow \textbf{of} death * and to \textbf{guide} our feet \textbf{in}to the way of peace.
	
	Glory be to \textbf{the} Father, and \textbf{to} the Son * \textbf{---} \textbf{and} to the Holy Spirit.
	
	As it was in the beginning, is now, \textbf{and} ever \textbf{shall} be * \textbf{---} \textbf{world} without end. Amen.
\end{multicols}