\begin{multicols}{2}
	And hath raised up a mighty sal\textbf{va}tion \textbf{for} us * in the house of his \textbf{ser}vant \textbf{Da}vid.
	
	As he spake by the mouth of his \textbf{ho}ly \textbf{Pro}phets * which have been \textbf{since} the \textbf{world} began.
	
	That we should be saved \textbf{from} our \textbf{en}emies * and from the hand of \textbf{all} who \textbf{hate} us.
	
	To perform the mercy promised \textbf{to} our \textbf{fore}fathers * and to remember his \textbf{ho}ly \textbf{cov}enant. 
	
	To perform the oath which he sware to our \textbf{fore}father \textbf{A}braham * that \textbf{he} would \textbf{give} us.
	
	That we being delivered out of the hand \textbf{of} our \textbf{en}emies * might \textbf{serve} him with\textbf{out} fear.
	
	In holiness and \textbf{right}eousness \textbf{be}fore him * \textbf{---} all the days \textbf{of} our life.
	
	And thou, child, shalt be called the Prophet \textbf{of} the \textbf{High}est * for thou shalt go before the face of the \textbf{Lord} to pre\textbf{pare} his ways.
	
	To give knowledge of salvation un\textbf{to} his \textbf{peo}ple * for the re\textbf{mis}sion \textbf{of} their sins.
	
	Through the tender \textbf{mer}cy \textbf{of} our God * whereby the dayspring from on high hath \textbf{vi}sit\textbf{e}d us.
	
	To give light to them that sit in darkness and in the \textbf{sha}dow \textbf{of} death * and to guide our feet in\textbf{to} the \textbf{way} of peace.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}it.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}