\begin{multicols}{2}
	I am as \textbf{glad} of \textbf{thy} word * as one who findeth \textbf{great} spoils.
	
	As for lies, I hate \textbf{and} ab\textbf{hor} them * but thy \textbf{law} do I love.
	
	Seven times a day \textbf{do} I \textbf{praise} thee * because of thy right\textbf{eous} judgments.
	
	Great is the peace that they \textbf{have} who \textbf{love} thy law * and they are not offend\textbf{ed} at it.
	
	Lord, I have looked for \textbf{thy} sal\textbf{va}tion * and done after thy \textbf{com}mandments.
	
	My soul hath kept thy \textbf{tes}ti\textbf{mo}nies * and loved them \textbf{ex}ceedingly.
	
	I have kept thy commandments and \textbf{tes}ti\textbf{mo}nies * for all my ways are \textbf{be}fore thee.
	
	Let my complaint come be\textbf{fore} thee, \textbf{O} Lord * give me understanding accord\textbf{ing} to thy word.
	
	Let my supplication \textbf{come} be\textbf{fore} thee * deliver me accord\textbf{ing} to thy word.
	
	My lips shall \textbf{speak} of \textbf{thy} praise * when thou hast taught me \textbf{thy} statutes.
	
	Yea, my tongue shall \textbf{sing} of \textbf{thy} word * for all thy commandments \textbf{are} righteous.
	
	Let \textbf{thine} hand \textbf{help} me * for I have chosen thy \textbf{com}mandments.
	
	I have longed for thy sal\textbf{va}tion, \textbf{O} Lord * and in thy law \textbf{is} my delight.
	
	O let my soul live, and \textbf{it} shall \textbf{praise} thee * and thy judgments \textbf{shall} help me.
	
	I have gone astray like a \textbf{sheep} that \textbf{is} lost * O seek thy servant, for I do not forget thy \textbf{com}mandments.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the Ho\textbf{ly} Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world without \textbf{end}. Amen.
\end{multicols}