\begin{multicols}{2}
	I am \textbf{as} glad of thy word * as one that \textbf{find}eth great spoils.
	
	As for lies, I hate \textbf{and} abhor them * \textbf{but} thy law do I love.
	
	Seven times a day \textbf{do} I praise thee * because of \textbf{thy} righteous judgments.
	
	Great is the peace that they \textbf{have} who love thy law * and they are not \textbf{of}fended at it.
	
	Lord, I have looked for \textbf{thy} salvation * and done af\textbf{ter} thy commandments.
	
	My soul hath kept thy \textbf{tes}timonies * and \textbf{loved} them exceedingly.
	
	I have kept thy commandments and \textbf{tes}timonies * for all my \textbf{ways} are before thee.
	
	Let my complaint come \textbf{be}fore thee, O Lord * give me understanding \textbf{ac}cording to thy word.
	
	Let my supplication \textbf{come} before thee * deliver me \textbf{ac}cording to thy word.
	
	My lips \textbf{shall} speak of thy praise * when thou hast \textbf{taught} me thy statutes.
	
	Yea, my tongue \textbf{shall} sing of thy word * for all thy com\textbf{mand}ments are righteous.
	
	Let \textbf{thine} hand help me * for I have cho\textbf{sen} thy commandments.
	
	I have longed for thy sal\textbf{va}tion, O Lord * and in \textbf{thy} law is my delight.
	
	O let my soul live, and \textbf{it} shall praise thee * and thy \textbf{judg}ments shall help me.
	
	I have gone astray like \textbf{a} sheep that is lost * O seek thy servant, for I do not for\textbf{get} thy commandments.
	
	Glory be to the Fath\textbf{er}, and to the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now and \textbf{ev}er shall be * world \textbf{with}out end. Amen.
\end{multicols}