\begin{multicols}{2}
	I am as glad \textbf{of} thy word * as one that \textbf{find}eth great \textbf{spoi}ls.
	
	As for lies, I hate and ab\textbf{hor} them * but thy \textbf{law} do \textbf{I} love.
	
	Seven times a day do I \textbf{praise} thee * because of thy \textbf{right}eous \textbf{judg}ments.
	
	Great is the peace that they have who \textbf{love} thy law * and they are not of\textbf{fend}ed \textbf{at} it.
	
	Lord, I have looked for thy sal\textbf{va}tion * and done after \textbf{thy} com\textbf{mand}ments.
	
	My soul hath kept thy testi\textbf{mo}nies * and loved \textbf{them} ex\textbf{cee}dingly.
	
	I have kept thy commandments and testi\textbf{mo}nies * for all my \textbf{ways} are be\textbf{fore} thee.
	
	Let my complaint come before \textbf{thee}, O Lord * give me understanding ac\textbf{cord}ing \textbf{to} thy word.
	
	Let my supplication come be\textbf{fore} thee * deliver me ac\textbf{cord}ing \textbf{to} thy word.
	
	My lips shall speak \textbf{of} thy praise * when thou hast \textbf{taught} me thy \textbf{stat}utes.
	
	Yea, my tongue shall sing \textbf{of} thy word * for all thy com\textbf{mand}ments are \textbf{right}eous.
	
	Let thine hand \textbf{help} me * for I have chosen \textbf{thy} com\textbf{mand}ments.
	
	I have longed for thy salvation, \textbf{O} Lord * and in thy \textbf{law} is \textbf{my} delight.
	
	O let my soul live, and it shall \textbf{praise} thee * and thy \textbf{judg}ments shall \textbf{help} me.
	
	I have gone astray like a sheep \textbf{that} is lost * O seek thy servant, for I do not for\textbf{get} thy com\textbf{mand}ments.
	
	Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}it.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}