\begin{multicols}{2}
	I am as \textbf{glad} of \textbf{thy} word * as one that \textbf{find}eth great \textbf{spoi}ls.
	
	As for lies, I \textbf{hate} and ab\textbf{hor} them * but thy \textbf{law} do \textbf{I} love.
	
	Seven times a \textbf{day} do I \textbf{praise} thee * because of thy \textbf{righ}teous \textbf{judg}ments.
	
	Great is the peace that they \textbf{have} who love \textbf{thy} law * and they are not of\textbf{fend}ed \textbf{at} it.
	
	Lord, I have looked for \textbf{thy} sal\textbf{va}tion * and done after \textbf{thy} com\textbf{mand}ments.
	
	My soul hath kept thy \textbf{tes}tim\textbf{on}ies * and loved \textbf{them} ex\textbf{cee}dingly.
	
	I have kept thy commandments and \textbf{te}sti\textbf{mo}nies * for all my \textbf{ways} are be\textbf{fore} thee.
	
	Let my complaint come be\textbf{fore} thee, \textbf{O} Lord * give me understanding ac\textbf{cord}ing to \textbf{thy} word.
	
	Let my supplication \textbf{come} be\textbf{fore} thee * deliver me ac\textbf{cord}ing to \textbf{thy} word.
	
	My lips shall \textbf{speak} of \textbf{thy} praise * when thou hast taught \textbf{me} thy \textbf{stat}utes.
	
	Yea, my tongue shall \textbf{sing} of \textbf{thy} word * for all thy com\textbf{mand}ments are \textbf{righ}teous.
	
	\textbf{Let} thine hand \textbf{help} me * for I have chosen \textbf{thy} com\textbf{mand}ments.
	
	I have longed for thy sal\textbf{va}tion, \textbf{O} Lord * and in thy \textbf{law} is my \textbf{de}light.
	
	O let my soul live, and \textbf{it} shall \textbf{praise} thee * and thy \textbf{judg}ments shall \textbf{help} me.
	
	I have gone astray like a \textbf{sheep} that \textbf{is} lost * O seek thy servant, for I do not for\textbf{get} thy com\textbf{mand}ments.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}rit.
	
	As it was in the beginning, is now and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}