\begin{multicols}{2}
	The kings of the earth stand up, and the rulers take \textbf{coun}sel to\textbf{ge}ther * against the Lord, and against his \textbf{A}nointed.
	
	Let us break their \textbf{bonds} a\textbf{sun}der * and cast away \textbf{their} cords from us.
	
	He who dwelleth in heaven shall \textbf{laugh} them \textbf{to} scorn * the Lord shall have them in \textbf{der}ision.
	
	Then shall he speak unto \textbf{them} in \textbf{his} wrath * and vex them in his sore \textbf{dis}pleasure.
	
	I am appointed King by him over Zion his \textbf{ho}ly \textbf{moun}tain * preaching the command\textbf{ment} of the Lord.
	
	Whereof the Lord \textbf{hath} said un\textbf{to} me * Thou art my Son; this day have I \textbf{be}gotten thee.
	
	Ask of me, and I shall give thee the nations \textbf{for} thine in\textbf{her}itance * and the uttermost parts of the earth for thy \textbf{pos}session.
	
	Thou shalt bruise them with a \textbf{rod} of \textbf{ir}on * and break them in pieces like a pot\textbf{ters'} vessel.
	
	Be wise now there\textbf{fore}, O \textbf{ye} kings * take counsel, ye who are jud\textbf{ges} of the earth.
	
	Serve \textbf{ye} the \textbf{Lord} in fear * and rejoice unto him \textbf{with} reverence.
	
	Lay hold of instruction, lest at any time the \textbf{Lord} be \textbf{an}gry * and ye perish from \textbf{the} righteous way.
	
	When quickly his \textbf{wrath} be \textbf{kind}led * blessed are all they who have put \textbf{their} trust in him.
	
	Glory be to the \textbf{Fa}ther, and \textbf{t}o the Son * and to the Ho\textbf{ly} Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world without \textbf{end}. Amen.
\end{multicols}