\begin{multicols}{2}
	My mouth is enlarged over mine en\textbf{e}mies * because I rejoice in \textbf{thy} salvation.
	
	There is none holy as \textbf{the} Lord * for there is no one beside thee; neither is there any \textbf{rock} like our God.
	
	Talk no more so exceedingly \textbf{proud}ly * let not arrogancy \textbf{come} out of your mouth.
	
	For the Lord is a God of \textbf{know}ledge * and by him \textbf{ac}tions are weighed.
	
	The bows of the mighty men are \textbf{bro}ken * and they who stumbled are \textbf{gird}ed with strength.
	
	They who were full have hired out themselves \textbf{for} bread * and they \textbf{who} were hungry ceased.
	
	So that the barren hath born \textbf{se}ven * and she who hath many children \textbf{is} waxed feeble.
	
	The Lord killeth, and maketh \textbf{a}live * he bringeth down to the \textbf{grave}, and bringeth up.
	
	The Lord maketh poor, and mak\textbf{eth} rich * he bringeth \textbf{low}, and lifteth high.
	
	He raiseth up the poor out of \textbf{the} dust * and lifteth up the beggar \textbf{from} the dunghill.
	
	To set them among \textbf{prin}ces * and to make them inherit the \textbf{throne} of glory.
	
	For the pillars of the earth are \textbf{the} Lord's * and he hath set the \textbf{world} upon them.
	
	He will keep the feet of his saints, and the wicked shall be silent in \textbf{dark}ness * for by strength \textbf{shall} no man prevail.
	
	The adversaries of the Lord shall be broken to \textbf{pie}ces * out of heaven shall he thun\textbf{der} upon them.
	
	The Lord shall judge the ends of \textbf{the} earth * and he shall give strength unto his king, and exalt the horn of \textbf{his} annointed.
	
	Glory be to the Father, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}