\begin{multicols}{2}
	Let my judgment come forth \textbf{from} thy \textbf{pres}ence * and let thine eyes look u\textbf{pon} up\textbf{right}ness.
	
	Thou hast proved and visited mine heart in the night season, thou hast tried me, and shall find no \textbf{wick}edness \textbf{in} me * for I am utterly purposed that my \textbf{mouth} shall \textbf{not} offend.
	
	Because of men's works, that are done against the \textbf{words} of thy \textbf{lips} * I have kept me from the ways \textbf{of} the des\textbf{troy}er.
	
	O hold thou up my \textbf{go}ings \textbf{in} thy paths * that my \textbf{foot}steps \textbf{slip} not.
	
	I have called upon thee, O God, for \textbf{thou} shalt \textbf{hear} me * incline thine ear to me, and \textbf{hear}ken un\textbf{to} my words.
	
	Shew thy marvelous \textbf{lov}ing-\textbf{kind}ness * thou who art the Savior of them who \textbf{put} their \textbf{trust} in thee.
	
	From such as resist thy right hand, keep me as the \textbf{ap}ple \textbf{of} thine eye * hide me under the \textbf{sha}dow \textbf{of} thy wings.
	
	From the un\textbf{god}ly who \textbf{trou}ble me * mine enemies compass me round about to \textbf{take} away \textbf{my} soul.
	
	They are inclosed \textbf{in} their \textbf{own} fat * and their mouth \textbf{speak}eth \textbf{proud} things.
	
	They lie waiting \textbf{in} on \textbf{ev}ery side * turning their eyes \textbf{down} to \textbf{the} ground.
	
	Like as a lion who is \textbf{greed}y \textbf{of} his prey * and as it were a lion's whelp, lurking in \textbf{se}cret \textbf{pla}ces.
	
	Arise, O Lord, disappoint him \textbf{and} cast \textbf{him} down * deliver my soul from the ungodly, which \textbf{is} a \textbf{sword} of thine.
	
	From the men of thy hand, O Lord, from the men, I say, and \textbf{from} the \textbf{ev}il world * who have their portion in this life, whose bellies thou fillest with \textbf{thy} hid \textbf{trea}sure.
	
	They have children \textbf{at} their de\textbf{si}re * and leave the rest of their \textbf{sub}stance \textbf{for} their babes.
	
	But as for me, I will behold thy \textbf{pres}ence in \textbf{right}eousness * and when I awake up after thy likeness, I shall be \textbf{sat}isfied \textbf{with} it.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}it.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}