Hearken, O Lord, unto my righteousness and consider my complaint * hear my prayer that goeth not out of feigned lips.

Let my judgment come forth from thy presence * and let thine eyes look upon uprightness.

Thou hast proved and visited mine heart in the night season, thou hast tried me, and shall find no wickedness in me * for I am utterly purposed that my mouth shall not offend.

Because of men's works, that are done against the words of thy lips * I have kept me from the ways of the destroyer.

O hold thou up my goings in thy paths * that my footsteps slip not.

I have called upon thee, O God, for thou shalt hear me * incline thine ear to me, and hearken unto my words.

Shew thy marvelous loving-kindness * thou who art the Savior of them who put their trust in thee.

From such as resist thy right hand, keep me as the apple of thine eye * hide me under the shadow of thy wings.

From the ungodly who trouble me * mine enemies compass me round about to take away my soul.

They are inclosed in their own fat * and their mouth speaketh proud things.

They lie waiting in on every side * turning their eyes down to the ground.

Like as a lion who is greedy of his prey * and as it were a lion's whelp, lurking in secret places.

Arise, O Lord, disappoint him and cast him down * deliver my soul from the ungodly, which is a sword of thine.

From the men of thy hand, O Lord, from the men, I say, and from the evil world * who have their portion in this life, whose bellies thou fillest with thy hid treasure.

They have children at their desire * and leave the rest of their substance for their babes.

But as for me, I will behold thy presence in righteousness * and when I awake up after thy likeness, I shall be satisfied with it.