\begin{multicols}{2}
	How he \textbf{sware} unto the Lord * and vowed a vow unto the almighty God of \textbf{Ja}cob.
	
	I will not come within the taber\textbf{na}cle of mine house * nor climb up into \textbf{my} bed.
	
	I will not suffer mine eyes to sleep, nor mine eye\textbf{lids} to slumber * neither the temples of my head to take a\textbf{ny} rest.
	
	Until I find out a place for the \textbf{tem}ple of the Lord * a habitation for the mighty God of \textbf{Ja}cob.
	
	Lo, we heard of the \textbf{same} at Ephrata * and found it in \textbf{the} wood.
	
	We will go into his \textbf{ta}bernacle * and fall low on our knees before his \textbf{foot}stool.
	
	Arise, O Lord, in\textbf{to} thy resting place * thou, and the ark of \textbf{thy} strength.
	
	Let thy priests be \textbf{clothed} with righteousness * and let thy saints sing with joy\textbf{ful}ness.
	
	For thy \textbf{ser}vant David's sake * turn not away the presence of thine A\textbf{noin}ted\footnote{The Latin reads \textit{Christi tui.}}.
	
	The Lord hath made a faithful oath \textbf{un}to David * and he shall not shrink \textbf{from} it.
	
	Of the fruit \textbf{of} thy body * shall I set upon \textbf{thy} seat.
	
	If thy children will keep my covenant, and my testimonies that \textbf{I} shall learn them * their children also shall sit upon thy throne fore\textbf{ver}more.
	
	For the Lord hath chosen Zion to be a habi\textbf{ta}tion for himself * he hath longed \textbf{for} her.
	
	This shall be my \textbf{rest} forever * here will I dwell, for I have a delight \textbf{there}in.
	
	I will bless her victu\textbf{als} with increase * and will satisfy her poor \textbf{with} bread.
	
	I will deck her priests \textbf{with} salvation * and her saints shall rejoice \textbf{and} sing.
	
	There shall I make the horn of Da\textbf{vid} to flourish * I have ordained a lantern for mine A\textbf{noin}ted\footnote{Likewise here \textit{Christo meo.}}.
	
	As for her enemies, I \textbf{shall} clothe them with shame * but upon himself shall his crown \textbf{flour}ish.
	
	Glory be to the Fa\textbf{ther}, and to the Son * and to the Holy \textbf{Spir}it.
	
	As it was in the beginning, is now, and \textbf{ev}er shall be * world without end. \textbf{A}men.
\end{multicols}