\begin{multicols}{2}
	How he sware un\textbf{to} the Lord * and vowed a vow unto the almighty \textbf{God} of Jacob.
	
	I will not come within the tabernacle \textbf{of} mine house * nor climb \textbf{up} into my bed.
	
	I will not suffer mine eyes to sleep, nor mine eyelids to \textbf{slum}ber * neither the temples of my head \textbf{to} take any rest.
	
	Until I find out a place for the temple \textbf{of} the Lord * a habitation for the mighty \textbf{God} of Jacob.
	
	Lo, we heard of the same at Eph\textbf{ra}ta * and \textbf{found} it in the wood.
	
	We will go into his taber\textbf{na}cle * and fall low on our knees be\textbf{fore} his footstool.
	
	Arise, O Lord, into thy \textbf{rest}ing place * thou, and \textbf{the} ark of thy strength.
	
	Let thy priests be clothed with \textbf{right}eousness * and let thy saints \textbf{sing} with joyfulness.
	
	For thy servant \textbf{Da}vid's sake * turn not away the presence of \textbf{thine} Anointed\footnote{The Latin reads \textit{Christi tui.}}.
	
	The Lord hath made a faithful oath unto \textbf{Da}vid * and he \textbf{shall} not shrink from it.
	
	Of the fruit of thy \textbf{bo}dy * shall \textbf{I} set upon thy seat.
	
	If thy children will keep my covenant, and my testimonies that I shall \textbf{learn} them * their children also shall sit upon thy \textbf{throne} forevermore.
	
	For the Lord hath chosen Zion to be a habitation \textbf{for} himself * \textbf{he} hath longed for her.
	
	This shall be my rest for\textbf{ev}er * here will I dwell, for I have a \textbf{de}light therein.
	
	I will bless her victuals with \textbf{in}crease * and will satis\textbf{fy} her poor with bread.
	
	I will deck her priests with sal\textbf{va}tion * and her saints \textbf{shall} rejoice and sing.
	
	There shall I make the horn of David to \textbf{flour}ish * I have ordained a lantern for \textbf{mine} Anointed\footnote{Likewise here \textit{Christo meo.}}.
	
	As for her enemies, I shall clothe \textbf{them} with shame * but upon himself shall \textbf{his} crown flourish.
	
	Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world wit\textbf{hout} end. Amen
\end{multicols}