Lord, remember David * and all his trouble.

How he sware unto the Lord * and vowed a vow unto the almighty God of Jacob.

I will not come within the tabernacle of mine house * nor climb up into my bed.

I will not suffer mine eyes to sleep, nor mine eyelids to slumber * neither the temples of my head to take any rest.

Until I find out a place for the temple of the Lord * a habitation for the mighty God of Jacob.

Lo, we heard of the same at Ephrata * and found it in the wood.

We will go into his tabernacle * and fall low on our knees before his footstool.

Arise, O Lord, into thy resting place * thou, and the ark of thy strength.

Let thy priests be clothed with righteousness * and let thy saints sing with joyfulness.

For thy servant David's sake * turn not away the presence of thine Anointed\footnote{The Latin reads \textit{Christi tui.}}.

The Lord hath made a faithful oath unto David * and he shall not shrink from it.

Of the fruit of thy body * shall I set upon thy seat.

If thy children will keep my covenant, and my testimonies that I shall learn them * their children also shall sit upon thy throne forevermore.

For the Lord hath chosen Zion to be a habitation for himself * he hath longed for her.

This shall be my rest forever * here will I dwell, for I have a delight therein.

I will bless her victuals with increase * and will satisfy her poor with bread.

I will dick her priests with salvation * and her saints shall rejoice and sing.

There shall I make the horn of David to flourish * I have ordained a lantern for mine Anointed\footnote{Likewise here \textit{Christo meo.}}.

As for her enemies, I shall clothe them with shame * but upon himself shall his crown flourish.

Glory be to the Father, and to the Son * and to the Holy Spirit.

As it was in the beginning, is now, and ever shall be * world without end. Amen