\begin{multicols}{2}
	Thou, through thy commandments, hast made me wiser \textbf{than} mine \textbf{en}emies * for they are \textbf{ev}er with me.
	
	I have more understanding \textbf{than} my \textbf{tea}chers * for thy testimonies \textbf{are} my study.
	
	I am wiser \textbf{than} mine \textbf{el}ders * because I keep \textbf{thy} commandments.
	
	I have refrained my feet from \textbf{ev}ery e\textbf{vil} way * that \textbf{I} may keep thy word.
	
	I have not shrunk \textbf{from} thy \textbf{jud}gments * \textbf{for} thou teachest me.
	
	O how sweet are thy \textbf{words} unto \textbf{my} throat * yea, sweeter than ho\textbf{ney} unto my mouth.
	
	Through thy commandments I get \textbf{un}der\textbf{stan}ding * therefore I \textbf{hate} all evil ways.
	
	Thy word is a \textbf{lan}tern unto \textbf{my} feet * and a \textbf{light} unto my paths.
	
	I have sworn, and am \textbf{stead}fastly \textbf{pur}posed * to keep thy \textbf{righ}teous judgments.
	
	I am troubled \textbf{a}bove \textbf{mea}sure * quicken me, O Lord, ac\textbf{cord}ing to thy word.
	
	Let the free-will offerings of my mouth \textbf{please} thee, \textbf{O} Lord * and teach \textbf{me} thy judgments.
	
	My soul is \textbf{a}lways in \textbf{my} hand * yet do I \textbf{not} forget thy law.
	
	The ungodly have \textbf{laid} a snare \textbf{for} me * but yet I swerved not from \textbf{thy} commandments.
	
	Thy testimonies have I claimed as mine heri\textbf{tage} for\textbf{ev}er * and why? they are the very \textbf{joy} of my heart.
	
	I have applied my heart to fulfill thy \textbf{stat}utes \textbf{al}ways * e\textbf{ven} unto the end.
	
	Glory be to the \textbf{Fa}ther, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}