\begin{multicols}{2}
	Thou, through thy commandments, hast made me wiser \textbf{than} mine \textbf{en}emies * for they are \textbf{ev}er \textbf{with} me.
	
	I have more understanding \textbf{than} my \textbf{tea}chers * for thy testimonies \textbf{are} my \textbf{stu}dy.
	
	I am wiser \textbf{than} mine \textbf{el}ders * because I keep \textbf{thy} com\textbf{mand}ments.
	
	I have refrained my feet from \textbf{ev}ery \textbf{ev}il way * that \textbf{I} may \textbf{keep} thy word.
	
	I have not shrunk \textbf{from} thy \textbf{judg}ments * \textbf{--} for thou \textbf{tea}chest me.
	
	O how sweet are thy \textbf{words} un\textbf{to} my throat * yea, sweeter than \textbf{hon}ey un\textbf{to} my mouth.
	
	Through thy commandments I get \textbf{un}der\textbf{stand}ing * therefore I \textbf{hate} all \textbf{ev}il ways.
	
	Thy word is a \textbf{lan}tern un\textbf{to} my feet * and a \textbf{light} un\textbf{to} my paths.
	
	I have sworn, and am \textbf{stead}fastly \textbf{pur}posed * to keep thy \textbf{righ}teous \textbf{judg}ments.
	
	I am troubled \textbf{a}bove \textbf{mea}sure * quicken me, O Lord, ac\textbf{cord}ing \textbf{to} thy word.
	
	Let the free-will offerings of my mouth \textbf{please} thee, \textbf{O} Lord * and teach \textbf{me} thy \textbf{judg}ments.
	
	My soul is \textbf{al}ways \textbf{in} my hand * yet do I \textbf{not} forget \textbf{thy} law.
	
	The ungodly have \textbf{laid} a \textbf{snare} for me * but yet I swerved not from \textbf{thy} com\textbf{mand}ments.
	
	Thy testimonies have I claimed as mine herit\textbf{age} for\textbf{ev}er * and why? they are the very \textbf{joy} of \textbf{my} heart.
	
	I have applied my heart to fulfill thy \textbf{stat}utes \textbf{al}ways * \textbf{---} even un\textbf{to} the end.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}it.
	
	As it was in the beginning is now, and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}