\begin{multicols}{2}
	Lord, what love have \textbf{I} unto thy law * all the day long is my study in \textbf{it}.
	
	Thou, through thy commandments, hast made me wiser \textbf{than} mine enemies * for they are ever with \textbf{me}.
	
	I have more understanding \textbf{than} my teachers * for thy testimonies are my stu\textbf{dy}.
	
	I am wiser \textbf{than} mine elders * because I keep thy command\textbf{ments}.
	
	I have refrained my feet from \textbf{ev}ery evil way * that I may keep \textbf{thy} word.
	
	I have not shrunk \textbf{from} thy judgments * for thou teach\textbf{est} me.
	
	O how sweet are thy \textbf{words} unto my throat * yea, sweeter than honey unto \textbf{my} mouth.
	
	Through thy commandments I get \textbf{un}derstanding * therefore I hate all e\textbf{vil} ways.
	
	Thy word is a lan\textbf{tern} unto my feet * and a light unto \textbf{my} paths.
	
	I have sworn, and am stead\textbf{fast}ly purposed * to keep thy righteous judg\textbf{ments}.
	
	I am troubled \textbf{a}bove measure * quicken me, O Lord, according to \textbf{thy} word.
	
	Let the free-will offerings of my \textbf{mouth} please thee, O Lord * and teach me thy judg\textbf{ments}.
	
	My soul is \textbf{al}ways in my hand * yet do I not forget \textbf{thy} law.
	
	The ungodly have \textbf{laid} a snare for me * but yet I swerved not from thy command\textbf{ments}.
	
	Thy testimonies have I claimed as mine heri\textbf{tage} forever * and why? they are the very joy of \textbf{my} heart.
	
	I have applied my heart to fulfill thy \textbf{stat}utes always * even unto \textbf{the} end.
\end{multicols}