\begin{multicols}{2}
	O give thanks unto the \textbf{God} of \textbf{all} gods * for his mercy en\textbf{dur}eth forever.
	
	O thank the \textbf{Lord} of \textbf{all} lords * for his mercy en\textbf{dur}eth forever.
	
	Who alone \textbf{do}eth great \textbf{won}ders * for his mercy en\textbf{dur}eth forever.
	
	Who by his excellent wisdom \textbf{made} the \textbf{hea}vens * for his mercy en\textbf{dur}eth forever.
	
	Who laid out the earth a\textbf{bove} the \textbf{wa}ters * for his mercy en\textbf{dur}eth forever.
	
	Who \textbf{hath} made \textbf{great} lights * for his mercy en\textbf{dur}eth forever.
	
	The \textbf{sun} to \textbf{rule} the day * for his mercy en\textbf{dur}eth forever.
	
	The moon and the stars to \textbf{gov}ern \textbf{the} night * for his mercy en\textbf{dur}eth forever.
	
	Who smote Egypt, \textbf{with} their \textbf{first}born * for his mercy en\textbf{dur}eth forever.
	
	And brought Israel \textbf{from} a\textbf{mong} them * for his mercy en\textbf{dur}eth forever.
	
	With a mighty hand and \textbf{streched} out arm * for his mercy en\textbf{dur}eth forever.
	
	Who divided the \textbf{Red} sea \textbf{in} two parts * for his mercy en\textbf{dur}eth forever.
	
	And made Israel to go \textbf{through} the \textbf{midst} of it * for his mercy en\textbf{dur}eth forever.
	
	But as for Pharaoh and his host, he overthrew them \textbf{in} the \textbf{Red} sea * for his mercy en\textbf{dur}eth forever.
	
	Who lead his people \textbf{through} the \textbf{wild}erness * for his mercy en\textbf{dur}eth forever.
	
	Who \textbf{smote} the \textbf{great} kings * for his mercy en\textbf{dur}eth forever.
	
	Yea, and slew \textbf{migh}ty kings * for his mercy en\textbf{dur}eth forever.
	
	Sehon \textbf{king} of the \textbf{A}morites * for his mercy en\textbf{dur}eth forever.
	
	And Og the \textbf{king} of \textbf{Ba}san * for his mercy en\textbf{dur}eth forever.
	
	And gave away their land \textbf{for} a \textbf{her}itage * for his mercy en\textbf{dur}eth forever.
	
	Even for a heritage unto Isra\textbf{el} his \textbf{ser}vant * for his mercy en\textbf{dur}eth forever.
	
	Who remembered us when we \textbf{were} in \textbf{trou}ble * for his mercy en\textbf{dur}eth forever.
	
	And hath delivered us \textbf{from} our \textbf{en}emies * for his mercy en\textbf{dur}eth forever.
	
	Who giveth \textbf{food} to \textbf{all} flesh * for his mercy en\textbf{dur}eth forever.
	
	O give thanks unto the \textbf{God} of \textbf{hea}ven * for his mercy en\textbf{dur}eth forever.
	
	O give thanks un\textbf{to} the \textbf{Lord} of lords * for his mercy en\textbf{dur}eth forever.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world \textbf{with}out end. Amen.
\end{multicols}