\vesectionp{Introduction}\label{compline:introduction}

	\instruct{Before the service begins, kneel and make these prayers quietly.}
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
	
	Hail Mary, full of grace, the Lord is with thee. Blessed art thou among women and blessed is the fruit of thy womb, Jesus. Holy Mary, Mother of God, pray for us sinners now and at the hour of our death. Amen.
	
	\instruct{Continue kneeling as the officiant begins in a low voice.}
	
	\gresetinitiallines{0}
	\skiplines{0.5}\gabcsnippet{
		(f3) <sp>v</sp> Turn(f) us(hv) then,(h) O(h) God(h) our(h) Sav(g)ior.(hv)
		<sp>r</sp>(::) And(hv) let(h) thine(h) an(h)ger(h) cease(h) from(g) us.(hv)
	}

	\instruct{Stand at the signal as the officiant begins in a higher voice.}
	
	\skiplines{0.5}\gabcsnippet{(c3) <sp>v</sp> O(f) God,(hv) make(h) speed(iv) to(h) save(g) me.(hv) <sp>r</sp>(::) O(hv) Lord,(h) make(h) haste(h) to(h) help(g) me.(hv)}\pagebreak[3]
	
	\instruct{The congregation continues together, turning toward the altar, making a profound bow, and crossing themselves at the invocation of the Holy Trinity here and whenever else:}
	
	\skiplines{0.5}\gabcsnippet{(c3) <sp>a</sp> Glor(h)y(h) be(h) to(h) the(h) Fa(h)ther,(h) and(h) to(h) the(h) Son,(h) (,) and(h) to(h) the(h) Ho(h)ly(h) Spir(g)it.(h) (:) As(h) it(h) was(h) in(h) the(h) be(h)gin(h)ning,(h) is(h) now(h) and(h) ev(h)er(h) shall(g) be:(h) (,) world(h) with(h)out(h) end.(h) A(g)men.(h) (::) A(h)le(hi)lu(h)ia.(hg)}
	
\vesectionp{Psalmody and Propers}

	\instruct{Turn to the \greenribbon and sing the psalms antiphonally, with the cantors alternating leading each verse until the asterisk, then that side of the congregation joining. The antiphons themselves are intoned in like manner by each cantor in turn until the asterisk, then joined by the whole choir; their repetitions are sung by the whole congregation.}

	\instruct{The lector then proclaims the chapter from the capitulary. Respond}
	
	\skiplines{1}\gabcsnippet{(c3) <sp>r</sp> Thanks(h) be(h) to(h) God.(h)}

	\instruct{Turn to the \blueribbon and sing the responsory, hymn, versicle, and canticle. If the first line of the responsory ends \enquote{ii.}, the lector will sing it whole and the congregation echoes; else, he intones it until the asterisk and is then joined by the choir. In all cases, the lector sings the verses and the congregation makes the responses. The precantor intones the first verse of the hymn, and is then joined by the whole congregation. The canticle is sung in like manner as the psalmody.}
	
\vesectionp{Conclusion}\label{compline:conclusion}

	\instruct{All then kneel as the cantors turn back to the \redribbon and sing the kyrie as there appointed.}
	
	\instruct{This completed, all continue kneeling and quietly make this prayer.}
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
	
	\instruct{All then say together in a low voice.}
	
	I confess \textcolor{red}{*} to almighty God and to all the Saints that I have sinned exceedingly in thought, word, and deed: through my fault, through my fault, through my most grievous fault. Therefore I beseech blessed Mary ever-Virgin, blessed Michael the Archangel, blessed John the Baptist, the holy apostles Peter and Paul, all the Saints, and you, brethren, to pray for me to the Lord our God.
	
	\instruct{The officiant alone continues.}
	
	May almighty God \textcolor{red}{\GreCross{17}} have mercy upon us and forgive us all our sins, deliver us from all evil, and bring us to everlasting life. Amen.
	
	\instruct{Stand at the signal as the officiant begins.}
	
	\skiplines{0.5}\gabcsnippet{
		(c3) <sp>v</sp> O(h) Lord,(h) hear(h) my(f) prayer.(g)
		<sp>r</sp>(::) And(h) let(h) my(h) cry(h) come(h) un(h)to(f) thee.(f)
		(::) <sp>v</sp> Let(h) us(g) pray.(h)
	}
	
	\instruct{The officiant will then pray the collect from the collectary. This completed, all respond.}
	
	\skiplines{1}\gabcsnippet{<sp>r</sp> A(gh)men.(h)}
	
	\instruct{Then is said this petition.}
	
	\skiplines{0.5}\gregorioscore{common/compline_conclusion.gabc}
	
	\instruct{All turn back to the \blueribbon and sing the anthem with its versicle and collect. The officiant then says}
	
	\skiplines{1}\gabcsnippet{(c3) Let(h) us(g) pray.(h)}
	
	\instruct{He then prays the prescribed collect from the collectary. All respond.}
	
	\skiplines{0.5}\gabcsnippet{<sp>r</sp> A(gh)men.(h) <sp>v</sp>(::) May(h) the(h) di(h)vine(h) a(h)ssis(h)tance(h) <sp>+</sp> remain(h) with(h) us(h) al(h)ways,(h) and(h) with(h) our(h) ab(h)sent(h) bre(h)thren.(d)
		<sp>r</sp>(::) A(gh)men.(h)
	}
	
	\instruct{All then kneel and make these prayers quietly.}
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
	
	Hail Mary, full of grace, the Lord is with thee. Blessed art thou among women and blessed is the fruit of thy womb, Jesus. Holy Mary, Mother of God, pray for us sinners now and at the hour of our death. Amen.
	
	I believe in God the Father almighty, maker of heaven and earth. And in Jesus Christ his only Son our Lord: who was conceived by the Holy Spirit, born of the Virgin Mary, suffered under Pontius Pilate, was crucified, died, and buried. He descended into hell. The third day he rose again from the dead; he ascended into heaven, and sitteth on the right hand of God the Father almighty. From whence he shall come to judge the living and the dead. I believe in the Holy Spirit, the holy catholic Church, the communion of the Saints, the remission of sins, the resurrection of the body, and the life everlasting. Amen.
	
	\pagebreak[3]