\begin{multicols}{2}
	The same is my comfort in my \textbf{trou}ble * for thy word \textbf{hath} quickened me.

	The proud have had me exceedingly in de\textbf{ri}sion * yet have I not \textbf{shrinked} from thy law.
	
	For I remembered thine everlasting judgments, \textbf{O} Lord * and \textbf{re}ceived comfort.
	
	I am horribly \textbf{a}fraid * for the ungodly that \textbf{for}sake thy law.
	
	Thy statutes have been \textbf{my} songs * in the house \textbf{of} my pilgrimage.
	
	I have thought upon thy Name, O Lord, in the night \textbf{sea}son * \textbf{and} have kept thy law.
	
	This has be\textbf{come} mine * because I kept \textbf{thy} commandments.
	
	Thou art my portion, \textbf{O} Lord * I have promised \textbf{to} keep thy law.
	
	I made my humble petition in thy presence with my \textbf{whole} heart * O be merciful unto me, ac\textbf{cord}ing to thy word.
	
	I called mine own ways to re\textbf{mem}brance * and turned my feet unto thy \textbf{tes}timonies.
	
	I made haste, and prolonged not \textbf{the} time * to keep \textbf{thy} commandments.
	
	The congregation of the ungodly have \textbf{robbed} me * but I have not for\textbf{got}ten thy law.
	
	At midnight I will rise to give thanks un\textbf{to} thee * because of thy \textbf{right}eous judgments.
	
	I am a companion of all them that \textbf{fear} thee * and keep \textbf{thy} commandments.
	
	The earth, O Lord, is full of thy \textbf{mer}cy * O teach \textbf{me} thy statutes.
	
	Glory be to the Father, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}