\begin{multicols}{2}
	The same is my comfort in my \textbf{trou}ble * for thy word hath \textbf{quick}ened me.
	
	The proud have had me exceedingly in de\textbf{ri}sion * yet have I not \textbf{shrinked} from thy law.
	
	For I remembered thine everlasting judgments, \textbf{O} Lord * and re\textbf{ceived} comfort.
	
	I am horrib\textbf{ly} afraid * for the ungodly who \textbf{for}sake thy law.
	
	Thy statutes have \textbf{been} my songs * in the house of \textbf{my} pilgrimage.
	
	I have thought upon thy Name, O Lord, in the night \textbf{sea}son * and \textbf{have} kept thy law.
	
	This has be\textbf{come} mine * because I kept thy \textbf{com}mandments.
	
	Thou art my portion, \textbf{O} Lord * I have promised \textbf{to} keep thy law.
	
	I made my humble petition in thy presence with my \textbf{whole} heart * O be merciful unto me, accord\textbf{ing} to thy word.
	
	I called mine own ways to re\textbf{mem}brance * and turned my feet unto thy tes\textbf{ti}monies.
	
	I made haste, and prolonged \textbf{not} the time * to keep thy \textbf{com}mandments.
	
	The congregation of the ungodly have \textbf{robbed} me * but I have not forgot\textbf{ten} thy law.
	
	At midnight I will rise to give thanks \textbf{un}to thee * because of thy right\textbf{eous} judgments.
	
	I am a companion of all them who \textbf{fear} thee * and keep thy \textbf{com}mandments.
	
	The earth, O Lord, is full of thy \textbf{mer}cy * O teach me \textbf{thy} statutes.
	
	Glory be to the Father, and \textbf{to} the Son * and to the Ho\textbf{ly} Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world without \textbf{end}. Amen.
\end{multicols}