\begin{multicols}{2}
	The same is my comfort \textbf{in} my trouble * for \textbf{thy} word hath quickened me.
	
	The proud have had me exceedingly \textbf{in} derision * yet have \textbf{I} not shrinked from thy law.
	
	For I remembered thine everlasting \textbf{judg}ments, O Lord * \textbf{and} received comfort.
	
	I am hor\textbf{ri}bly afraid * for the ungod\textbf{ly} who forsake thy law.
	
	Thy stat\textbf{utes} have been my songs * in the \textbf{house} of my pilgrimage.
	
	I have thought upon thy Name, O Lord, in \textbf{the} night season * \textbf{and} have kept thy law.
	
	This \textbf{has} become mine * because I \textbf{kept} thy commandments.
	
	Thou art my \textbf{por}tion, O Lord * I have \textbf{pro}mised to keep thy law.
	
	I made my humble petition in thy presence \textbf{with} my whole heart * O be merciful unto me, \textbf{ac}cording to thy word.
	
	I called mine own ways \textbf{to} remembrance * and turned my feet unto \textbf{thy} testimonies.
	
	I made haste, and \textbf{pro}longed not the time * to \textbf{keep} thy commandments.
	
	The congregation of the ungod\textbf{ly} have robbed me * but I have not \textbf{for}gotten thy law.
	
	At midnight I will rise to give \textbf{thanks} unto thee * because of \textbf{thy} righteous judgments.
	
	I am a companion of all \textbf{them} who fear thee * and \textbf{keep} thy commandments.
	
	The earth, O Lord, is full \textbf{of} thy mercy * O \textbf{teach} me thy statutes.
	
	Glory be to the Fath\textbf{er}, and to the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now and \textbf{ev}er shall be * world \textbf{with}out end. Amen.
\end{multicols}