\begin{multicols}{2}
	The same is my comfort \textbf{in} my \textbf{trou}ble * for thy \textbf{word} hath \textbf{quick}ened me.
	
	The proud have had me exceedingly \textbf{in} de\textbf{ri}sion * yet have I not \textbf{shrinked} from \textbf{thy} law.
	
	For I remembered thine everlasting \textbf{judg}ments, \textbf{O} Lord * \textbf{---} and received \textbf{com}fort.
	
	I am \textbf{hor}ribly \textbf{a}fraid * for the ungodly \textbf{who} for\textbf{sake} thy law.
	
	Thy \textbf{stat}utes have \textbf{been} my songs * in the \textbf{house} of my \textbf{pil}grimage.
	
	I have thought upon thy Name, O Lord, \textbf{in} the night \textbf{sea}son * \textbf{---} and have \textbf{kept} thy law.
	
	This \textbf{has} be\textbf{come} mine * because I kept \textbf{thy} com\textbf{mand}ments.
	
	Thou art my \textbf{por}tion, \textbf{O} Lord * I have pro\textbf{mised} to \textbf{keep} thy law.
	
	I made my humble petition in thy presence \textbf{with} my \textbf{whole} heart * O be merciful unto me, ac\textbf{cord}ing \textbf{to} thy word.
	
	I called mine own ways \textbf{to} re\textbf{mem}brance * and turned my feet unto thy \textbf{tes}ti\textbf{mo}nies.
	
	I made haste, and pro\textbf{longed} not \textbf{the} time * to keep \textbf{thy} com\textbf{mand}ments.
	
	The congregation of the un\textbf{god}ly have \textbf{robbed} me * but I have not for\textbf{got}ten \textbf{thy} law.
	
	At midnight I will rise to give \textbf{thanks} un\textbf{to} thee * because of thy \textbf{right}eous \textbf{judg}ments.
	
	I am a companion of \textbf{all} them who \textbf{fear} thee * and keep \textbf{thy} com\textbf{mand}ments.
	
	The earth, O Lord, is \textbf{full} of thy \textbf{mer}cy * O \textbf{teach} me thy \textbf{stat}utes.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}it.
	
	As it was in the beginning is now, and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}