\begin{multicols}{2}
		The same is my comfort in my \textbf{trou}ble * for thy \textbf{word} hath quickened me.
		
		The proud have had me exceedingly in de\textbf{ri}sion * yet have I \textbf{not} shrinked from thy law.
		
		For I remembered thine everlasting judgments, \textbf{O} Lord * and \textbf{re}ceived comfort.
		
		I am horribly \textbf{a}fraid * for the ungodly \textbf{who} forsake thy law.
		
		Thy statutes have \textbf{been} my songs * in the house \textbf{of} my pilgrimage.
		
		I have thought upon thy Name, O Lord, in the night \textbf{sea}son * \textbf{and} have kept thy law.
		
		This has be\textbf{come} mine * because I kept thy com\textbf{mand}ments.
		
		Thou art my portion, \textbf{O} Lord * I have pro\textbf{mised} to keep thy law.
		
		I made my humble petition in thy presence with my \textbf{whole} heart * O be merciful unto me, ac\textbf{cord}ing to thy word.
		
		I called mine own ways to re\textbf{mem}brance * and turned my feet unto thy \textbf{tes}timonies.
		
		I made haste, and prolonged \textbf{not} the time * to keep \textbf{thy} commandments.
		
		The congregation of the ungodly have \textbf{robbed} me * but I have not for\textbf{got}ten thy law.
		
		At midnight I will rise to give thanks \textbf{un}to thee * because of thy \textbf{righ}teous judgments.
		
		I am a companion of all them who \textbf{fear} thee * and keep \textbf{thy} commandments.
		
		The earth, O Lord, is full of thy \textbf{mer}cy * O teach \textbf{me} thy statutes.
		
		Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly Spirit.
		
		As it was in the beginning, is now and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}