\begin{multicols}{2}
	O think upon thy servant, as con\textbf{cern}ing thy word * wherein thou hast caused me to put \textbf{my} trust.
	
	The same is my comfort \textbf{in} my trouble * for thy word hath quick\textbf{ened} me.
	
	The proud have had me exceedingly \textbf{in} derision * yet have I not shrinked from \textbf{thy} law.
	
	For I remembered thine everlasting \textbf{judg}ments, O Lord * and received com\textbf{fort}.
	
	I am hor\textbf{ri}bly afraid * for the ungodly who forsake \textbf{thy} law.
	
	Thy stat\textbf{utes} have been my songs * in the house of my pil\textbf{gri}mage.
	
	I have thought upon thy Name, O Lord, in \textbf{the} night season * and have kept \textbf{thy} law.
	
	This \textbf{has} become mine * because I kept thy command\textbf{ments}.
	
	Thou art my \textbf{por}tion, O Lord * I have promised to keep \textbf{thy} law.
	
	I made my humble petition in thy presence \textbf{with} my whole heart * O be merciful unto me, according to \textbf{thy} word.
	
	I called mine own ways \textbf{to} remembrance * and turned my feet unto thy testimon\textbf{ies}.
	
	I made haste, and \textbf{pro}longed not the time * to keep thy command\textbf{ments}.
	
	The congregation of the ungod\textbf{ly} have robbed me * but I have not forgotten thy \textbf{law}.
	
	At midnight I will rise to \textbf{give} thanks unto thee * because of thy righteous judg\textbf{ments}.
	
	I am a companion of all \textbf{them} who fear thee * and keep thy command\textbf{ments}.
	
	The earth, O Lord, is full \textbf{of} thy mercy * O teach me thy stat\textbf{utes}.
\end{multicols}