\begin{multicols}{2}
	The Lord is \textbf{my} strength and my song * and he is be\textbf{come} my salvation.
	
	He is my God, and I will prepare him a \textbf{ha}bitation * my father's God, and \textbf{I} will exalt him.
	
	The Lord is \textbf{as} a man of war * \textbf{the} Lord is his Name.
	
	Pharaoh's chariots and his host hath he \textbf{cast} into the sea * his chosen captains also are \textbf{drowned} in the Red sea.
	
	The \textbf{depths} have covered them * they sank into \textbf{the} bottom as a stone.
	
	Thy right hand, O Lord, is become glori\textbf{ous} in power * thy right hand, O Lord, hath dashed in \textbf{pie}ces the enemy.
	
	And in the greatness of thine excellency thou hast overthrown them that rose \textbf{up} against thee * thou sentest forth thy wrath, which con\textbf{sumed} them as stubble.
	
	And with the blast of thy nostrils the waters were gathered \textbf{up} together * the floods stood upright as a heap, and the depths were congealed \textbf{in} the heart of the sea.
	
	The enemy said, I will pursue, I will overtake, I will div\textbf{ide} the spoil * my lust shall be sa\textbf{tis}fied upon them.
	
	\textbf{I} will draw my sword * my \textbf{hand} shall destroy them.
	
	Thou didst blow with thy wind, \textbf{the} sea covered them * they sank as lead in \textbf{the} mighty waters.
	
	Who is like unto thee, O \textbf{Lord}, among the gods? * who is like thee, glorious in holiness, fearful in prai\textbf{ses}, doing wonders?
	
	Thou stretchedst \textbf{out} thy right hand * \textbf{the} earth swallowed them.
	
	Thou in thy mercy hast led forth the people \textbf{which} thou hast redeemed * thou hast guided them in thy strength unto thy ho\textbf{ly} habitation.
	
	The people shall \textbf{hear}, and be afraid * sorrow shall take hold of the inhabitants \textbf{of} Philistia.
	
	Then the princes of E\textbf{dom} shall be amazed * the mighty men of Moab, trembling shall take hold of them; all the inhabitants of \textbf{Ca}naan shall melt away.
	
	Fear and dread shall fall upon them; by the greatness of thine arm they shall \textbf{be} as still as stone * till thy people pass over, O Lord, till the people pass over, \textbf{whom} thou hast purchased.
	
	Thou shalt bring them in, and plant them in the mountain of \textbf{thine} inheritance * in the place, O Lord, which thou hast made \textbf{for} thee to dwell in.
	
	In the sanctu\textbf{ar}y, O Lord * which thy \textbf{lands} have established.
	
	\textbf{The} Lord shall reign * for\textbf{ev}er and ever.
	
	For the horse of Pharaoh went in with his chariots and with his horse\textbf{men} into the sea * and the Lord brought out again the waters of \textbf{the} sea upon them.
	
	But the children of Israel \textbf{went} on dry land * \textbf{in} the midst of the sea.
	
	Glory be to the Fa\textbf{ther}, and to the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er shall be * world \textbf{with}out end. Amen.
\end{multicols}