\begin{multicols}{2}
	Day unto day \textbf{pour}eth forth speech * and night unto night \textbf{pro}claimeth knowledge.
	
	There is neither \textbf{speech} nor language * but their voices \textbf{are} heard among them.
	
	Their sound is gone out \textbf{in}to all lands * and their words in\textbf{to} the ends of the world.
	
	In them hath he set a taber\textbf{na}cle for the sun * which cometh forth as a bridegroom out of his chamber, and rejoiceth as a \textbf{gi}ant to run his course.
	
	It goeth forth from the uttermost part of the heavens, and runneth about un\textbf{to} the end again * and there is nothing \textbf{hid} from the heat thereof.
	
	The law of the Lord is an undefiled law, \textbf{con}verting the soul * the testimony of the Lord is sure, and giveth wisdom \textbf{un}to the simple.
	
	The statutes of the Lord are right, \textbf{and} rejoice the heart * the commandment of the Lord is pure, and giv\textbf{eth} light unto the eyes.
	
	The fear of the Lord is clean, and endur\textbf{eth} forever * the judgments of the Lord are true, and right\textbf{eous} altogether.
	
	More to be desired than any gold, yea, \textbf{than} much fine gold * sweeter also than hon\textbf{ey} and the honeycomb.
	
	Moreover, by them \textbf{is} thy servant taught * and in keeping of \textbf{them} there is great reward.
	
	Who can tell how oft \textbf{he} offendeth * O cleanse thou \textbf{me} from my secret faults.
	
	Keep thy servant also from presumptuous sings, lest they get the dom\textbf{in}ion over me * so shall I be undefiled, and inno\textbf{cent} from the great offense.
	
	Let the words of my mouth, and the meditation of my heart, be always accep\textbf{ta}ble in thy sight * O Lord, my strength, \textbf{and} my redeemer.
	
	Glory be to the Fath\textbf{er}, and to the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er shall be * world \textbf{with}out end. Amen.
\end{multicols}