The heavens declare the glory of God * and the firmament sheweth the work of his hands.

Day unto day poureth forth speech * and night unto night proclaimeth knowledge.

There is neither speech nor language * but their voices are heard among them.

Their sound is gone out into all lands * and their words into the ends of the world.

In them hath he set a tabernacle for the sun * which cometh forth as a bridegroom out of his chamber, and rejoiceth as a giant to run his course.

It goeth forth from the uttermost part of the heavens, and runneth about unto the end again * and there is nothing hid from the heat thereof.

The law of the Lord is an undefiled law, coverting the soul * the testimony of the Lord is sure, and giveth wisdom unto the simple.

The statutes of the Lord are right, and rejoice the heart * the commandment of the Lord is pure, and giveth light unto the eyes.

The fear of the Lord is clean, and andureth forever * the judgments of the Lord are true, and righteous altogether.

More to be desired than any gold, yea, than much fine gold * sweeter also than honey and the honeycomb.

Moreover, by them is thy servant taught * and in keeping of them there is great reward.

Who can tell how oft he offendeth * O cleanse thou me from my secret faults.

Keep thy servant also from presumptuous sings, lest they get the dominion over me * so shall I be undefiled, and innocent from the great offense.

Let the words of my mouth, and the meditation of my heart, be always acceptable in thy sight * O Lord, my strength, and my redeemer.