\veant{1}{i. i}
\gregorioscore{ant/spiritu_principali.gabc}

\greannotation{\veformat{Ps. 50}}
\greannotation{\veformat{i. i.}}
\skiplines{1}\gabcsnippet{
	(c4) Have(f) mer(g:?)cy(hr) upon() me,() O() God,() after() thy() great() <b>mer</b>(g)cy(h) <sp>*</sp>(:) according(hr) to() the() multitude() of() thy() mercies() do() away(h) <b>mine</b>(g) of(f)fen(gh)ses.(gr)
}

\input{psalter/50/1}

\repant{ant/spiritu_principali.gabc}

\skiplines{1}\veant{2}{viii. i}
\gregorioscore{ant/in_veritate.gabc}

\greannotation{\veformat{Ps. 142}}
\greannotation{\veformat{viii. i}}
\skiplines{1}\gabcsnippet{
	(c4) Hear(g) my(h) (:?) prayer,(jr) O() Lord,() and() consider() my() de(j)<b>si</b>(k)re(jr) <sp>*</sp>(:) hearken(jr) unto() me() for() thy() truth() and(j) <b>right</b>(i)eous(j)ness'(h) sake.(gr)
}

\input{psalter/142/8}

\skiplines{0}\repant{ant/in_veritate.gabc}

\skiplines{1}\veant{3}{iv. vii}
\gregorioscore{ant/illumina_domine.gabc}


\greannotation{\veformat{Ps. 62}}
\greannotation{\veformat{iv. vii.}}
\skiplines{1}\gabcsnippet{
	(c4) O(hr) <b>God</b>,(g) thou(h) art(i) my(hr) God(h) <sp>*</sp>(:) early(hr) will() I(h) <b>seek</b>(g) thee.(h)
}

\input{psalter/62/4(7)}

\greannotation{\veformat{Ps. 66}}
\greannotation{\veformat{iv. vii.}}
\skiplines{1}\gabcsnippet{
	(c4) God(h) be(g) (:?) merciful(hr) unto(h) <b>us</b>(g) and(h) bless(i) us(hr) <sp>*</sp>(:) and(hr) shew() us() the() light() of() his() countenance,() and() be() merciful() un(h)<b>to</b>(g) us.(h)
}

\input{psalter/66/4(7)}

\skiplines{-1.5}\repant{ant/illumina_domine.gabc}

\skiplines{0}\veant{4}{iv. i}
\gregorioscore{ant/domine_audivi.gabc}

\vecomment{Song of Habakkuk}
\vecomment{Habakkuk iii}

\greannotation{\veformat{Ode}}
\greannotation{\veformat{iv. i.}}
\gabcsnippet{
	(c4) O(hr) Lord,(h) <b>I</b>(g) have(h) heard(i) thy(hr) speech() <sp>*</sp>(:) (hr) <b>and</b>(g) I(h) was(ih) a(gvFE)fraid.(er)
}

\input{psalter/habakkuk3/4}

\repant{ant/domine_audivi.gabc}

\skiplines{1}\veant{5}{i. ii}
\gregorioscore{ant/in_tympano_et_choro.gabc}

\greannotation{\veformat{Ps. 148}}
\greannotation{\veformat{ii. i.}}
\skiplines{1}\gabcsnippet{
	(f3) O(e) praise(f) (:?) the(hr) Lord() of() <b>hea</b>(i)ven(hr) <sp>*</sp>(:) praise(hr) <b>him</b>(g) in(er) the() height.(f)
}

\input{psalter/148/2}

\greannotation{\veformat{Ps. 149}}
\greannotation{\veformat{ii. i.}}
\skiplines{1}\gabcsnippet{
	(f3) O(e) sing(f) (:?) unto(hr) the() Lord() a(h) <b>new</b>(i) song(hr) <sp>*</sp>(:) let() the() congregation() of(h) <b>saints</b>(g) praise(er) him.(f)
}

\input{psalter/149/2}

\greannotation{\veformat{Ps. 150}}
\greannotation{\veformat{ii. i.}}
\clearpage\skiplines{0}\gabcsnippet{
	(f3) O(e) praise(f) (:?) God(hr) in() his() <b>ho</b>(i)li(hr)ness(h) <sp>*</sp>(:) praise(h) him() in() the() firmament() of(h) <b>his</b>(g) pow(er)er.(f)
}

\input{psalter/150/2}

\repant{ant/in_tympano_et_choro.gabc}

\instruct{Turn back to the \whiteribbon for the chapter.}