\veant{1}{vi}
\gregorioscore{ant/miserere_mei_deus.gabc}

\greannotation{\veformat{Ps. 50}}
\greannotation{\veformat{vi.}}
\skiplines{1}\gabcsnippet{
	(c4) Have(f) mer(g:?)cy(hr) upon() me,() O() God,() after() thy() great(h) <b>mer</b>(g)cy(h) <sp>*</sp>(:) according(hr) to() the() multitude() of() thy() mercies() do() away(h) <b>mine</b>(f) of(gh)fen(g)ses.(fr f)
}

\input{psalter/50/6}

\repant{ant/miserere_mei_deus.gabc}


\pagebreak[1]


\skiplines{1}\veant{2}{viii. ii}
\gregorioscore{ant/intellige_clamorem.gabc}

\greannotation{\veformat{Ps. 5}}
\greannotation{\veformat{viii. ii.}}
\skiplines{1}\gabcsnippet{
	(c3) Pon(e)der(f) (:?) my(hr) <b>words</b>,(i) O(hr) Lord(h) <sp>*</sp>(:) consider(hr) my(h) <b>med</b>(f)i(h)ta(i)tion.(hr h)
}

\input{psalter/5/8}

\repant{ant/intellige_clamorem.gabc}


\pagebreak[1]


\skiplines{1}\veant{3}{viii. i}
\gregorioscore{ant/deus_deus_meus.gabc}

\greannotation{\veformat{Ps. 62}}
\greannotation{\veformat{viii. i.}}
\skiplines{1}\gabcsnippet{
	(c4) O(g) God,(h) (:?) thou(jr) <b>art</b>(k) my(jr) God(j) <sp>*</sp>(:) ear(jr)ly(j) <b>will</b>(i) I(j) seek(h) thee.(gr g)
}

\input{psalter/62/8}

\greannotation{\veformat{Ps. 66}}
\greannotation{\veformat{viii. i.}}
\skiplines{1}\gabcsnippet{
	(c4) God(g) be(h) (:?) merciful(jr) unto() us,() and(j) <b>bless</b>(k) us(jr j) <sp>*</sp>(:) and(jr) shew() us() the() light() of() his() countenance,() and() be() mer(j)<b>ci</b>(i)ful(j) un(h)to(gr) us.(g)
}

\input{psalter/66/8}

\repant{ant/deus_deus_meus.gabc}


\pagebreak[1]


\skiplines{1}\veant{4}{viii. i}
\gregorioscore{ant/conversus_est.gabc}

\vecomment{Canticle of Isaiah}
\vecomment{Isaiah xii}

\greannotation{\veformat{Ode.}}
\greannotation{\veformat{viii. i.}}
\gabcsnippet{
	(c3) O(e) Lord,(f) I(hr) will() praise() thee,() though() thou() wast() angry(h) <b>with</b>(i) me(hr h) <sp>*</sp>(:) thine(hr) anger() is() turned() away,() and() thou(h) <b>com</b>(g)fort(h)edst(f) me.(er e)
}

\input{psalter/isaiah12/8}

\repant{ant/conversus_est.gabc}


\pagebreak[1]


\skiplines{1}\veant{5}{i. iv}
\gregorioscore{ant/laudate_dominum_caeli.gabc}

\greannotation{\veformat{Ps. 148}}
\greannotation{\veformat{i. iv.}}
\skiplines{1}\gabcsnippet{
	(c4) O(f) praise(g) (:?) the(hr) Lord() of(h) <b>hea</b>(g)ven(h) <sp>*</sp>(:) (hr) <b>praise</b>(g) him(f) in(g) the(gr) height.(h)
}

\input{psalter/148/1}

\greannotation{\veformat{Ps. 149}}
\greannotation{\veformat{i. iv.}}
\skiplines{1}\gabcsnippet{
	(c4) O(f) sing(g) (:?) unto(hr) the() Lord() a(h) <b>new</b>(g) song(h) <sp>*</sp>(:) let(hr) the() congregation(h) <b>of</b>(g) the(f) saints(g) praise(gr) him.(h)
}

\input{psalter/149/1}

\greannotation{\veformat{Ps. 150}}
\greannotation{\veformat{i. iv.}}
\skiplines{1}\gabcsnippet{
	(c4) O(f) praise(g) (:?) God(hr) in() his() ho(h)<b>li</b>(g)ness(h) <sp>*</sp>(:) praise(hr) him() in() the() firmament(h) <b>of</b>(g) his(f) pow(gr)er.(f)
}

\input{psalter/150/1}

\repant{ant/laudate_dominum_caeli.gabc}