\veant{1}{iv. i}
\gregorioscore{ant/benigne_fac.gabc}

\greannotation{\veformat{Ps. 50}}
\greannotation{\veformat{iv. i.}}
\skiplines{1}\gabcsnippet{
	(f3) Have(j) mer(i:?)cy(jr) upon() me,() O() God,() after(j) <b>thy</b>(i) great(j) mer(k)cy(jr j) <sp>*</sp>(:) according(jr) to() the() multitude() of() thy() mercies() do() a(j)<b>way</b>(i) mine(j) of(kj)fen(ivHG)ses.(gr g)
}

\input{psalter/50/4}

\repant{ant/benigne_fac.gabc}



\pagebreak[1]


\skiplines{1}\veant{2}{viii. ii}
\gregorioscore{ant/bonum_est_confiteri.gabc}

\greannotation{\veformat{Ps. 91}}
\greannotation{\veformat{viii. ii.}}
\clearpage\gabcsnippet{
	(c3) It(e) is(f) (:?) a(hr) good() thing() to() give() thanks() un(h)<b>to</b>(i) the(hr) Lord(h) <sp>*</sp>(:) and(hr) to() sing() praises() unto() thy() Name,(h) <b>O</b>(f) most(h) High(i)est.(hr h)
}

\input{psalter/91/8}

\skiplines{-1}\repant{ant/bonum_est_confiteri.gabc}



\pagebreak[1]


\skiplines{1}\veant{3}{viii. ii}
\gregorioscore{ant/metuant_dominum.gabc}

\greannotation{\veformat{Ps. 62}}
\greannotation{\veformat{viii. i.}}
\skiplines{1}\gabcsnippet{
	(c3) O(e) God,(f) (:?) thou(hr) <b>art</b>(i) my(hr) God(h) <sp>*</sp>(:) ear()ly(hr) <b>will</b>(g) I(h) seek(f) thee.(er e)
}

\input{psalter/62/8}

\greannotation{\veformat{Ps. 66}}
\greannotation{\veformat{viii. i.}}
\clearpage\gabcsnippet{
	(c3) God(e) be(f) (:?) merciful(hr) unto() us,() and(h) <b>bless</b>(i) us(hr h) <sp>*</sp>(:) and(hr) shew() us() the() light() of() his() countenance,() and() be() mer(h)<b>ci</b>(g)ful(h) un(f)to(er) us.(e)
}

\input{psalter/66/8}

\repant{ant/metuant_dominum.gabc}



\pagebreak[1]


\skiplines{1}\veant{4}{iv. i}
\gregorioscore{ant/et_in_servis.gabc}

\vecomment{Song of Moses}
\vecomment{Deuteronomy xxxii, 1-43}

\greannotation{\veformat{Ode}}
\greannotation{\veformat{iv. i.}}
\gabcsnippet{
	(f3) Give(j) ear,(i) (:?) O(jr) ye() hea(j)<b>vens</b>(i) and(j) I(k) will(jr) speak(j) <sp>*</sp>(:) and(jr) hear,() O(j) <b>earth</b>,(i) the(j) words(kj) of(ivHG) my(gr) mouth.(g)
}

\input{psalter/deuteronomy32/4}

\repant{ant/et_in_servis.gabc}



\pagebreak[1]


\skiplines{0}\veant{5}{iv. i}
\gregorioscore{ant/in_cymbalis.gabc}

\greannotation{\veformat{Ps. 148}}
\greannotation{\veformat{iv. i.}}
\skiplines{1}\gabcsnippet{
	(f3) O(j) praise(i) (:?) the(jr) <b>Lord</b>(i) of(j) hea(k)ven(jr j) <sp>*</sp>(:) (jr) <b>praise</b>(i) him(j) in(kj) the(ivHG) height.(gr g)
}

\input{psalter/148/4}

\greannotation{\veformat{Ps. 149}}
\greannotation{\veformat{iv. i.}}
\skiplines{1}\gabcsnippet{
	(f3) O(j) sing(i) (:?) unto(jr) the(j) <b>Lord</b>(i) a(j) new(k) song(jr j) <sp>*</sp>(:) let(jr) the() con(j)gre(j)ga(j)<b>tion</b>(i) of(j) saints(kj) praise(ivHG) him.(gr g)
}

\input{psalter/149/4}

\greannotation{\veformat{Ps. 150}}
\greannotation{\veformat{iv. i.}}
\skiplines{1}\gabcsnippet{
	(f3) O(j) praise(i) (:?) God(jr) <b>in</b>(i) his(j) ho(k)li(jr)ness(j) <sp>*</sp>(:) praise(j) him() in() the() fir(j)ma(j)<b>ment</b>(i) of(j) his(kj) pow(ivHG)er.(gr g)
}

\input{psalter/150/4}

\skiplines{-2}\repant{ant/in_cymbalis.gabc}

\instruct{Turn back to the \whiteribbon for the chapter.}