\veant{1}{iii. iv}
\gregorioscore{ant/regnavit_dominus.gabc}

\greannotation{\veformat{Ps. 92}}
\greannotation{\veformat{iii. iv.}}
\skiplines{1}\gabcsnippet{
	(c3) The(e) Lord(f) (:?) is(hr) King,() and() is(h) <b>clothed</b>(i) with(hr) <b>beau</b>(g)ty(hr) <sp>*</sp>(:) the(hr) Lord() is() clothed() with() majesty,() and() hath() gird--()ed(h) <b>him</b>(f)self(hr) with() strength.(g)
}

\input{psalter/92/3}

\skiplines{-1}\repant{ant/regnavit_dominus.gabc}



\veant{2}{iv. i}
\skiplines{1}\gregorioscore{ant/sciamus_omnes.gabc}

\greannotation{\veformat{Ps. 99}}
\greannotation{\veformat{iv. i.}}
\skiplines{1}\gabcsnippet{
	(c4) O(h) be(g) (:?) joy(hr)ful() in(h) <b>the</b>(f) Lord,(h) all(i) ye(hr) lands() <sp>*</sp>(:) serve(hr) the() Lord() with() gladness,() and() come() before(h) <b>his</b>(g) pres(h)sence(ih) with(gvFE) song.(er)
}

\input{psalter/99/4}

\skiplines{0}\repant{ant/sciamus_omnes.gabc}



\pagebreak[1]



\veant{3}{v. ii}
\skiplines{1}\gregorioscore{ant/benedicam_te_domine.gabc}

\greannotation{\veformat{Ps. 62}}
\greannotation{\veformat{v. ii.}}
\skiplines{1}\gabcsnippet{
	(c3) O(d) God,(f) (:?) thou(hr) <b>art</b>(i) my(hr) God() <sp>*</sp>(:) ear(hr)ly(h) <b>will</b>(i) I(gr) <b>seek</b>(h) thee.(fr) 
}

\input{psalter/62/5}

\greannotation{\veformat{Ps. 66}}
\greannotation{\veformat{v. ii.}}
\skiplines{0}\gabcsnippet{
	(c3) God(d) be(f) (:?) mer(hr)ciful() unto() us,() and(h) <b>bless</b>(i) us(hr) <sp>*</sp>(:) and(hr) shew() the() light() of() his() countenance,() and() be(h) <b>mer</b>(i)ci(gr)ful() <b>un</b>(h)to(fr) us.()
}

\input{psalter/66/5}

\repant{ant/benedicam_te_domine.gabc}


\pagebreak[1]


\veant{4}{iv. i}
\skiplines{1}\gregorioscore{ant/omnis_creatura.gabc}

\vecomment{Song of the Three Children}
\vecomment{Daniel iii, 23-91}

\greannotation{\veformat{Ode.}}
\greannotation{\veformat{iv. i.}}
\gabcsnippet{
	(c4) O(h) all(g) (:?) ye(hr) works() of() the(h) <b>Lord</b>(g) bless(h) ye(i) the(hr) Lord() <sp>*</sp>(:) praise(hr) him,() and() mag--()ni(h)<b>fy</b>(g) him(h) for(ih)ev(gvFE)ver.(er)
}

\input{psalter/daniel3/4}

\clearpage\skiplines{-1}\repant{ant/omnis_creatura.gabc}


\veant{5}{viii. i}
\skiplines{1}\gregorioscore{ant/spiritus_omnis.gabc}


\greannotation{\veformat{Ps. 148}}
\greannotation{\veformat{viii. i.}}
\skiplines{1}\gabcsnippet{
	(c3) O(e) praise(f) (:?) the(hr) Lord() of(h) <b>hea</b>(i)ven(hr) <sp>*</sp>(:) (hr) <b>praise</b>(g) him(h) in(f) the(er) height.()
}

\input{psalter/148/8}

\greannotation{\veformat{Ps. 149}}
\greannotation{\veformat{viii. i.}}
\skiplines{1}\gabcsnippet{
	(c3) O(e) sing(f) (:?) un(hr)to() the() Lord() a(h) <b>new</b>(i) song(hr) <sp>*</sp>(:) let(hr) the() congrega--()tion(h) <b>of</b>(g) saints(h) praise(f) him.(er)
}

\input{psalter/149/8}

\greannotation{\veformat{Ps. 150}}
\greannotation{\veformat{viii. i.}}
\skiplines{1}\gabcsnippet{
	(c3) O(e) praise(f) (:?) God(hr) in() his(h) <b>ho</b>(i)li(hr)ness() <sp>*</sp>(:) praise(h) him() in() the() firma--()ment(h) <b>of</b>(g) his(h) pow(f)er.(er)
}

\input{psalter/150/8}

\skiplines{-1}\repant{ant/spiritus_omnis.gabc}

\instruct{Turn back to the \whiteribbon for the chapter.}