\veant{1}{viii. i}
\gregorioscore{ant/tibi_soli_peccavi.gabc}

\greannotation{\veformat{Ps. 50}}
\greannotation{\veformat{viii. i.}}
\skiplines{1}\gabcsnippet{
	(c3) Have(e) mer(f:?)cy(hr) upon() me,() O() God,() after() thy() great(h) <b>mer</b>(i)cy(hr h) <sp>*</sp>(:) according(hr) to() the() multitude() of() thy() mercies() do() away(h) <b>mine</b>(g) of(h)fen(f)ses.(er e)
}

\input{psalter/50/8}

\repant{ant/tibi_soli_peccavi.gabc}



\pagebreak[1]



\skiplines{1}\veant{2}{vi}
\gregorioscore{ant/domine_refugium.gabc}

\greannotation{\veformat{Ps. 89}}
\greannotation{\veformat{vi.}}
\clearpage\gabcsnippet{
	(c4) Lord,(f) thou(g) (:?) hast(hr) been() our(h) <b>re</b>(g)fuge(h) <sp>*</sp>(:) from(hr) one() generation(h) <b>to</b>(f) a(gh)noth(g)er.(fr f)
}

\input{psalter/89/6}

\repant{ant/domine_refugium.gabc}


\pagebreak[1]


\skiplines{1}\veant{3}{iv. vii}
\gregorioscore{ant/in_matutinis.gabc}

\greannotation{\veformat{Ps. 62}}
\greannotation{\veformat{iv. vii.}}
\skiplines{1}\gabcsnippet{
	(c4) O(hr) <b>God</b>,(g) thou(h) art(i) my(hr) God(h) <sp>*</sp>(:) early(h) will(h) I(h) <b>seek</b>(g) thee.(h)
}

\input{psalter/62/4(7)}

\greannotation{\veformat{Ps. 66}}
\greannotation{\veformat{iv. vii.}}
\skiplines{1}\gabcsnippet{
	(c4) God(h) be(g) (:?) merciful(hr) unto(h) <b>us</b>(g) and(h) bless(i) us(hr h) <sp>*</sp>(:) and(hr) shew() us() the() light() of() his() countenance,() and() be() merciful() un(h)<b>to</b>(g) us.(h)
}

\input{psalter/66/4(7)}

\repant{ant/in_matutinis.gabc}


\pagebreak[1]


\skiplines{1}\veant{4}{iv. i}
\gregorioscore{ant/regnabit_in_eternum.gabc}

\pagebreak[3]

\vecomment{Song of Moses}
\vecomment{Exodus xv}\nopagebreak

\greannotation{\veformat{Ode}}
\greannotation{\veformat{iv. i.}}
\gabcsnippet{
	(c4) I(h) will(g) (:?) sing(hr) unto() the() Lord,() for() he() hath() hath() triumphed(h) <b>glo</b>(g)ri(h)ous(i)ly(hr h) <sp>*</sp>(:) the(hr) horse() and() his() rider() hath(h) <b>he</b>(g) thrown(h) in(ih)to(gvFE) the(er) sea.(e)
}

\input{psalter/exodus15/4}

\repant{ant/regnabit_in_eternum.gabc}




\pagebreak[1]


\skiplines{1}\veant{5}{vi}
\gregorioscore{ant/in_sanctis_ejus.gabc}

\greannotation{\veformat{Ps. 148}}
\greannotation{\veformat{vi.}}
\skiplines{1}\gabcsnippet{
	(c4) O(f) praise(g:?) the(hr) Lord of(h) <b>hea</b>(g)ven(h) <sp>*</sp>(:) (hr) <b>praise</b>(f) him(gh) in(g) the(fr) height.(f)
}

\input{psalter/148/6}

\greannotation{\veformat{Ps. 149}}
\greannotation{\veformat{vi.}}
\skiplines{1}\gabcsnippet{
	(c4) O(f) sing(g:?) unto(hr) the() Lord() a(h) <b>new</b>(g) song(h) <sp>*</sp>(:) let(hr) the() congregation(h) <b>of</b>(f) saints(gh) praise(g) him.(fr f)
}

\input{psalter/149/6}

\greannotation{\veformat{Ps. 150}}
\greannotation{\veformat{vi.}}
\skiplines{1}\gabcsnippet{
	(c4) O(f) praise(g) (:?) God(hr) in() his() ho(h)<b>li</b>(g)ness(h) <sp>*</sp>(:) praise(hr) him() in() the() firmament(h) <b>of</b>(f) his(gh) pow(g)er.(fr f)
}

\input{psalter/150/6}

\repant{ant/in_sanctis_ejus.gabc}

\instruct{Turn back to the \whiteribbon for the chapter.}