\veant{1}{i. iii}
\gregorioscore{ant/secundum_magnam.gabc}

\greannotation{\veformat{Ps. 50}}
\greannotation{\veformat{i. iii.}}
\skiplines{1}\gabcsnippet{
	(c4) Have(f) mer(g:?)cy(hr) upon() me,() O() God,() after() thy() great() <b>mer</b>(g)cy(h) <sp>*</sp>(:) according(hr) to() the() multitude() of() thy() mercies() do() away(h) <b>mine</b>(g) of(f)fen(gr)ses.(ghg)
}

\input{psalter/50/1}

\skiplines{-1}\repant{ant/secundum_magnam.gabc}


\pagebreak[1]


\skiplines{1}\veant{2}{vi}
\gregorioscore{ant/salutare.gabc}

\greannotation{\veformat{Ps. 42}}
\greannotation{\veformat{vi.}}
\skiplines{1}\gabcsnippet{
	(c3) Judge(f) me(g) (:?) O(hr) God,() and() defend() my() cause() against() the() ungod--()ly(h) <b>peo</b>(g)ple(h) <sp>*</sp>(:) O(hr) deliver() me() from() the() de--()ceit(h)<b>ful</b>(f) and(gh) wick(g)ed(fr) man.()
}

\input{psalter/42/6}

\clearpage\skiplines{-1}\repant{ant/salutare.gabc}


\pagebreak[1]


\skiplines{1}\veant{3}{vii. i}
\gregorioscore{ant/ad_te_de_luce.gabc}

\greannotation{\veformat{Ps. 62}}
\greannotation{\veformat{vii. i.}}
\skiplines{1}\gabcsnippet{
	(c3) O(ir) <b>God</b>(k) thou(jr) <b>art</b>(i) my(jr) God(j) <sp>*</sp>(:) ear(ir)ly(i) <b>will</b>(j) I(ir) <b>seek</b>(hr) thee.(gf)
}

\input{psalter/62/7}

\greannotation{\veformat{Ps. 66}}
\greannotation{\veformat{vii. i.}}
\skiplines{0}\gabcsnippet{
	(c3) God(g) be(h:?) merciful(ir) unto(i) <b>us</b>(k) and(jr) <b>bless</b>(i) us(jr j) <sp>*</sp>(:) and(ir) shew() us() the() light() of() his() countenance,() and() be(i) <b>mer</b>(j)ci(ir)ful(i) <b>un</b>(h)to(hr) us.(gf)
}

\input{psalter/66/7}

\skiplines{0}\repant{ant/ad_te_de_luce.gabc}


\skiplines{1}\veant{4}{iii. iv}
\gregorioscore{ant/cunctis_diebus.gabc}

\clearpage\vecomment{Song of Hezekiah}
\vecomment{Isaiah xxxviii, 10-20}

\greannotation{\veformat{Ode}}
\greannotation{\veformat{iii. iv.}}
\gabcsnippet{
	(c3) I(g) said(h:?) in(jr) the() cutting(j) <b>off</b>(k) of(jr) <b>my</b>(i) days(jr j) <sp>*</sp>(:) I(jr) shall() go() to() the(j) <b>gates</b>(h) of(j) the(jr) grave.(i)
}

\input{psalter/isaiah38/3}

\clearpage\skiplines{-1}\repant{ant/cunctis_diebus.gabc}

\skiplines{1}\veant{5}{vi}
\gregorioscore{ant/in_excelsis.gabc}

\greannotation{\veformat{Ps. 148}}
\greannotation{\veformat{vi.}}
\skiplines{1}\gabcsnippet{
	(c4) O(f) praise(g:?) the(hr) Lord() of(h) <b>hea</b>(g)ven(h) <sp>*</sp>(:) (hr) <b>praise</b>(f) him(gh) in(g) the(fr) height.()
}

\input{psalter/148/6}

\greannotation{\veformat{Ps. 149}}
\greannotation{\veformat{vi.}}
\clearpage\gabcsnippet{
	(c4) O(f) sing(g:?) unto(hr) the() Lord() a(h) <b>new</b>(g) song(h) <sp>*</sp>(:) let(hr) the() congregation(h) <b>of</b>(f) saints(gh) praise(g) him.(fr)
}

\input{psalter/149/6}

\greannotation{\veformat{Ps. 150}}
\greannotation{\veformat{vi.}}
\skiplines{1}\gabcsnippet{
	(c4) O(f) praise(g) (:?) God(hr) in() his() ho(h)<b>li</b>(g)ness(h) <sp>*</sp>(:) praise(hr) him() in() the() firmament(h) <b>of</b>(f) his(gh) pow(g)er.(fr)
}

\input{psalter/150/6}

\repant{ant/in_excelsis.gabc}

\instruct{Turn back to the \whiteribbon for the chapter.}