\veant{1}{viii. i}
\gregorioscore{ant/amplius_lava_me.gabc}

\greannotation{\veformat{Ps. 50}}
\greannotation{\veformat{viii. i.}}
\skiplines{1}\gabcsnippet{
	(c3) Have(e) mer(f:?)cy(hr) upon() me,() O() God,() after() thy() great(h) <b>mer</b>(i)cy(hr h) <sp>*</sp>(:) according(hr) to() the() multitude() of() thy() mercies() do() away(h) <b>mine</b>(g) of(h)fen(f)ses.(er e)
}

\input{psalter/50/8}

\repant{ant/amplius_lava_me.gabc}


\pagebreak[1]


\skiplines{1}\veant{2}{viii. ii}
\gregorioscore{ant/te_decet_hymnis.gabc}

\greannotation{\veformat{Ps. 64}}
\greannotation{\veformat{viii. ii.}}
\clearpage\gabcsnippet{
	(c3) Thou,(e) O(f) (:?) God(hr) art() praised() in(h) <b>Zi</b>(i)on.(hr h) <sp>*</sp>(:) and(hr) unto() thee() shall() the() vow() be() performed(h) <b>in</b>(f) Je(h)ru(i)sa(hr)lem.(h)
}

\input{psalter/64/8}

\skiplines{-2}\repant{ant/te_decet_hymnis.gabc}




\skiplines{1}\veant{3}{viii. i}
\gregorioscore{ant/labia_mea_laudabunt.gabc}

\greannotation{\veformat{Ps. 62}}
\greannotation{\veformat{viii. i.}}
\skiplines{1}\gabcsnippet{
	(c3) O(e) God,(f) (:?) thou(hr) <b>art</b>(i) my(hr) God(h) <sp>*</sp>(:) ear()ly(hr) <b>will</b>(g) I(h) seek(f) thee.(er e)
}

\input{psalter/62/8}

\greannotation{\veformat{Ps. 66}}
\greannotation{\veformat{viii. i.}}
\clearpage\gabcsnippet{
	(c3) God(e) be(f) (:?) merciful(hr) unto() us,() and(h) <b>bless</b>(i) us(hr h) <sp>*</sp>(:) and(hr) shew() us() the() light() of() his() countenance,() and() be() mer(h)<b>ci</b>(g)ful(h) un(f)to(er) us.(e)
}

\input{psalter/66/8}

\repant{ant/labia_mea_laudabunt.gabc}


\pagebreak[1]


\skiplines{1}\veant{4}{i. iii}
\gregorioscore{ant/dominus_judicabit.gabc}

\vecomment{Song of Hannah}
\vecomment{1 Samuel ii, 1-10}

\greannotation{\veformat{Ode}}
\greannotation{\veformat{i. iii.}}
\gabcsnippet{
	(c4) My(f) heart(g) (:?) rejoiceth(hr) in(h) <b>the</b>(g) Lord(h) <sp>*</sp>(:) mine(hr) horn() is() ex(h)<b>al</b>(g)ted(f) in(g) the(gr) Lord.(ghg)
}

\input{psalter/1samuel2/1}

\skiplines{-2}\repant{ant/dominus_judicabit.gabc}



\skiplines{1}\veant{5}{ii. i}
\gregorioscore{ant/celi_celorum.gabc}

\greannotation{\veformat{Ps. 148}}
\greannotation{\veformat{ii. i.}}
\skiplines{1}\gabcsnippet{
	(f3) O(e) praise(f) (:?) the(hr) Lord() of() <b>hea</b>(i)ven(hr h) <sp>*</sp>(:) praise(hr) <b>him</b>(g) in(e) the(er) height.(f)
}

\skiplines{0}\input{psalter/148/2}

\greannotation{\veformat{Ps. 149}}
\greannotation{\veformat{ii. i.}}
\skiplines{1}\gabcsnippet{
	(f3) O(e) sing(f) (:?) unto(hr) the() Lord() a(h) <b>new</b>(i) song(hr h) <sp>*</sp>(:) let() the() congregation() of(h) <b>saints</b>(g) praise(er) him.(f)
}

\input{psalter/149/2}

\greannotation{\veformat{Ps. 150}}
\greannotation{\veformat{ii. i.}}
\skiplines{1}\gabcsnippet{
	(f3) O(e) praise(f) (:?) God(hr) in() his() <b>ho</b>(i)li(hr)ness(h) <sp>*</sp>(:) praise(h) him() in() the() firmament() of(h) <b>his</b>(g) pow(er)er.(f)
}

\input{psalter/150/2}

\repant{ant/celi_celorum.gabc}

\instruct{Turn back to the \whiteribbon for the chapter.}