\begin{multicols}{2}
	Thou art about \textbf{my} path, and a\textbf{bout} my bed * and \textbf{spi}est out all my ways.
	
	For lo, there is not a \textbf{word} in \textbf{my} tongue * but thou, O Lord, knowest \textbf{it} altogether.
	
	Thou hast fashioned me be\textbf{hind} and \textbf{be}fore * and laid \textbf{thine} hand upon me.
	
	Such knowledge is too wonderful and \textbf{ex}cellent \textbf{for} me * I can\textbf{not} attain unto it.
	
	If I climb up into \textbf{hea}ven, \textbf{thou} art there * if I go down to hell, \textbf{thou} art there also.
	
	If I take the wings \textbf{of} the \textbf{morn}ing * and remain in the ut\textbf{ter}most parts of the sea.
	
	Even there also shall \textbf{thy} hand \textbf{lead} me * and thy \textbf{right} hand shall hold me.
	
	If I say, Peradventure the \textbf{dark}ness shall \textbf{co}ver me * then shall \textbf{my} night be turned to day.
	
	Yea, the darkness is no darkness with thee, but the night is as \textbf{clear} as \textbf{the} day * the darkness and light \textbf{to} thee are both alike.
	
	For my \textbf{reins} are thine * thou hast covered \textbf{me} in my mother's womb.
	
	I will give thanks unto thee, for I am fearfully and \textbf{won}der\textbf{ful}ly made * marvelous are thy works, and that my \textbf{soul} knoweth right well.
	
	My bones \textbf{are} not \textbf{hid} from thee * though I be made secretly, and fa\textbf{shioned} beneath in the earth.
	
	Thine eyes did see my substance, yet \textbf{be}ing im\textbf{per}fect * and in thy book were all \textbf{my} members written.
	
	Which day by \textbf{day} were \textbf{fa}shioned * when as \textbf{yet} there was none of them.
	
	How dear are thy counsels \textbf{un}to \textbf{me}, O God * O how \textbf{great} is the sum of them.
	
	If I tell them, they are more in \textbf{num}ber \textbf{than} the sand * when I wake up, I \textbf{am} present with thee.
	
	Wilt thou not slay the \textbf{wick}ed, \textbf{O} God? * depart from \textbf{me}, ye bloodthirsty men.
	
	For they speak unrighteous\textbf{ly} a\textbf{gainst} thee * and thine ene\textbf{mies} take thy Name in vain.
	
	Do not I hate them, O \textbf{Lord}, that \textbf{hate} thee * and am not I grieved with those that \textbf{rise} up against thee?
	
	Yea, I \textbf{hate} them \textbf{right} sore * even as though \textbf{they} were mine enemies.
	
	Try me, O God, and seek the \textbf{ground} of \textbf{my} heart * prove me, and \textbf{ex}amine my thoughts.
	
	Look well if there be any way of \textbf{wick}edness \textbf{in} me * and lead me in the \textbf{way} everlasting.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world \textbf{with}out end. Amen.
\end{multicols}