\begin{multicols}{2}
	Thou art about my path, \textbf{and} a\textbf{bout} my bed * and \textbf{spi}est out \textbf{all} my ways.
	
	For lo, there is \textbf{not} a word \textbf{in} my tongue * but thou, O Lord, knowest it \textbf{al}to\textbf{ge}ther.
	
	Thou hast fashioned me behind \textbf{and} before * and laid thine \textbf{hand} u\textbf{pon} me.
	
	Such knowledge is too wonderful and \textbf{ex}cellent \textbf{for} me * I cannot \textbf{at}tain \textbf{un}to it.
	
	Whither shall I go then \textbf{from} thy \textbf{Spir}it? * or whither shall I go then \textbf{from} thy \textbf{pres}ence?
	
	If I climb up into \textbf{hea}ven, \textbf{thou} art there * if I go down to hell, thou \textbf{art} there \textbf{al}so.
	
	If I take the wings \textbf{of} the \textbf{morn}ing * and remain in the utter\textbf{most} parts \textbf{of} the sea.
	
	Even there also \textbf{shall} thy hand \textbf{lead} me * and thy \textbf{right} hand shall \textbf{hold} me.
	
	If I say, Peradventure the \textbf{dark}ness shall \textbf{co}ver me * then shall my \textbf{night} be \textbf{turned} to day.
	
	Yea, the darkness is no darkness with thee, but the \textbf{night} is \textbf{clear} as day * the darkness and light to \textbf{thee} are \textbf{both} alike.
	
	For my \textbf{reins} are thine * thou hast covered me \textbf{in} my \textbf{mo}ther's womb.
	
	I will give thanks unto thee, for I am fearfully and \textbf{won}der\textbf{ful}ly made * marvelous are thy works, and that my soul \textbf{know}eth \textbf{right} well.
	
	My bones \textbf{are} not \textbf{hid} from thee * though I be made secretly, and fashioned \textbf{be}neath \textbf{in} the earth.
	
	Thine eyes did see my substance, yet \textbf{be}ing im\textbf{per}fect * and in thy book were all my \textbf{mem}bers \textbf{writ}ten.
	
	Which day by \textbf{day} were \textbf{fash}ioned * when as yet \textbf{there} were \textbf{none} of them.
	
	How dear are thy counsels \textbf{un}to \textbf{me}, O God * O how \textbf{great} is the \textbf{sum} of them.
	
	If I tell them, they are more in \textbf{num}ber \textbf{than} the sand * when I wake up, I am \textbf{pres}ent \textbf{with} thee.
	
	Wilt thou not slay the \textbf{wick}ed, \textbf{O} God * depart from me, \textbf{ye} blood-\textbf{thirs}ty men.
	
	For they speak unrighteous\textbf{ly} a\textbf{gainst} thee * and thine enemies \textbf{take} thy \textbf{Name} in vain.
	
	Do not I hate them, O \textbf{Lord}, that \textbf{hate} thee? * and am not I grieved with those that rise \textbf{up} a\textbf{gainst} thee?
	
	Yea, I \textbf{hate} them \textbf{right} sore * even as though they \textbf{were} mine \textbf{en}emies.
	
	Try me, O God, and \textbf{seek} the ground \textbf{of} my heart * prove me, and ex\textbf{am}ine \textbf{my} thoughts.
	
	Look well if there be any way of \textbf{wick}edness \textbf{in} me * and lead me in the way \textbf{ev}er\textbf{last}ing.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}it.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}