\begin{multicols}{2}
	Thou art about my path, \textbf{and} about my bed * and spiest out all \textbf{my} ways.
	
	For lo, there is not \textbf{a} word in my tongue * but thou, O Lord, knowest it altoge\textbf{ther}.
	
	Thou hast fashioned me \textbf{be}hind and before * and laid thine hand upon \textbf{me}.
	
	Such knowledge is too wonderful and ex\textbf{cel}lent for me * I cannot attain un\textbf{t}o it.
	
	Whither shall I go then \textbf{from} thy Spirit? * or whither shall I go then from thy pres\textbf{ence}?
	
	If I climb up into \textbf{hea}ven, thou art there * if I go down to hell, thou art there al\textbf{so}.
	
	If I take the wings \textbf{of} the morning * and remain in the uttermost parts of \textbf{the} sea.
	
	Even there also shall \textbf{thy} hand lead me * and thy right hand shall hold \textbf{me}.
	
	If I say, Now the dark\textbf{ness} shall cover me * then shall my night be turned \textbf{to} day.
	
	Yea, the darkness is no darkness with thee, but the \textbf{night} is clear as day * the darkness and light to thee are both \textbf{a}like.
	
	For \textbf{my} reins are thine * thou hast covered me in my mot\textbf{her's} womb.
	
	I will give thanks unto thee, for I am fearfully and \textbf{won}derfully made * marvelous are thy works, and that my soul knoweth right \textbf{well}.
	
	My bones \textbf{are} not hid from thee * though I be made secretly, and fashioned beneath in \textbf{the} earth.
	
	Thine eyes did see my substance, yet be\textbf{ing} imperfect * and in thy book were all my members writ\textbf{ten}.
	
	Which day by \textbf{day} were fashioned * when as yet there were none \textbf{of} them.
	
	How dear are thy counsels \textbf{un}to me, O God * O how great is the sum \textbf{of} them.
	
	If I tell them, they are more in \textbf{num}ber than the sand * when I wake up, I am present with \textbf{thee}.
	
	Wilt thou not slay the \textbf{wick}ed, O God * depart from me, ye blood-thirs\textbf{ty} men.
	
	For they speak unrighteous\textbf{ly} against thee * and thine enemies take thy Name \textbf{in} vain.
	
	Do not I hate them, O \textbf{Lord}, who hate thee? * and am not I grieved with those who rise up against \textbf{thee}?
	
	Yea, I \textbf{hate} them right sore * even as though they were mine en\textbf{e}mies.
	
	Try me, O God, and seek \textbf{the} ground of my heart * prove me, and examine my \textbf{thoughts}.
	
	Look well if there be any way of wick\textbf{ed}ness in me * and lead me in the way everlast\textbf{ing}.
\end{multicols}