\begin{multicols}{2}
	O Lord my God, I cried \textbf{un}to thee * and \textbf{thou} hast saved me.
	
	Thou, Lord, hast brought my soul \textbf{out} of hell * thou hast kept my life from them who go \textbf{down} into the pit.
	
	Sing praise unto the Lord, \textbf{O} ye saints * and give thanks unto him for a remembrance \textbf{of} his holiness.
	
	For his wrath endureth but the twinkling \textbf{of} an eye * heaviness may endure for a night, but joy cometh \textbf{in} the morning.
	
	And in my prosperity I said, I shall ne\textbf{ver} be moved * thou, Lord, of thy goodness hast made strong \textbf{as} a mountain.
	
	Thou didst turn thy \textbf{face} from me * and I \textbf{was} then troubled.
	
	Then cried I unto \textbf{thee}, O Lord * and gat me to my \textbf{Lord} right humbly.
	
	What profit is there \textbf{in} my blood * when I go \textbf{down} into the pit?
	
	Shall the dust give thanks \textbf{un}to thee? * or shall \textbf{it} declare thy truth?
	
	Hear, O Lord, and have mercy u\textbf{pon} me * Lord, be \textbf{thou} my helper.
	
	Thou hast turned my heaviness \textbf{in}to joy * thou hast put off my sackcloth, and girded \textbf{me} with gladness.
	
	Therefore shall every good man sing of thy praise without \textbf{ceas}ing * O my God, I will give thanks unto \textbf{thee} forever.
	
	Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}