\begin{multicols}{2}
	Thou art \textbf{my} defense \textbf{and} shield * and my \textbf{trust} is in thy word.
	
	Away from \textbf{me}, ye \textbf{wick}ed * I will keep the com\textbf{mand}ments of my God.
	
	O establish me according to thy \textbf{word} that I \textbf{may} live * and let me not be disap\textbf{poin}ted of my hope.
	
	Hold thou me up, and \textbf{I} shall \textbf{be} safe * yea, my delight shall be ever \textbf{in} thy statutes.
	
	Thou hast trodden down all them that de\textbf{part} from thy \textbf{stat}utes * for they i\textbf{ma}gine but deceit.
	
	Thou puttest away all the ungodly \textbf{of} the earth \textbf{like} dross * therefore I love thy \textbf{tes}timonies.
	
	My flesh \textbf{trem}bleth for fear \textbf{of} thee * and I am afraid \textbf{of} thy judgments.
	
	I deal with the thing that is \textbf{law}ful \textbf{and} right * O give me not over unto \textbf{mine} oppressors.
	
	Make thou thy servant to delight in \textbf{that} which \textbf{is} good * that the proud \textbf{do} me no wrong.
	
	Mine eyes was wasted away with looking for \textbf{thy} sal\textbf{va}tion * and for the word \textbf{of} thy righteousness.
	
	O deal with thy servant according unto thy \textbf{lov}ing \textbf{mer}cy * and teach \textbf{me} thy statutes.
	
	I am thy servant, O grant me \textbf{un}der\textbf{stand}ing * that I may know thy \textbf{tes}timonies.
	
	It is time for thee, O Lord, to \textbf{lay} to \textbf{thine} hand * for they have \textbf{made} void thy law.
	
	For I \textbf{love} thy com\textbf{mand}ments * above \textbf{gold} and precious stones.
	
	Therefore hold I straight \textbf{all} thy com\textbf{mand}ments * and all false ways I \textbf{ut}terly abhor.
	
	Glory be to the \textbf{Fa}ther, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}