\begin{multicols}{2}
	Thou art my defense \textbf{and} shield * and my \textbf{trust} is in thy word.
	
	Away from me, ye \textbf{wick}ed * I will keep the com\textbf{mand}ments of my God.
	
	O establish me according to thy word that I \textbf{may} live * and let me not be disap\textbf{poin}ted of my hope.
	
	Hold thou me up, and I shall \textbf{be} safe * yea, my delight shall be ever \textbf{in} thy statutes.
	
	Thou hast trodden down all them who depart from thy \textbf{stat}utes * for they i\textbf{ma}gine but deceit.
	
	Thou puttest away all the ungodly of the earth \textbf{like} dross * therefore I love thy \textbf{tes}timonies.
	
	My flesh trembleth for fear \textbf{of} thee * and I am afraid \textbf{of} thy judgments.
	
	I deal with the thing that is lawful \textbf{and} right * O give me not over unto \textbf{mine} oppressors.
	
	Make thou thy servant to delight in that which \textbf{is} good * that the proud \textbf{do} me no wrong.
	
	Mine eyes are wasted away with looking for thy sal\textbf{va}tion * and for the word \textbf{of} thy righteousness.
	
	O deal with thy servant according unto thy loving \textbf{mer}cy * and teach \textbf{me} thy statutes.
	
	I am thy servant, O grant me under\textbf{stand}ing * that I may know thy \textbf{tes}timonies.
	
	It is time for thee, O Lord, to lay to \textbf{thine} hand * for they \textbf{have} made void thy law.
	
	For I love thy com\textbf{mand}ments * above \textbf{gold} and precious stones.
	
	Therefore hold I straight all thy com\textbf{mand}ments * and all false ways I \textbf{ut}terly abhor. 
	
	Glory be to the Father, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}