\begin{multicols}{2}
	Thou art my \textbf{de}fense \textbf{and} shield * and my \textbf{trust} is \textbf{in} thy word.
	
	Away from \textbf{me}, ye \textbf{wick}ed * I will keep the com\textbf{mand}ments \textbf{of} my God.
	
	O establish me according to thy \textbf{word} that \textbf{I} may live * and let me not be disap\textbf{poin}ted \textbf{of} my hope.
	
	Hold thou me up, and \textbf{I} shall \textbf{be} safe * yea, my delight shall be ever \textbf{in} thy \textbf{stat}utes.
	
	Thou hast trodden down all them who de\textbf{part} from thy \textbf{stat}utes * for they i\textbf{ma}gine \textbf{but} deceit.
	
	Thou puttest away all the ungodly \textbf{of} the earth \textbf{like} dross * therefore I love thy \textbf{tes}ti\textbf{mo}nies.
	
	My flesh \textbf{trem}bleth for \textbf{fear} of thee * and I am a\textbf{fraid} of thy \textbf{judg}ments.
	
	I deal with the thing that is \textbf{law}ful \textbf{and} right * O give me not over unto \textbf{mine} op\textbf{pres}sors.
	
	Make thou thy servant to delight in \textbf{that} which \textbf{is} good * that the proud \textbf{do} me \textbf{no} wrong.
	
	Mine eyes are wasted away with looking for \textbf{thy} sal\textbf{va}tion * and for the word \textbf{of} thy \textbf{righ}teousness.
	
	O deal with thy servant according unto thy \textbf{lov}ing \textbf{mer}cy * and \textbf{teach} me \textbf{thy} statutes.
	
	I am thy servant, O grant me \textbf{un}der\textbf{stan}ding * that I may know thy \textbf{tes}ti\textbf{mo}nies.
	
	It is time for thee, O Lord, to \textbf{lay} to \textbf{thine} hand * for they have \textbf{made} void \textbf{thy} law.
	
	For I love \textbf{thy} com\textbf{mand}ments * above \textbf{gold} and \textbf{pre}cious stones.
	
	Therefore hold I straight all \textbf{thy} com\textbf{mand}ments * and all false ways I \textbf{ut}ter\textbf{ly} abhor. 
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}it.
	
	As it was in the beginning is now, and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}