\begin{multicols}{2}
	I hate them that i\textbf{ma}gine evil things * but thy law do \textbf{I} love.
	
	Thou art \textbf{my} defense and shield * and my trust is in \textbf{thy} word.
	
	Away from \textbf{me}, ye wicked * I will keep the commandments of \textbf{my} God.
	
	O establish me according to thy \textbf{word} that I may live * and let me not be disappointed of \textbf{my} hope.
	
	Hold thou me up, \textbf{and} I shall be safe * yea, my delight shall be ever in thy stat\textbf{utes}.
	
	Thou hast trodden down all them that depart \textbf{from} thy statutes * for they imagine but \textbf{de}ceit.
	
	Thou puttest away all the ungodly \textbf{of} the earth like dross * therefore I love thy testimon\textbf{ies}.
	
	My flesh trembl\textbf{eth} for fear of thee * and I am afraid of thy judg\textbf{ments}.
	
	I deal with the thing that is \textbf{law}ful and right * O give me not over unto mine oppres\textbf{sors}.
	
	Make thou thy servant to delight \textbf{in} that which is good * that the proud do me \textbf{no} wrong.
	
	Mine eyes are wasted away with looking for \textbf{thy} salvation * and for the word of thy right\textbf{eous}ness.
	
	O deal with thy servant according unto thy \textbf{lov}ing mercy * and teach me thy stat\textbf{utes}.
	
	I am thy servant, O grant me \textbf{un}derstanding * that I may know thy testimon\textbf{ies}.
	
	It is time for thee, O Lord, \textbf{to} lay to thine hand * for they have made void \textbf{thy} law.
	
	For I love \textbf{thy} commandments * above gold and pre\textbf{cious} stones.
	
	Therefore hold I straight all \textbf{thy} commandments * and all false ways I utterly \textbf{ab}hor. 
\end{multicols}