\begin{multicols}{2}
	Every day will I give thanks \textbf{un}to thee * and praise thy Name forev\textbf{er} and ever.
	
	Great is the Lord, and marvelous, worthy \textbf{to} be praised * there is no end \textbf{of} his greatness.
	
	One generation shall praise thy works unto a\textbf{noth}er * and de\textbf{clare} thy power.
	
	As for me, I will be talking of thy \textbf{wor}ship * thy glory, thy \textbf{praise}, and wondrous works.
	
	So that men shall speak of the might of thy marve\textbf{lous} acts * and I will also tell \textbf{of} thy greatness.
	
	The memorial of thine abundant kindness \textbf{shall} be shewed * and men shall sing \textbf{of} thy righteousness.
	
	The Lord is gracious and \textbf{mer}ciful * long-suffering, and \textbf{of} great goodness.
	
	The Lord is loving unto \textbf{ev}ery man * and his mercy is \textbf{ov}er all his works.
	
	All thy works praise \textbf{thee}, O Lord * and thy saints \textbf{give} thanks unto thee.
	
	They shew the glory of thy \textbf{king}dom * and talk \textbf{of} thy power.
	
	That thy power, thy glory, and mightiness of thy \textbf{king}dom * might \textbf{be} known unto men.
	
	Thy kingdom is an everlasting \textbf{king}dom * and thy dominion endureth through\textbf{out} all ages.
	
	The Lord upholdeth all \textbf{such} as fall * and lifteth up all \textbf{those} who are down.
	
	The eyes of all wait upon \textbf{thee}, O Lord * and thou givest them their meat \textbf{in} due season.
	
	Thou openest \textbf{thine} hand * and fillest all things liv\textbf{ing} with plenteousness.
	
	The Lord is righteous in \textbf{all} his ways * and ho\textbf{ly} in all his works.
	
	The Lord is nigh unto all them that call up\textbf{on} him * yea, all such as call up\textbf{on} him faithfully.
	
	He will fulfill the desire of them that \textbf{fear} him * he also will hear their cry, \textbf{and} will help them.
	
	The Lord preserveth all who \textbf{love} him * but scattereth abroad all \textbf{the} ungodly.
	
	My mouth shall speak the praise \textbf{of} the Lord * and let all flesh give thanks unto his holy Name forev\textbf{er} and ever.
	
	Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}