\begin{multicols}{2}
	I am deprived of the residue \textbf{of} my years * I said, I shall not see the Lord, even the Lord in the land of \textbf{the} living.
	
	I shall behold \textbf{man} no more * with the inhabit\textbf{ants} of the world.
	
	Mine age is de\textbf{part}ed * and is removed from me as \textbf{a} shepherd's tent.
	
	I have cut off like a wea\textbf{ver} my life * he will cut me off with pin\textbf{ing} sickness.
	
	From day even \textbf{to} night * wilt thou make \textbf{an} end of me.
	
	I reckoned till morning that, as a lion, so will he break \textbf{all} my bones * from day even to night wilt thou make \textbf{an} end of me.
	
	Like a crane or swallow, so did I \textbf{chat}ter * I did \textbf{mourn} as a dove.
	
	Mine eyes fail with looking \textbf{up}ward * O Lord, I am oppressed, under\textbf{take} for me.
	
	What shall I say? he hath both spoken unto me, and himself hath \textbf{done} it * I shall go softly all my years in the bitter\textbf{ness} of my soul.
	
	O Lord, by these things men live, and in all these things is the life of my \textbf{spi}rit * so wilt thou recover me, and \textbf{make} me to live.
	
	Behold, for peace I had great bitterness, but thou hast in love to my soul delivered it from the pit of cor\textbf{rup}tion * for thou hast cast all my sins \textbf{be}hind my back.
	
	For the grave cannot praise thee, death cannot cele\textbf{brate} thee * they who go down into the pit cannot \textbf{hope} for thy truth.
	
	The living, the living, he shall praise thee as I \textbf{do} this day * the father to his children shall \textbf{make} known thy truth.
	
	The Lord was ready to save me, therefore we will \textbf{sing} our psalms * all the days of our life in the \textbf{house} of the Lord.
\end{multicols}