\begin{multicols}{2}
	I am deprived of the \textbf{re}sidue \textbf{of} my years * I said, I shall not see the Lord, even the Lord in the land of \textbf{the} living.
	
	I shall be\textbf{hold} man \textbf{no} more * with the inhabi\textbf{tants} of the world.
	
	Mine \textbf{age} is de\textbf{part}ed * and is removed from me as \textbf{a} shepherd's tent.
	
	I have cut off like a \textbf{wea}ver \textbf{my} life * he will cut me off with pi\textbf{ning} sickness.
	
	From day \textbf{ev}en \textbf{to} night * wilt thou make \textbf{an} end of me.
	
	I reckoned till morning that, as a lion, so will he \textbf{break} all \textbf{my} bones * from day even to night wilt thou make \textbf{an} end of me.
	
	Like a crane or swallow, \textbf{so} did I \textbf{chat}ter * I did \textbf{mourn} as a dove.
	
	Mine eyes fail with \textbf{look}ing \textbf{up}ward * O Lord, I am oppressed, un\textbf{der}take for me.
	
	What shall I say? he hath both spoken unto me, and him\textbf{self} hath \textbf{done} it * I shall go softly all my years in the bitter\textbf{ness} of my soul.
	
	O Lord, by these things men live, and in all these things is the \textbf{life} of my \textbf{spir}it * so wilt thou recover me, and \textbf{make} me to live.
	
	Behold, for peace I had great bitterness, but thou hast in love to my soul delivered it from the \textbf{pit} of cor\textbf{ru}ption * for thou hast cast all my sins \textbf{be}hind my back.
	
	For the grave cannot praise thee, death cannot \textbf{ce}le\textbf{brate} thee * they that go down into the pit cannot \textbf{hope} for thy truth.
	
	The living, the living, he shall praise thee \textbf{as} I \textbf{do} this day * the father to his children shall \textbf{make} known thy truth.
	
	The Lord was ready to save me, therefore \textbf{we} will \textbf{sing} our psalms * all the days of our life in the \textbf{house} of the Lord.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the Ho\textbf{ly} Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world without \textbf{end}. Amen.
\end{multicols}