I said in the cutting off of my days * I shall go to the gates of the grave.

I am deprived of the residue of my years * I said, I shall not see the Lord, even the Lord in the land of the living.

I shall behold man no more * with the inhabitants of the world.

Mine age is departed * and is removed from me as a shepherd's tent.

I have cut off like a weaver my life * he will cut me off with pining sickness.

From day even to night * wilt thou make an end of me.

I reckoned till morning that, as a lion, so will he break all my bones * from day even to night wilt thou make an end of me.

Like a crane or swallow, so did I chatter * I did mourn as a dove.

Mine eyes fail with looking upward * O Lord, I am oppressed, undertake for me.

What shall I say? he hath both spoken unto me, and himself hath done it * I shall go softly all my years in the bitterness of my soul.

O Lord, by these things men live, and in all these things is the life of my spirit * so wilt thou recover me, and make me to live.

Behold, for peace I had great bitterness, but thou hast in love to my soul delivered it from the pit of corruption * for thou hast cast all my sins behind my back.

For the grave cannot praise thee, death cannot celebrate thee * they that go down into the pit cannot hope for thy truth.

The living, the living, he shall praise thee as I do this day * the father to his children shall make known thy truth.

The Lord was ready to save me, therefore we will sing our psalms * all the days of our life in the house of the Lord.