\begin{multicols}{2}
	The Lord is the strength of \textbf{my} life * of whom then \textbf{shall} I be afraid?
	
	When the wicked, even mine enemies and my foes, came upon me to eat up \textbf{my} flesh * they \textbf{stum}bled and fell.
	
	Though a host of men were laid against me, yet shall not my heart be \textbf{a}fraid * and though there rose up war against me, yet will I \textbf{put} my trust in him.
	
	One thing I have desired of the Lord, that I may dwell in the house of the Lord all the days of \textbf{my} life * to behold the fair beauty of the Lord, and to vis\textbf{it} his temple.
	
	For in the time of trouble he shall hide me in his taber\textbf{na}cle * yea, in the secret place of his dwelling shall he hide me, and set me u\textbf{pon} a rock of stone.
	
	And now shall he lift up \textbf{mine} head * above mine enemies \textbf{round} about me.
	
	Therefore will I offer in his dwelling an oblation with great \textbf{glad}ness * I will sing and speak prai\textbf{ses} unto the Lord.
	
	Hearken unto my voice, O Lord, when I cry un\textbf{to} thee * have mercy upon \textbf{me}, and hear me.
	
	My heart hath said of thee, Seek ye \textbf{my} face * Thy face, \textbf{O} Lord, will I seek.
	
	O hide not thou thy face \textbf{from} me * nor cast thy servant away \textbf{in} displeasure.
	
	Thou hast been my \textbf{suc}cor * leave me not, neither forsake me, O God of \textbf{my} salvation.
	
	When my father and my mother for\textbf{sake} me * the Lord \textbf{tak}eth me up.
	
	Teach me thy way, \textbf{O} Lord * and lead me in the right way, because \textbf{of} mine enemies.
	
	Deliver me not over into the will of mine adver\textbf{sar}ies * for there are false witnesses risen up against me, and \textbf{such} as speak wrong.
	
	I should utterly have \textbf{per}ished * but that I believe  to see the goodness of the Lord in the land \textbf{of} the living.
	
	O expect thou the Lord, and let thy heart take \textbf{cour}age * be strong, and put thou thy trust \textbf{in} the Lord.
	
	Glory be to the Father, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}