\begin{multicols}{2}
	The Lord is \textbf{the} strength of my life * of whom \textbf{then} shall I be afraid?
	
	When the wicked, even mine enemies and my foes, came upon me \textbf{to} eat up my flesh * \textbf{they} stumbled and fell.
	
	Though a host of men were laid against me, yet shall not \textbf{my} heart be afraid * and though there rose up war against me, yet will \textbf{I} put my trust in him.
	
	One thing I have desired of the Lord, that I may dwell in the house of the Lord all \textbf{the} days of my life * to behold the fair beauty of the Lord, and to \textbf{vi}sit his temple.
	
	For in the time of trouble he shall hide me in his \textbf{ta}bernacle * yea, in the secret place of his dwelling shall he hide me, and set me \textbf{up}on a rock of stone.
	
	And now shall \textbf{he} lift up mine head * above mine ene\textbf{mies} round about me.
	
	Therefore will I offer in his dwelling an oblation \textbf{with} great gladness * I will sing and speak \textbf{prai}ses unto the Lord.
	
	Hearken unto my voice, O Lord, when \textbf{I} cry unto thee * have mercy u\textbf{po}n me, and hear me.
	
	My heart hath said of \textbf{thee}, Seek ye my face * Thy \textbf{face}, O Lord, will I seek.
	
	O hide not \textbf{thou} thy face from me * nor cast thy servant a\textbf{way} in displeasure.
	
	Thou hast \textbf{been} my succor * leave me not, neither forsake me, O God \textbf{of} my salvation.
	
	When my father and my mo\textbf{ther} forsake me * the \textbf{Lord} taketh me up.
	
	Teach \textbf{me} thy way, O Lord * and lead me in the right way, be\textbf{cause} of mine enemies.
	
	Deliver me not over into the will of mine \textbf{ad}versaries * for there are false witnesses risen up against me, \textbf{and} such as speak wrong.
	
	I should utter\textbf{ly} have perished * but that I believe  to see the goodness of the Lord in the \textbf{land} of the living.
	
	O expect thou the Lord, and let thy \textbf{heart} take courage * be strong, and put \textbf{thou} thy trust in the Lord.
\end{multicols}