The Lord is my light and my salvation * whom therefore shall I fear?

The Lord is the strength of my life * of whom then shall I be afraid?

When the wicked, even mine enemies and my foes, came upon me to eat up my flesh * they stumbled and fell.

Though a host of men were laid against me, yet shall not my heart be afraid * and though there rose up war against me, yet will I put my trust in him.

One thing I have desired of the Lord, that I may dwell in the house of the Lord all the days of my life * to behold the fair beauty of the Lord, and to visit his temple.

For in the time of trouble he shall hide me in his tabernacle * yea, in the secret place of his dwelling shall he hide me, and set me upon a rock of stone.

And now shall he lift up mine head * above mine enemies round about me.

Therefore will I offer in his dwelling an oblation with great gladness * I will sing and speak praises unto the Lord.

Hearken unto my voice, O Lord, when I cry unto thee * have mercy upon me, and hear me.

My heart hath said of thee, Seek ye my face * Thy face, O Lord, will I seek.

O hide not thou thy face from me * nor cast thy servant away in displeasure.

Thou hast been my succor * leave me not, neither forsake me, O God of my salvation.

When my father and my mother forsake me * the Lord taketh me up.

Teach me thy way, O Lord * and lead me in the right way, because of mine enemies.

Deliver me not over into the will of mine adversaries * for there are false witnesses risen up against me, and such as speak wrong.

I should utterly have perished * but that I believe  to see the goodness of the Lord in the land of the living.

O expect thou the Lord, and let thy heart take courage * be strong, and put thou thy trust in the Lord.