\vesectionp{Introduction}\label{terce:introduction}

	\instruct{Before the service begins, kneel and make these prayers quietly.}
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
	
	Hail Mary, full of grace, the Lord is with thee. Blessed art thou among women and blessed is the fruit of thy womb, Jesus. Holy Mary, Mother of God, pray for us sinners now and at the hour of our death. Amen.
	
	\instruct{Stand as the minister begins from his place:}
	
	\gresetinitiallines{0}
	\skiplines{0.5}\gabcsnippet{(c3) <sp>v</sp> O(f) God,(hv) make(h) speed(iv) to(h) save(g) me.(hv) <sp>r</sp>(::) O(hv) Lord,(h) make(h) haste(h) to(h) help(g) me.(hv)}
	
	\instruct{The congregation continues together, turning toward the altar, making a profound bow, and crossing themselves at the invocation of the Holy Trinity here and whenever else:}
	
	\skiplines{0.5}\gabcsnippet{(c3) <sp>a</sp> Glor(h)y(h) be(h) to(h) the(h) Fa(h)ther,(h) and(h) to(h) the(h) Son,(h) (,) and(h) to(h) the(h) Ho(h)ly(h) Spir(g)it.(h) (:) As(h) it(h) was(h) in(h) the(h) be(h)gin(h)ning,(h) is(h) now(h) and(h) ev(h)er(h) shall(g) be:(h) (,) world(h) with(h)out(h) end.(h) A(g)men.(h) (::) A(h)le(hi)lu(h)ia.(hg)}
	
\vesectionp{Psalmody and Propers}

	\instruct{The minor hours always begin with the hymn. Turn to the \blueribbon and sing it as prescribed there, with the precantor singing the first verse as an intonation, then turn to the \greenribbon and sing the psalms appointed there antiphonally, with each cantor alternating the intonation of each verse until the asterisk, then being joined by that side of the congregation. The antiphons are intoned in like manner, while the full choir joining after the asterisk; their repetitions are sung by the congregation.}
	
	\instruct{The lector then proclaims from the capitulary the chapter. Respond}
	
	\skiplines{1}\gabcsnippet{
		(c3) <sp>r</sp> Thanks(h) be(h) to(h) God.(h)
	} 
	
	\instruct{Turn again to the \blueribbon and sing the responsory appointed there. If the first line of the responsory ends \enquote{ii.}, the lector will sing it whole and the congregation echoes; else, he intones it until the asterisk and is then joined by the choir. In all cases, the lector sings the verses and the congregation makes the responses.}
	
\vesectionp{Conclusion}\label{terce:conclusion}

	\instruct{All then kneel as the cantors turn back to the \redribbon and sing the kyrie as there appointed.}
	
	\instruct{This completed, all continue kneeling and quietly make this prayer.}
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
	
	\instruct{All then say together in a low voice.}
	
	I confess \textcolor{red}{\GreStarHeight{17}} to almighty God and to all the Saints that I have sinned exceedingly in thought, word, and deed: through my fault, through my fault, through my most grievous fault. Therefore I beseech blessed Mary ever-Virgin, blessed Michael the Archangel, blessed John the Baptist, the holy apostles Peter and Paul, all the Saints, and you, brethren, to pray for me to the Lord our God.
	
	\instruct{The officiant alone continues.}
	
	May almighty God \textcolor{red}{\GreCross{17}} have mercy upon us and forgive us all our sins, deliver us from all evil, and bring us to everlasting life. Amen.
	
	\instruct{Stand at the signal as the officiant begins.}
	
	\skiplines{1}\gabcsnippet{
		(c3) <sp>v</sp> O(h) Lord,(h) hear(h) my(f) prayer.(g)
		<sp>r</sp>(::) And(h) let(h) my(h) cry(h) come(h) un(h)to(f) thee.(f)
		(::) <sp>v</sp> Let(h) us(g) pray.(h)
	}
	
	\instruct{The officiant will then pray the collect from the collectary. Respond.}
	
	\skiplines{1}\gabcsnippet{<sp>r</sp> A(gh)men.(h)}
	
	\instruct{This petition concludes the office of Prime, Terce, Sext, and None.}
	
	\skiplines{1}\gregorioscore{common/prime_conclusion.gabc}
	
	\instruct{All then kneel and quietly make this prayer.}
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.