\begin{multicols}{2}
	My hope and my fortress, my castle and deliverer, my defender in whom \textbf{I} trust * who subdueth my people \textbf{that} is under me.
	
	Lord, what is man that thou hast such respect un\textbf{to} him? * or the son of man, that thou \textbf{so} regardest him?
	
	Man is like a thing \textbf{of} nought * his time passeth away \textbf{like} a shadow.
	
	Bow thy heavens, O Lord, and \textbf{come} down * touch the moun\textbf{tains}, and they shall smoke.
	
	Cast forth thy lightning, and \textbf{tear} them * shoot out thine arrows, \textbf{and} consume them.
	
	Send down thine hand from \textbf{a}bove * deliver me, and take me out of the great waters, from the hand \textbf{of} strange children.
	
	Whose mouth talketh of van\textbf{i}ty * and their right hand is a right \textbf{hand} of wickedness.
	
	I will sing a new song unto thee, \textbf{O} God * and sing praises unto thee u\textbf{pon} a ten-stringed lute.
	
	Thou hast given victory un\textbf{to} kings * and hast delivered David thy servant from the \textbf{pe}ril of the sword.
	
	Save me, and deliver me from the hand of strange \textbf{child}ren * whose mouth talketh of vanity, and their right hand is a right hand \textbf{of} iniquity.
	
	That our sons may grow up as the \textbf{young} plants * and that our daughters may be as the polished corners \textbf{of} the temple.
	
	That our garners may be full and plenteous with all manner \textbf{of} store * that our sheep may bring forth thousands and ten \textbf{thou}sands in our streets.
	
	That our oxen may be strong to labor, that there be no \textbf{de}cay * no leading into captivity, and no com\textbf{plain}ing in our streets.
	
	Happy are the people that are in such \textbf{a} case * yea, blessed are the people who have \textbf{the} Lord for their God.
	
	Glory be to the Father, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}