\begin{multicols}{8}
	Thou hast given him his heart's de\textbf{si}re * and hast not denied him the \textbf{re}quest of his lips.
	
	For thou shall prevent him with the blessings of \textbf{good}ness * and shall set a crown of pure \textbf{gold} upon his head.
	
	He asked life of thee, and thou gavest him a \textbf{long} life * even fore\textbf{ve}r and ever.
	
	His honor is great in thy sal\textbf{va}tion * glory and great worship shall thou \textbf{lay} upon him.
	
	For thou shalt given him everlasting fe\textbf{li}city * and make him glad with the joy \textbf{of} thy countenance.
	
	And why? because the King putteth his trust \textbf{in} the Lord * and in the mercy of the most High he shall \textbf{not} miscarry.
	
	All thine enemies shall \textbf{feel} thy hand * thy right and shall find out \textbf{them} who hate thee.
	
	Thou shall make them like a fiery oven in the time \textbf{of} thy wrath * the Lord shall destroy them in his displeasure, and the fire \textbf{shall} consume them.
	
	Their fruit shall thou root out \textbf{of} the earth * and their seed from among the \textbf{child}ren of men.
	
	For they intended mischief a\textbf{gainst} thee * and imagined such a device as they are not \textbf{ab}le to perform.
	
	Therefore shall thou put \textbf{them} to flight * and the strings of thy bow shall thou make ready a\textbf{gainst} the face of them.
	
	Be thou exalted, O Lord, in thine \textbf{own} strength * so will we sing, and \textbf{praise} thy power.
	
	Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}