\begin{multicols}{2}
	When \textbf{thy} word \textbf{go}eth forth * it giveth light and understanding unto \textbf{the} simple.
	
	I opened my mouth, and \textbf{drew} in \textbf{my} breath * for my delight was in thy \textbf{com}mandments.
	
	O look thou upon me, and be \textbf{mer}ciful \textbf{un}to me * as thou usest to do unto those who \textbf{love} thy Name.
	
	Order my \textbf{steps} in \textbf{thy} word * and so shall no wickedness have domin\textbf{ion} over me.
	
	O deliver me from the wrongful \textbf{deal}ings \textbf{of} men * and so shall I keep thy \textbf{com}mandments.
	
	Shew the light of thy countenance u\textbf{pon} thy \textbf{ser}vant * and teach me \textbf{thy} statutes.
	
	Mine eyes gush \textbf{out} with \textbf{wa}ter * because men \textbf{keep} not thy law.
	
	Righteous art \textbf{thou}, O Lord * and true is \textbf{thy} judgment.
	
	The testimonies which thou \textbf{hast} com\textbf{mand}ed * are exceedingly right\textbf{eous} and true.
	
	My zeal hath \textbf{ev}en con\textbf{sum}ed me * because mine enemies have forgot\textbf{ten} thy words.
	
	Thy word is tried \textbf{to} the \textbf{ut}termost * and thy ser\textbf{vant} loveth it.
	
	I am small, and of no \textbf{re}pu\textbf{ta}tion * yet do I not forget thy \textbf{com}mandments.
	
	Thy righteousness is an ever\textbf{las}ting \textbf{righ}teousness * and thy \textbf{law} is the truth.
	
	Trouble and heaviness have \textbf{ta}ken hold u\textbf{pon} me * yet is my delight in thy \textbf{com}mandments.
	
	The righteousness of thy testimonies is \textbf{ev}er\textbf{last}ing * O grant me understanding, \textbf{and} I shall live.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the Ho\textbf{ly} Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world without \textbf{end}. Amen.
\end{multicols}