\begin{multicols}{2}
	When \textbf{thy} word goeth forth * it giveth light and understanding \textbf{un}to the simple.
	
	I opened my mouth, \textbf{and} drew in my breath * for my delight was \textbf{in} thy commandments.
	
	O look thou upon me, and be mer\textbf{ci}ful unto me * as thou usest to do un\textbf{to} those who love thy Name.
	
	Order \textbf{my} steps in thy word * and so shall no wickedness have \textbf{do}minion over me.
	
	O deliver me from the wrongful \textbf{deal}ings of men * and so shall I \textbf{keep} thy commandments.
	
	Shew the light of thy countenance u\textbf{pon} thy servant * and \textbf{teach} me thy statutes.
	
	Mine eyes gush \textbf{out} with water * be\textbf{cause} men keep not thy law.
	
	Righ\textbf{teous} art thou, O Lord * and \textbf{true} is thy judgment.
	
	The testimonies which thou \textbf{hast} commanded * are exceeding\textbf{ly} righteous and true.
	
	My zeal hath e\textbf{ven} consumed me * because mine enemies have \textbf{for}gotten thy words.
	
	Thy word is tried \textbf{to} the uttermost * and \textbf{thy} servant loveth it.
	
	I am small, and of no \textbf{re}putation * yet do I not for\textbf{get} thy commandments.
	
	Thy righteousness is an ever\textbf{las}ting righteousness * \textbf{and} thy law is the truth.
	
	Trouble and heaviness have taken \textbf{hold} upon me * yet is my delight \textbf{in} thy commandments.
	
	The righteousness of thy testimonies is \textbf{ev}erlasting * O grant me under\textbf{stand}ing, and I shall live.
	
	Glory be to the Fath\textbf{er}, and to the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now and \textbf{ev}er shall be * world \textbf{with}out end. Amen.
\end{multicols}