\begin{multicols}{2}
	When thy word \textbf{go}eth forth * it giveth light and understanding \textbf{un}to the \textbf{sim}ple.
	
	I opened my mouth, and drew \textbf{in} my breath * for my delight was in \textbf{thy} com\textbf{mand}ments.
	
	O look thou upon me, and be merciful \textbf{un}to me * as thou usest to do unto \textbf{those} who \textbf{love} thy Name.
	
	Order my steps \textbf{in} thy word * and so shall no wickedness have do\textbf{min}ion \textbf{o}ver me.
	
	O deliver me from the wrongful dealings \textbf{of} men * and so shall I \textbf{keep} thy com\textbf{mand}ments.
	
	Shew the light of thy countenance upon thy \textbf{ser}vant * and \textbf{teach} me thy \textbf{stat}utes.
	
	Mine eyes gush out with \textbf{wa}ter * because \textbf{men} keep \textbf{not} thy law.
	
	Righteous art \textbf{thou}, O Lord * and \textbf{true} is thy \textbf{judg}ment.
	
	The testimonies which thou hast com\textbf{mand}ed * are exceedingly \textbf{right}eous \textbf{and} true.
	
	My zeal hath even con\textbf{sumed} me * because mine enemies have for\textbf{got}ten \textbf{thy} words.
	
	Thy word is tried to the \textbf{ut}termost * and thy \textbf{ser}vant \textbf{lov}eth it.
	
	I am small, and of no repu\textbf{ta}tion * yet do I not for\textbf{get} thy com\textbf{mand}ments.
	
	Thy righteousness is an everlasting \textbf{right}eousness * and thy \textbf{law} is \textbf{the} truth.
	
	Trouble and heaviness have taken hold u\textbf{pon} me * yet is my delight in \textbf{thy} com\textbf{mand}ments.
	
	The righteousness of thy testimonies is ever\textbf{last}ing * O grant me under\textbf{stand}ing, and \textbf{I} shall live.
	
	Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}it.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}