\begin{multicols}{2}
	When \textbf{thy} word \textbf{go}eth forth * it giveth light and understanding \textbf{un}to the \textbf{sim}ple.
	
	I opened my mouth, and \textbf{drew} in \textbf{my} breath * for my delight was in \textbf{thy} com\textbf{mand}ments.
	
	O look thou upon me, and be \textbf{mer}ciful un\textbf{to} me * as thou usest to do unto \textbf{those} that love \textbf{thy} Name.
	
	Order my \textbf{steps} in \textbf{thy} word * and so shall no wickedness have do\textbf{min}ion o\textbf{ver} me.
	
	O deliver me from the wrongful \textbf{deal}ings \textbf{of} men * and so shall I \textbf{keep} thy com\textbf{mand}ments.
	
	Shew the light of thy countenance u\textbf{pon} thy \textbf{ser}vant * and \textbf{teach} me thy \textbf{stat}utes.
	
	Mine eyes gush \textbf{out} with \textbf{wa}ter * because \textbf{men} keep \textbf{not} thy law.
	
	Righ\textbf{teous} art \textbf{thou}, O Lord * and \textbf{true} is thy \textbf{judg}ment.
	
	The testimonies that \textbf{thou} hast com\textbf{mand}ed * are exceedingly \textbf{righ}teous \textbf{and} true.
	
	My zeal hath \textbf{e}ven con\textbf{sum}ed me * because mine enemies have for\textbf{got}ten \textbf{thy} words.
	
	Thy word is tried \textbf{to} the \textbf{ut}termost * and \textbf{thy} servant \textbf{lov}eth it.
	
	I am small, and of \textbf{no} repu\textbf{ta}tion * yet do I not for\textbf{get} thy com\textbf{mand}ments.
	
	Thy righteousness is an ever\textbf{last}ing \textbf{right}eousness * and \textbf{thy} law is \textbf{the} truth.
	
	Trouble and heaviness have taken \textbf{hold} u\textbf{pon} me * yet is my delight in \textbf{thy} com\textbf{mand}ments.
	
	The righteousness of thy testimonies is \textbf{ev}er\textbf{last}ing * O grant me under\textbf{stand}ing, and \textbf{I} shall live.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}rit.
	
	As it was in the beginning, is now and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}