\begin{multicols}{2}
	Give me understanding, and I shall \textbf{keep} thy law * yea, I shall keep it with \textbf{my} whole heart.
	
	Make me to go in the path of thy com\textbf{mand}ments * for therein \textbf{is} my desire.
	
	Incline my heart unto thy testi\textbf{mo}nies * and not to co\textbf{ve}tousness.
	
	O turn away mine eyes, lest they behold \textbf{va}nity * and quicken thou \textbf{me} in thy way.
	
	O establish thy word in thy \textbf{ser}vant * that I \textbf{may} fear thee.
	
	Take away the rebuke that I am a\textbf{fraid} of * for thy judg\textbf{ments} are good.
	
	Behold, my delight is in thy com\textbf{mand}ments * O quicken thou me in \textbf{thy} righteousness.
	
	Let thy loving mercy come also unto \textbf{me}, O Lord * even thy salvation, according \textbf{un}to thy word.
	
	So shall I make answer unto my \textbf{blas}phemers * for my trust \textbf{is} in thy word.
	
	O take not the word of thy truth utterly out \textbf{of} my mouth * for my hope is in \textbf{thy} judgments.
	
	So shall I always \textbf{keep} thy law * yea, forever \textbf{and} ever.
	
	And I will walk at \textbf{li}berty * for I seek thy \textbf{com}mandments.
	
	I will speak of thy testimonies also, even be\textbf{fore} kings * and will not \textbf{be} ashamed.
	
	And my delight shall be in thy com\textbf{mand}ments * which \textbf{I} have loved.
	
	My hands also will I lift up unto thy commandments, which \textbf{I} have loved * and my study shall be in \textbf{thy} statues.
	
	Glory be to the Father, and \textbf{to} the Son * and to the Ho\textbf{ly} Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world without \textbf{end}. Amen.
\end{multicols}