\begin{multicols}{2}
	Give me understanding, and \textbf{I} shall keep thy law * yea, I shall \textbf{keep} it with my whole heart.
	
	Make me to go in the path of \textbf{thy} commandments * for there\textbf{in} is my desire.
	
	Incline my heart unto thy \textbf{tes}timonies * and \textbf{not} to covetousness.
	
	O turn away mine eyes, lest they \textbf{be}hold vanity * and qui\textbf{cken} thou me in thy way.
	
	O establish thy word \textbf{in} thy servant * \textbf{that} I may fear thee.
	
	Take away the rebuke that I \textbf{am} afraid of * for \textbf{thy} judgments are good.
	
	Behold, my delight is in \textbf{thy} commandments * O quicken thou \textbf{me} in thy righteousness.
	
	Let thy loving mercy come also \textbf{un}to me, O Lord * even thy salvation, ac\textbf{cord}ing unto thy word.
	
	So shall I make answer un\textbf{to} my blasphemers * for \textbf{my} trust is in thy word.
	
	O take not the word of thy truth utter\textbf{ly} out of my mouth * for my hope \textbf{is} in thy judgments.
	
	So shall I \textbf{al}ways keep thy law * yea, for\textbf{ev}er and ever.
	
	And I will \textbf{walk} at liberty * for I \textbf{seek} thy commandments.
	
	I will speak of thy testimonies also, e\textbf{ven} before kings * \textbf{and} will not be ashamed.
	
	And my delight shall be in \textbf{thy} commandments * be\textbf{cause} I have loved them.
	
	My hands also will I lift up unto thy command\textbf{ments}, which I have loved * and my study shall \textbf{be} in thy statues.
	
	Glory be to the Fath\textbf{er}, and to the Son * and to \textbf{the} Holy Spirit.
	
	As it was in the beginning, is now and \textbf{ev}er shall be * world \textbf{with}out end. Amen.
\end{multicols}