\begin{multicols}{2}
	Give me understanding, and \textbf{I} shall \textbf{keep} thy law * yea, I shall keep it \textbf{with} my \textbf{whole} heart.
	
	Make me to go in the path of \textbf{thy} com\textbf{mand}ments * for \textbf{there}in is my de\textbf{si}re.
	
	Incline my heart unto thy \textbf{tes}ti\textbf{mo}nies * and not to \textbf{co}ve\textbf{tous}ness.
	
	O turn away mine eyes, lest \textbf{they} behold \textbf{van}ity * and quicken \textbf{thou} me \textbf{in} thy way.
	
	O establish thy word \textbf{in} thy \textbf{ser}vant * that \textbf{I} may \textbf{fear} thee.
	
	Take away the rebuke that \textbf{I} am a\textbf{fraid} of * for thy \textbf{judg}ments \textbf{are} good.
	
	Behold, my delight is in \textbf{thy} com\textbf{mand}ments * O quicken thou me \textbf{in} thy \textbf{right}eousness.
	
	Let thy loving mercy come also \textbf{un}to \textbf{me}, O Lord * even thy salvation, ac\textbf{cord}ing un\textbf{to} thy word.
	
	So shall I make answer unto \textbf{my} blas\textbf{phe}mers * for my \textbf{trust} is \textbf{in} thy word.
	
	O take not the word of thy truth utterly \textbf{out} of \textbf{my} mouth * for my hope is \textbf{in} thy \textbf{judg}ments.
	
	So shall I \textbf{al}ways \textbf{keep} thy law * yea, for\textbf{ev}er and \textbf{ev}er.
	
	And I will \textbf{walk} at \textbf{li}berty * for I seek \textbf{thy} com\textbf{mand}ments.
	
	I will speak of thy testimonies also, \textbf{ev}en be\textbf{fore} kings * and will \textbf{not} be \textbf{a}shamed.
	
	And my delight shall be in \textbf{thy} com\textbf{mand}ments * because \textbf{I} have \textbf{loved} them.
	
	My hands also will I lift up unto thy com\textbf{mand}ments, which \textbf{I} have loved * and my study shall be \textbf{in} thy \textbf{stat}ues.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}it.
	
	As it was in the beginning is now, and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}