\begin{multicols}{2}
	Give me understanding, and I shall \textbf{keep} thy law * yea, I shall keep it \textbf{with} my whole heart.
	
	Make me to go in the path of thy com\textbf{mand}ments * for therein is \textbf{my} desire.
	
	Incline my heart unto thy testi\textbf{mo}nies * and not to \textbf{co}vetousness.
	
	O turn away mine eyes, lest they behold \textbf{van}ity * and quicken \textbf{thou} me in thy way.
	
	O establish thy word in thy \textbf{ser}vant * that \textbf{I} may fear thee.
	
	Take away the rebuke that I am a\textbf{fraid} of * for thy \textbf{judg}ments are good.
	
	Behold, my delight is in thy com\textbf{mand}ments * O quicken thou me \textbf{in} thy righteousness.
	
	Let thy loving mercy come also unto \textbf{me}, O Lord * even thy salvation, accord\textbf{ing} unto thy word.
	
	So shall I make answer unto my \textbf{blas}phemers * for my \textbf{trust} is in thy word.
	
	O take not the word of thy truth utterly out \textbf{of} my mouth * for my hope is \textbf{in} thy judgments.
	
	So shall I always \textbf{keep} thy law * yea, fore\textbf{ver} and ever.
	
	And I will walk at \textbf{lib}erty * for I seek \textbf{thy} commandments.
	
	I will speak of thy testimonies also, even be\textbf{fore} kings * and \textbf{will} not be ashamed.
	
	And my delight shall be in thy com\textbf{mand}ments * because \textbf{I} have loved them.
	
	My hands also will I lift up unto thy commandments, which \textbf{I} have loved * and my study shall be \textbf{in} thy statues.
	
	Glory be to the Father, and \textbf{to} the Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}