\begin{multicols}{2}
	Thou who hearest \textbf{the} prayer * unto \textbf{thee} shall all flesh come.
	
	My misdeeds prevail a\textbf{gainst} me * O be thou merci\textbf{ful} unto our sins.
	
	Blessed is the man whom thou choosest, and receivest \textbf{un}to thee * he shall dwell in thy court, and shall be satisfied with the pleasure of thy \textbf{ho}ly temple.
	
	Thou shalt shew us wonderful things in thy righteousness, O God of our sal\textbf{va}tion * thou who art the hope of all the ends of the earth, and of them who remain \textbf{in} the broad sea.
	
	Who in his strength setteth fast the \textbf{moun}tains * and is girded a\textbf{bout} with power.
	
	Who stilleth the raging \textbf{of} the sea * and the noise of his waves, and the madness \textbf{of} the peoples.
	
	They also who swell in the uttermost parts of the earth shall be afraid \textbf{at} thy signs * thou who makest the outgoings of the morning and eve\textbf{ning} to praise thee.
	
	Thou visitest the earth, and \textbf{bles}sest it * thou makest it \textbf{ve}ry plenteous.
	
	The river of God is full of \textbf{wa}ter * thou preparest their corn, for so thou pro\textbf{vi}dest for the earth.
	
	Thou waterest her furrows, thou sendest rain into the little \textbf{val}leys * thou makest it soft with the drops of rain, and blessest the \textbf{in}crease of it.
	
	Thou crownest the year with thy \textbf{good}ness * and thy \textbf{clouds} drop fatness.
	
	They shall drop upon the dwellings of the \textbf{wil}derness * and the little hills shall re\textbf{joice} on every side.
	
	The folds shall be \textbf{full} of sheep * the valleys also shall stand so thick with corn, \textbf{they} shall laugh and sin.
\end{multicols}