Thou, O God, art praised in Zion * and unto thee shall the vow be performed in Jerusalem.

Thou that hearest the prayer * unto thee shall all flesh come.

My misdeeds prevail against me * O be thou merciful unto our sins.

Blessed is the man whom thou choosest, and receivest unto thee * he shall dwell in thy court, and shall be satisfied with the pleasure of thy holy temple.

Thou shalt shew us wonderful things in thy righteousness, O God of our salvation * thou that art the hope of all the ends of the earth, and of them that remain in the broad sea.

Who in his strength setteth fast the mountains * and is girded about with power.

Who stilleth the raging of the sea * and the noise of his waves, and the madness of the peoples.

They also that swell in the uttermost parts of the earth shall be afraid at thy signs * thou that makest the outgoings of the morning and evening to praise thee.

Thou visitest the earth, and blessest it * thou makest it very plenteous.

The river of God is full of water * thou preparest their corn, for so thou providest for the earth.

Thou waterest her furrows, thou sendest rain into the little valleys * thou makest it soft with the drops of rain, and blessest the increase of it.

Thou crownest the year with thy goodness * and thy clouds drop fatness.

They shall drop upon the dwellings of the wilderness * and the little hills shall rejoice on every side.

The folds shall be full of sheep * the valleys also shall stand so thick with corn, they shall laugh and sin.