\begin{multicols}{2}
	O ye angels of the Lord, bless ye \textbf{the} Lord * O ye hea\textbf{vens}, bless ye the Lord.
	
	O ye waters that be above the firmament, bless ye \textbf{the} Lord * O all ye powers of the \textbf{Lord}, bless ye the Lord.
	
	O ye sun and moon, bless ye \textbf{the} Lord * O ye stars of \textbf{hea}ven, bless ye the Lord.
	
	O ye showers and dew, bless ye \textbf{the} Lord * O ye winds of \textbf{God}, bless ye the Lord.
	
	O ye fire and heat, bless ye \textbf{the} Lord * O ye winter and sum\textbf{mer}, bless ye the Lord.
	
	O ye dews and frosts, bless ye \textbf{the} Lord * O ye frost and \textbf{cold}, bless ye the Lord.
	
	O ye ice and snow, bless ye \textbf{the} Lord * O ye nights and \textbf{days}, bless ye the Lord.
	
	O ye light and darkness, bless ye \textbf{the} Lord * O ye lightnings and \textbf{clouds}, bless ye the Lord.
	
	O let the earth bless \textbf{the} Lord * yea, let it praise him, and magnify \textbf{him} forever.
	
	O ye mountains and hills, bless ye \textbf{the} Lord * O all ye green things upon the \textbf{earth}, bless ye the Lord.
	
	O ye wells, bless ye \textbf{the} Lord * O ye seas and \textbf{floods}, bless ye the Lord.
	
	O ye whales, and all that move in the waters, bless ye \textbf{the} Lord * O all ye fowls of the \textbf{air}, bless ye the Lord.
	
	O all ye beasts and cattle, bless ye \textbf{the} Lord * O ye children of \textbf{man}, bless ye the Lord.
	
	O let Israel bless \textbf{the} Lord * praise him and magnify \textbf{him} forever.
	
	O ye priests of the Lord, bless ye \textbf{the} Lord * O ye servants of the \textbf{Lord}, bless ye the Lord.
	
	O ye spirits and souls of the righteous, bless ye \textbf{the} Lord * O ye holy and humble men of \textbf{heart}, bless ye the Lord.
	
	O Ananias, Azarias, and Misael, bless ye \textbf{the} Lord * praise him, and magnify \textbf{him} forever.
	
	Let us bless the Father, and the Son, with the Holy \textbf{Spir}it * let us praise him, and magnify \textbf{him} forever.
	
	Blessed art thou, O Lord, in the firmament of \textbf{hea}ven * and worthy to be praised, and glorious, and highly exal\textbf{ted} forever.
\end{multicols}