\begin{multicols}{2}
	O ye angels of the Lord, bless \textbf{ye} the Lord * O ye \textbf{hea}vens, bless \textbf{ye} the Lord.
	
	O ye waters that be above the firmament, bless \textbf{ye} the Lord * O all ye powers of the \textbf{Lord}, bless \textbf{ye} the Lord.
	
	O ye sun and moon, bless \textbf{ye} the Lord * O ye stars of \textbf{hea}ven, bless \textbf{ye} the Lord.
	
	O ye showers and dew, bless \textbf{ye} the Lord * O ye winds \textbf{of} God, bless \textbf{ye} the Lord.
	
	O ye fire and heat, bless \textbf{ye} the Lord * O ye winter and \textbf{sum}mer, bless \textbf{ye} the Lord.
	
	O ye dews and frosts, bless \textbf{ye} the Lord * O ye frost and \textbf{cold}, bless \textbf{ye} the Lord.
	
	O ye ice and snow, bless \textbf{ye} the Lord * O ye nights and \textbf{days}, bless \textbf{ye} the Lord.
	
	O ye light and darkness, bless \textbf{ye} the Lord * O ye lightnings and \textbf{clouds}, bless \textbf{ye} the Lord.
	
	O let the earth \textbf{bless} the Lord * yea, let it praise him, and magni\textbf{fy} him for\textbf{ev}er.
	
	O ye mountains and hills, bless \textbf{ye} the Lord * O all ye green things upon the \textbf{earth}, bless \textbf{ye} the Lord.
	
	O ye wells, bless \textbf{ye} the Lord * O ye \textbf{seas} and floods, bless \textbf{ye} the Lord.
	
	O ye whales, and all that move in the waters, bless \textbf{ye} the Lord * O all ye fowls of the \textbf{air}, bless \textbf{ye} the Lord.
	
	O all ye beasts and cattle, bless \textbf{ye} the Lord * O ye children of \textbf{man}, bless \textbf{ye} the Lord.
	
	O let Israel \textbf{bless} the Lord * praise him and magni\textbf{fy} him for\textbf{ev}er.
	
	O ye priests of the Lord, bless \textbf{ye} the Lord * O ye servants of the \textbf{Lord}, bless \textbf{ye} the Lord.
	
	O ye spirits and souls of the righteous, bless \textbf{ye} the Lord * O ye holy and humble men of \textbf{heart}, bless \textbf{ye} the Lord.
	
	O Ananias, Azarias, and Misael, bless \textbf{ye} the Lord * praise him, and magni\textbf{fy} him for\textbf{ev}er.
	
	Let us bless the Father, and the Son, with the Holy \textbf{Spir}it * let us praise him, and magni\textbf{fy} him for\textbf{eve}r.
	
	Blessed art thou, O Lord, in the firmament of \textbf{hea}ven * and worthy to be praised, and glorious, and highly ex\textbf{al}ted for\textbf{ev}er.
\end{multicols}