\begin{multicols}{2}
	O ye angels of the \textbf{Lord}, bless \textbf{ye} the Lord * O ye \textbf{hea}vens, bless \textbf{ye} the Lord.
	
	O ye waters that be above the \textbf{fir}mament, bless \textbf{ye} the Lord * O all ye powers of the \textbf{Lord}, bless \textbf{ye} the Lord.
	
	O ye sun and \textbf{moon}, bless \textbf{ye} the Lord * O ye stars of \textbf{hea}ven, bless \textbf{ye} the Lord.
	
	O ye showers and \textbf{dew}, bless \textbf{ye} the Lord * O ye winds of \textbf{God}, bless \textbf{ye} the Lord.
	
	O ye fire and \textbf{heat}, bless \textbf{ye} the Lord * O ye winter and \textbf{sum}mer, bless \textbf{ye} the Lord.
	
	O ye dews and \textbf{frosts}, bless \textbf{ye} the Lord * O ye frost and \textbf{cold}, bless \textbf{ye} the Lord.
	
	O ye ice and \textbf{snow}, bless \textbf{ye} the Lord * O ye nights and \textbf{days}, bless \textbf{ye} the Lord.
	
	O ye light and \textbf{dark}ness, bless \textbf{ye} the Lord * O ye lightnings and \textbf{clouds}, bless \textbf{ye} the Lord.
	
	O \textbf{let} the earth \textbf{bless} the Lord * yea, let it praise him, and magni\textbf{fy} him for\textbf{ev}er.
	
	O ye mountains and \textbf{hills}, bless \textbf{ye} the Lord * O all ye green things upon the \textbf{earth}, bless \textbf{ye} the Lord.
	
	O ye \textbf{wells}, bless \textbf{ye} the Lord * O ye seas and \textbf{floods}, bless \textbf{ye} the Lord.
	
	O ye whales, and all that move in the \textbf{wa}ters, bless \textbf{ye} the Lord * O all ye fowls of the \textbf{air}, bless \textbf{ye} the Lord.
	
	O all ye beasts and \textbf{cat}tle, bless \textbf{ye} the Lord * O ye children of \textbf{man}, bless \textbf{ye} the Lord.
	
	O let \textbf{Is}rael \textbf{bless} the Lord * praise him and magni\textbf{fy} him for\textbf{ev}er.
	
	O ye priests of the \textbf{Lord}, bless \textbf{ye} the Lord * O ye servants of the \textbf{Lord}, bless \textbf{ye} the Lord.
	
	O ye spirits and souls of the \textbf{right}eous, bless \textbf{ye} the Lord * O ye holy and humble men of \textbf{heart}, bless \textbf{ye} the Lord.
	
	O Ananias, Azarias, and \textbf{Mi}sael, bless \textbf{ye} the Lord * praise him, and magni\textbf{fy} him for\textbf{ev}er.
	
	Let us bless the Father, and the Son, with the \textbf{Ho}ly \textbf{Spir}it * let us praise him, and magni\textbf{fy} him for\textbf{ev}er.
	
	Blessed art thou, O Lord, in the firma\textbf{ment} of \textbf{hea}ven * and worthy to be praised, and glorious, and highly ex\textbf{al}ted for\textbf{ev}er.
\end{multicols}