\begin{multicols}{2}
	Mine eyes long sore for \textbf{thy} word, \textbf{say}ing: * O when wilt \textbf{thou} comfort me?
	
	For I am become like a \textbf{bot}tle \textbf{in} the smoke * yet do I not for\textbf{get} thy statutes.
	
	How many are the \textbf{days} of thy \textbf{ser}vant? * when wilt thou be avenged of them that \textbf{per}secute me?
	
	The proud have \textbf{dug} pits \textbf{for} me * which are not \textbf{af}ter thy law.
	
	All thy com\textbf{mand}ments \textbf{are} true * they persecute me falsely; \textbf{O} be thou my help.
	
	They had almost made an end of \textbf{me} u\textbf{pon} earth * but I forsook not \textbf{thy} commandments.
	
	O quicken me after thy \textbf{lov}ing-\textbf{kind}ness * and so shall I keep the testi\textbf{mo}nies of thy mouth.
	
	O Lord, thy word endureth for\textbf{ev}er in \textbf{hea}ven * thy truth also remaineth from one generation \textbf{to} another.
	
	Thou hast laid the foundation of the earth and \textbf{it} a\textbf{bid}eth * they continue this day according to thine ordinance, for \textbf{all} things serve thee.
	
	If my delight had \textbf{not} been in \textbf{thy} law * I should have perished \textbf{in} my trouble.
	
	I will never forget \textbf{thy} com\textbf{mand}ments * for with them thou \textbf{hast} quickened me.
	
	I am \textbf{thine}, O save \textbf{thou} me * for I have sought \textbf{thy} commandments.
	
	The ungodly laid wait for me \textbf{to} des\textbf{troy} me * but I will consider thy \textbf{tes}timonies.
	
	I see that all things come \textbf{to} an end * but thy commandment is \textbf{ex}ceedingly broad.
	
	Glory be to the \textbf{Fa}ther, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}