\begin{multicols}{2}
	Mine eyes long sore for thy word, \textbf{say}ing: * O when \textbf{wilt} thou comfort me?
	
	For I am become like a bottle in \textbf{the} smoke * yet do I not for\textbf{get} thy statutes.
	
	How many are the days of thy \textbf{ser}vant? * when wilt thou be avenged of them that \textbf{per}secute me?
	
	The proud have dug pits \textbf{for} me * which are not \textbf{af}ter thy law.
	
	All thy commandments \textbf{are} true * they persecute me falsely; \textbf{O} be thou my help.
	
	They had almost made an end of me u\textbf{pon} earth * but I forsook not \textbf{thy} commandments.
	
	O quicken me after thy loving-\textbf{kind}ness * and so shall I keep the testi\textbf{mo}nies of thy mouth.
	
	O Lord, thy word en\textbf{dur}eth * forev\textbf{er} in heaven.
	
	Thy truth also re\textbf{main}eth * from one generation \textbf{to} another.
	
	Thou hast laid the foundation of the earth and it a\textbf{bi}deth * they continue this day according to thine ordinance, for \textbf{all} things serve thee.
	
	If my delight had not been in \textbf{thy} law * I should have perished \textbf{in} my trouble.
	
	I will never forget thy com\textbf{mand}ments * for with them \textbf{thou} hast quickened me.
	
	I am thine, O save \textbf{thou} me * for I have sought \textbf{thy} commandments.
	
	The ungodly laid wait for me to des\textbf{troy} me * but I will consider thy \textbf{tes}timonies.
	
	I see that all things come to \textbf{an} end * but thy commandment is ex\textbf{cee}dingly broad.
	
	Glory be to the Father, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}