\begin{multicols}{2}
	Mine eyes long \textbf{sore} for thy word, \textbf{say}ing: * O \textbf{when} wilt thou \textbf{com}fort me?
	
	For I am become like a \textbf{bot}tle \textbf{in} the smoke * yet do I not for\textbf{get} thy \textbf{stat}utes.
	
	How many are the \textbf{days} of thy \textbf{ser}vant? * when wilt thou be avenged of them who \textbf{per}se\textbf{cute} me?
	
	The proud have \textbf{dug} pits \textbf{for} me * which are not \textbf{af}ter \textbf{thy} law.
	
	All thy com\textbf{mand}ments \textbf{are} true * they persecute me falsely; \textbf{O} be thou \textbf{my} help.
	
	They had almost made an end of \textbf{me} u\textbf{pon} earth * but I forsook not \textbf{thy} com\textbf{mand}ments.
	
	O quicken me after thy \textbf{lov}ing-\textbf{kind}ness * and so shall I keep the testi\textbf{mo}nies of \textbf{thy} mouth.
	
	O Lord, thy \textbf{word} en\textbf{dur}eth * forev\textbf{er} in \textbf{hea}ven.
	
	Thy truth \textbf{al}so re\textbf{main}eth * from one generation \textbf{to} a\textbf{no}ther.
	
	Thou hast laid the foundation of the earth and \textbf{it} a\textbf{bid}eth * they continue this day according to thine ordinance, for \textbf{all} things \textbf{serve} thee.
	
	If my delight had not \textbf{been} in \textbf{thy} law * I should have perished \textbf{in} my \textbf{trou}ble.
	
	I will never forget \textbf{thy} com\textbf{mand}ments * for with them \textbf{thou} hast \textbf{quick}ened me.
	
	I am \textbf{thine}, O \textbf{save} thou me * for I have sought \textbf{thy} com\textbf{mand}ments.
	
	The ungodly laid wait for me \textbf{to} des\textbf{troy} me * but I will consider thy \textbf{tes}ti\textbf{mo}nies.
	
	I see that all things \textbf{come} to \textbf{an} end * but thy commandment is ex\textbf{ceed}ing\textbf{ly} broad.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}it.
	
	As it was in the beginning is now, and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}