\begin{multicols}{2}
	I will be glad and rejoice \textbf{in} thee * yea, my songs will I make of thy name, \textbf{O} thou Most High.
	
	While mine enemies are dri\textbf{ven} back * they shall fall and perish \textbf{at} thy presence.
	
	For thou hast maintained my right and \textbf{my} cause * thou art set in the \textbf{throne} who judgest right.
	
	Thou hast rebuked the heathen, and destroyed the un\textbf{god}ly * thou hast put out their name fore\textbf{ver} and ever.
	
	O thou enemy, thy destructions are come to an eter\textbf{nal} end * even as the cities which thou hast destroyed shall \textbf{his} memorial end.
	
	But the Lord shall endure for\textbf{ev}er * he hath also prepared his \textbf{seat} for judgment.
	
	For he shall judge the world in right\textbf{eous}ness * and minister true judgment un\textbf{to} the people.
	
	The Lord also will be a defense for the \textbf{op}pressed * even a refuge in due \textbf{time} of trouble.
	
	And they who know thy name will put their trust \textbf{in} thee * for thou, Lord, hast never failed \textbf{them} who seek thee.
	
	O praise the Lord who dwelleth in \textbf{Zi}on * shew the people \textbf{of} his doings.
	
	For when he maketh inquisition for blood, he remember\textbf{eth} them * and forgotteth not the \textbf{com}plaint of the poor.
	
	Have mercy upon me, O Lord, consider the trouble which I suffer of them who \textbf{hate} me * thou who liftest me up \textbf{from} the gates of hell.
	
	That I may shew all thy praises within the ports of the daughter \textbf{Zi}on * I will rejoice in \textbf{thy} salvation.
	
	The heathen are sunk down into the pit that they \textbf{have} made * in the same net which they hid privily is \textbf{their} foot taken.
	
	The Lord is known to execute\textbf{ judg}ment * the ungodly is trapped in the work \textbf{of} his own hands.
	
	The wicked shall be turned in\textbf{to} hell * and all the peo\textbf{ple} who forget God.
	
	For the poor shall not always be for\textbf{got}ten * the patient abiding of the meek shall not per\textbf{ish} forever.
	
	Arise, O Lord, and let not man \textbf{pre}vail * let the heathen \textbf{be} judged in thy sight.
	
	Put them in fear, \textbf{O} Lord * that the heathen may know them\textbf{selves} to be but men.
	
	Why standest thou so far off, \textbf{O} Lord? * and hidest thy face in the \textbf{time} of trouble?
	
	The ungodly for his own lust doth persecute \textbf{the} poor * let them be taken in the crafty wiles that they \textbf{have} imagined.
	
	For the ungodly hath made boast of his own de\textbf{si}re * and speaketh good of the covetous, whom \textbf{God} abhorreth.
	
	The ungodly is so proud, that he careth not \textbf{for} God * neither is \textbf{God} in all his thoughts.
	
	His ways are always \textbf{grie}vous * thy judgments are far above out of his sight, and therefore defieth he \textbf{all} his enemies.
	
	For he hath said in his heart, I shall never be \textbf{cast} down * there shall no harm \textbf{hap}pen unto me.
	
	His mouth is full of cursing, deceit, \textbf{and} fraud * under his tongue is ungodli\textbf{ness} and vanity.
	
	He sitteth lurking in the thievish concerns of \textbf{the} streets * and privily in his lurking dens doth he murder the innocents; his eyes are \textbf{set} against the poor.
	
	He lieth waiting secretly, even as a lion he lurketh in \textbf{his} den * that he \textbf{may} ravish the poor.
	
	He doth ravish \textbf{the} poor * when he getteth \textbf{him} into his net.
	
	He falleth down, and humbleth \textbf{him}self * that the congregation of the poor may fall into the hands \textbf{of} his captains.
	
	He hath said in his heart, God hath for\textbf{got}ten * he hideth away his face, and he will \textbf{ne}ver see it.
	
	Arise, O Lord God, and lift up \textbf{thine} hand * and \textbf{for}get not the poor.
	
	Wherefore should the wicked blas\textbf{pheme} God * while he doth say in his heart, God car\textbf{est} not for it.
	
	Surely thou hast \textbf{seen} it * for thou beholdest un\textbf{god}liness and wrongs.
	
	That thou mayest take the matter into \textbf{thy} hand * the poor committeth himself unto thee, for thou art the helper \textbf{of} the friendless.
	
	Break thou the power of the ungodly and ma\textbf{li}cious * search out his ungodliness, un\textbf{til} thou find none.
	
	The Lord is King forever and \textbf{ev}er * and the heathen are per\textbf{ished} out of the land.
	
	Lord, thou hast heard the desire of \textbf{the} poor * thou preparest their heart, and thine ear hear\textbf{ken}eth thereto.
	
	To help the fatherless and poor unto \textbf{their} right * that the man of the earth be no more exalt\textbf{ed} against them.
	
	Glory be to the Father, and to \textbf{the} Son * and to the \textbf{Ho}ly Spirit.
	
	As it was in the beginning, is now, and ever \textbf{shall} be * world with\textbf{out} end. Amen.
\end{multicols}