I will give thanks unto thee, O Lord, with my whole heart * I will speak of all thy marvelous works.

I will be glad and rejoice in thee * yea, my songs will I make of thy name, O thou Most High.

While mine enemies are driven back * they shall fall and perish at thy presence.

For thou hast maintained my right and my cause * thou art set in the throne who judgest right.

Thou hast rebuked the heathen, and destroyed the ungodly * thou hast put out their name forever and ever.

O thou enemy, thy destructions are come to an eternal end * even as the cities which thou hast destroyed shall his memorial end.

But the Lord shall endure forever * he hath also prepared his seat for judgment.

For he shall judge the world in righteousness * and minister true judgment unto the people.

The Lord also will be a defense for the oppressed * even a refuge in due time of trouble.

And they who know thy name will put their trust in thee * for thou, Lord, hast never failed them who seek thee.

O praise the Lord who dwelleth in Zion * shew the people of his doings.

For when he maketh inquisition for blood, he remembereth them * and forgotteth not the complaint of the poor.

Have mercy upon me, O Lord, consider the trouble which I suffer of them who hate me * thou who liftest me up from the gates of hell.

That I may shew all thy praises within the ports of the daughter Zion * I will rejoice in thy salvation.

The heathen are sunk down into the pit that they have made * in the same net which they hid privily is their foot taken.

The Lord is known to execute judgment * the ungodly is trapped in the work of his own hands.

The wicked shall be turned into hell * and all the people who forget God.

For the poor shall not always be forgotten * the patient abiding of the meek shall not perish forever.

Arise, O Lord, and let not man prevail * let the heathen be judged in thy sight.

Put them in fear, O Lord * that the heathen may know themselves to be but men.

Why standest thou so far off, O Lord? * and hidest thy face in the time of trouble?

The ungodly for his own lust doth persecute the poor * let them be taken in the crafty wiles that they have imagined.

For the ungodly hath made boast of his own desire * and speaketh good of the covetous, whom God abhorreth.

The ungodly is so proud, that he careth not for God * neither is God in all his thoughts.

His ways are always grievous * thy judgments are far above out of his sight, and therefore defieth he all his enemies.

For he hath said in his heart, I shall never be cast down * there shall no harm happen unto me.

His mouth is full of cursing, deceit, and fraud * under his tongue is ungodliness and vanity.

He sitteth lurking in the thievish concerns of the streets * and privily in his lurking dens doth he murder the innocents; his eyes are set against the poor.

He lieth waiting secretly, even as a lion he lurketh in his den * that he may ravish the poor.

He doth ravish the poor * when he getteth him into his net.

He falleth down, and humbleth himself * that the congregation of the poor may fall into the hands of his captains.

He hath said in his heart, God hath forgotten * he hideth away his face, and he will never see it.

Arise, O Lord God, and lift up thine hand * and forget not the poor.

Wherefore should the wicked blaspheme God * while he doth say in his heart, God carest not for it.

Surely thou hast seen it * for thou beholdest ungodliness and wrongs.

That thou mayest take the matter into thy hand * the poor committeth himself unto thee, for thou art the helper of the friendless.

Break thou the power of the ungodly and malicious * search out his ungodliness, until thou find none.

The Lord is King forever and ever * and the heathen are perished out of the land.

Lord, thou hast heard the desire of the poor * thou preparest their heart, and thine ear hearkeneth thereto.

To help the fatherless and poor unto their right * that the man of the earth be no more exalted against them.