\skiplines{-1}\vesectionp{Introduction}\label{vigils:introduction}

	\instruct{The congregation and ministers kneel and quietly make these prayers.}
	
	In the name \red{\GreCross{17}} of the all-holy and undivided Trinity. Amen.
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
	
	Hail Mary, full of grace, the Lord is with thee. Blessed art thou among women and blessed is the fruit of thy womb, Jesus. Holy Mary, Mother of God, pray for us sinners now and at the hour of our death. Amen.
	
	I believe in God the Father almighty, maker of heaven and earth. And in Jesus Christ his only Son our Lord: who was conceived by the Holy Spirit, born of the Virgin Mary, suffered under Pontius Pilate, was crucified, died, and buried. He descended into hell. The third day he rose again from the dead; he ascended into heaven, and sitteth on the right hand of God the Father almighty. From whence he shall come to judge the living and the dead. I believe in the Holy Spirit, the holy catholic Church, the communion of the Saints, the remission of sins, the resurrection of the body, and the life everlasting. Amen.
	
	\instruct{The officiant begins in a low tone while all continue kneeling.}
	
	\gresetinitiallines{0}
	\skiplines{0.75}\gabcsnippet{
		(f3) <sp>v</sp> O(f) Lord,(hv) o(h)pen(h) thou(h) my(g) lips.(hv)
		<sp>r</sp>(::) And(hv) my(h) mouth(h) shall(h) shew(h) forth(h) thy(g) praise.(hv)
	}
	\gresetinitiallines{1}
	
	\instruct{Turn to the \blueribbon for the invitatory.}
	
	\clearpage\instruct{The congregation and minister then stand as the officiant begins in a higher voice.}
	
	\gresetinitiallines{0}
	\skiplines{0.75}\gabcsnippet{(c3) <sp>v</sp> O(f) God,(hv) <sp>+</sp> make(h) speed(iv) to(h) save(g) me.(hv) <sp>r</sp>(::) O(hv) Lord,(h) make(h) haste(h) to(h) help(g) me.(hv)}

	\instruct{The congregation and ministers say this together. Everywhere the three Persons of the Holy Trinity are invoked together, bow and cross yourself.}

	\skiplines{0.75}\gabcsnippet{(c3) <sp>a</sp> Glor(h)y(h) be(h) to(h) the(h) Fa(h)ther,(h) and(h) to(h) the(h) Son,(h) (,) and(h) to(h) the(h) Ho(h)ly(h) Spir(g)it.(h) (:) As(h) it(h) was(h) in(h) the(h) be(h)gin(h)ning,(h) is(h) now(h) and(h) ev(h)er(h) shall(g) be:(h) (,) world(h) with(h)out(h) end.(h) A(g)men.(h) (::) A(h)le(hi)lu(h)ia.(hg)}
	
	\instruct{Turn to the \blueribbon and sing the appointed hymn.}
	
\vesectionp{Nocturns}\label{vigils:nocturn}
	
	\instruct{These rubrics are for each nocturn. Re-place all ribbons at the end of each nocturn.}
	
	\instruct{Turn to the \greenribbon and sing the appointed psalms. Each psalmody is concluded with a versicle.}
	
	\instruct{The congregation and ministers then kneel and make this prayer quietly.}
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
	
	\clearpage\instruct{The officiant then gives the absolution appointed in the collectary. The congregation responds.}
	
	\skiplines{0.75}\gabcsnippet{
		<sp>r</sp> A(gh)men.(h)
	}
	
	\instruct{A lector says before each lesson.}
	
	\skiplines{0.75}\gabcsnippet{
		(c3) <sp>v</sp> Grant,(h) O(h) Lord,(h) thy(h) bles(h)sing.(f)
	}

	\instruct{The officiant then proclaims the appointed blessing from the collectary. The congregation responds.}
	
	\skiplines{0.75}\gabcsnippet{
		<sp>r</sp> Thanks(h) be(h) to(h) God.(h)
	}
	
	\instruct{The lector then reads the appointed lesson from the lectionary. Once finished, turn to the \redribbon and sing the appointed responsory.}
	
\vesectionp{Te Deum}

	\instruct{After the singing of the last responsory, on Sundays and all festivals of the saints regardless of their rank, the Te Deum is sung. But on all other days, skip to pp. \pageref{vigils:conclusion}.}
	
	\vecomment{Canticle of Saints Ambrose and Augustine}
	
	\instruct{The officiant will then proclaim the Gospel. When he has finished, he will intoned the Te decet.}
	
	\skiplines{0.75}\gregorioscore{vigils/te_decet.gabc}
	
\vesectionp{Conclusion}\label{vigils:conclusion}

	\instruct{If Lauds is being prayed together with Vigils, the service of Vigils ends here. Take up now the diurnal.}

	\instruct{If the Te Deum was not sung, all kneel while the cantors turn to the \blueribbon and sing the appointed Kyrie. Then, make this prayer quietly.}
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
	
	\instruct{All stand as the officiant says.}
	
	\skiplines{0.75}\gabcsnippet{
		(c3) <sp>v</sp> O(h) Lord,(h) hear(h) my(f) prayer.(g)
		<sp>r</sp>(::) And(h) let(h) my(h) cry(h) come(h) un(h)to(f) thee.(f)
		(::) Let(h) us(g) pray.(h)
	}

	\instruct{The officiant then proclaims the collect. The congregation responds.}
	
	\skiplines{0.75}\gabcsnippet{
		(c3) <sp>r</sp> A(gh)men.(h)
	}

	\gregorioscore{common/conclusion.gabc}
	
	\instruct{The congregation and ministers kneel and make quietly this prayer.}
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.