\skiplines{-1}\vesectionp{In the First Nocturn}
	
	\veant{1}{iii. iv}
	\gregorioscore{ant/servite_domino.gabc}
	
	\greannotation{\veformat{Ps. 1}}
	\greannotation{\veformat{iii. iv.}}
	\skiplines{1}\gabcsnippet{
		(c3) Bles(e)sed(f:?) is(hr) the() man() who() hath() not() walked() in() the() counsel() of() the() ungodly,() nor() stood() in() the(h) <b>way</b>(i) of(hr) <b>sin</b>(g)ners(hr) <sp>*</sp>(:) and(hr) hath() not() sat() in() the() chair(h) <b>of</b>(f) pesti(hr)lence.(g)
	}
	
	\input{psalter/1/3}
	
	\greannotation{\veformat{Ps. 2}}
	\greannotation{\veformat{iii. iv.}}
	\clearpage\skiplines{0}\gabcsnippet{
		(c3) Why(e) do(f:?) the(hr) hea--()then(h) <b>rage</b>(i) to(hr)<b>ge</b>(g)ther(hr) <sp>*</sp>(:) and(hr) the() people() ima--()gine(h) <b>a</b>(f) vain(hr) thing?(g)
	}
	
	\input{psalter/2/3}
	
	\greannotation{\veformat{Ps. 3}}
	\greannotation{\veformat{iii. iv.}}
	\skiplines{1}\gabcsnippet{
		(c3) Lord,(e) how(f:?) multiplied(hr) are(h) <b>they</b>(i) who(hr) <b>trou</b>(g)ble(hr) me() <sp>*</sp>(:) many(hr) are() they() who() rise(h) <b>a</b>(f)gainst(hr) me.(g)
	}
	
	\input{psalter/3/3}
	
	\greannotation{\veformat{Ps. 6}}
	\greannotation{\veformat{iii. iv.}}
	\skiplines{1}\gabcsnippet{
		(c3) O(e) Lord,(f:?) rebuke(hr) me() not() in() thine(h) <b>in</b>(i)dig(hr)<b>na</b>(g)tion(hr) <sp>*</sp>(:) neither(hr) chastise() me() in() thy(h) <b>dis</b>(f)plea(hr)sure.(g)
	}
	
	\input{psalter/6/3}
	
	\repant{ant/servite_domino.gabc}
	
	
	\veant{2}{i. iii.}
	\skiplines{1}\gregorioscore{ant/domine_deus_meus.gabc}
	
	\greannotation{\veformat{Ps. 7}}
	\greannotation{\veformat{i. iii.}}
	\skiplines{1}\gabcsnippet{
		(c4) O(f) Lord(g:?) my(hr) God,() in() thee() have() I() put(h) <b>my</b>(g) trust(h) <sp>*</sp>(:) save(hr) me() from() all() them() who() persecute() me,(h) <b>and</b>(g) de(f)li(gr)ver() me.(ghg)
	}
	
	\input{psalter/7/1}
	
	\greannotation{\veformat{Ps. 8}}
	\greannotation{\veformat{i. iii.}}
	\skiplines{1}\gabcsnippet{
		(c4) O(f) Lord(g:?) our(hr) Lord,() how() wonderful() is() thy() Name() in() all(h) <b>the</b>(g) world(h) <sp>*</sp>(:) thou(hr) who() hast() set() thy() glory() a(h)<b>bove</b>(g) the(f) hea(gr)vens.(ghg)
	}
	
	\input{psalter/8/1}
	
	\greannotation{\veformat{Ps. 9}}
	\greannotation{\veformat{i. iii.}}
	\skiplines{1}\gabcsnippet{
		(c4) I(f) will(g:?) give(hr) thanks() unto() thee,() O() Lord,() with() my() <b>whole</b>(g) heart(h) <sp>*</sp>(:) I(hr) will speak of all thy(h) <b>mar</b>(g)ve(f)lous(gr) works.(ghg)
	}
	
	\input{psalter/9/1}
	
	\greannotation{\veformat{Ps. 10}}
	\greannotation{\veformat{i. iii.}}
	\skiplines{1}\gabcsnippet{
		(c4) In(f) the(g:?) Lord(hr) I() put(h) <b>my</b>(g) trust(h) <sp>*</sp>(:) how(hr) say() ye() then() to() my() soul,() that() she() should() flee() as() a(h) <b>bird</b>(g) un(f)to(gr) the() hill?(ghg)
	}
	
	\input{psalter/10/1}
	
	\repant{ant/domine_deus_meus.gabc}
	
	
	\veant{3}{viii. i}
	\gregorioscore{ant/respice_et_exaudi_me.gabc}
	
	\greannotation{\veformat{Ps. 11}}
	\greannotation{\veformat{viii. i.}}
	\skiplines{1}\gabcsnippet{
		(c4) Help(g) me,(h:?) O(jr) Lord,() for() a() godly() man() there(j) <b>is</b>(k) no(jr) more() <sp>*</sp>(:) for(jr) truth() is() dimin--()ished(j) <b>from</b>(i) the(j) sons(h) of(gr) men.()
	}
	
	\input{psalter/11/8}
	
	\greannotation{\veformat{Ps. 12}}
	\greannotation{\veformat{viii. i.}}
	\skiplines{1}\gabcsnippet{
		(c4) How(g) long(h:?) wilt(jr) thou() utterly() for--()get(j) <b>me,</b>(k) O(jr) Lord?() <sp>*</sp>(:) how(jr) long() wilt() thou(j) <b>hide</b>(i) thy(j) face(h) from(gr) me?()
	}
	
	\input{psalter/12/8}
	
	\greannotation{\veformat{Ps. 13}}
	\greannotation{\veformat{viii. i.}}
	\skiplines{1}\gabcsnippet{
		(c4) The(g) fool(h:?) hath(jr) said(j) <b>in</b>(k) his(jr) heart() <sp>*</sp>(:) (jr) <b>There</b>(i) is(j) no(h) God.(gr)
	}
	
	\input{psalter/13/8}
	
	\greannotation{\veformat{Ps. 14}}
	\greannotation{\veformat{viii. i.}}
	\skiplines{1}\gabcsnippet{
		(c4) Lord,(g) who(:?) shall(jr) dwell() in() thy() tab--()er(j)<b>na</b>(k)cle?(jr) <sp>*</sp>(:) or(jr) who() shall() rest() upon() thy(j) <b>ho</b>(i)ly(j) moun(h)tain?(gr)
	}
	
	\input{psalter/14/8}
	
	\repant{ant/respice_et_exaudi_me.gabc}
	
	\gresetinitiallines{0}
	\skiplines{1}\gabcsnippet{
		(c3) <sp>v</sp> I(h) have(h) thought(h) upon(h) thy(h) Name,(h) O(h) Lord,(h) in(h) the(h) night(h) sea(f)son.(g)
		<sp>r</sp>(::) And(h) have(h) kept(h) thy(f) law.(f)
	}
	\gresetinitiallines{1}
	
	\instruct{Move the \greenribbon to this page, and turn to the \whiteribbon for the lessons.}
	
\vesectionp{In the Second Nocturn}

	\veant{4}{iii. iv.}
	\gregorioscore{ant/bonorum_meorum.gabc}
	
	\greannotation{\veformat{Ps. 15}}
	\greannotation{\veformat{iii. iv.}}
	\skiplines{1}\gabcsnippet{
		(c3) Pre(hr)<b>serve</b>(i) me,(hr) <b>O</b>(g) God(hr) <sp>*</sp>(:) for(hr) in() thee() have(h) <b>I</b>(f) put(hr) my() trust.(g)
	}
	
	\input{psalter/15/3}
	
	\repant{ant/bonorum_meorum.gabc}
	
	
	\veant{5}{vii. ii}
	\skiplines{1}\gregorioscore{ant/inclina_domine.gabc}
	
	\greannotation{\veformat{Ps. 16}}
	\greannotation{\veformat{vii. ii.}}
	\skiplines{1}\gabcsnippet{
		(c3) Hear(g)ken,(h:?) O(ir) Lord,() unto() my() righteousness() and() con(i)<b>si</b>(k)der(jr) <b>my</b>(i) complaint(jr) <sp>*</sp>(:) hear(ir) my() prayer() that() goeth() not(i) <b>out</b>(j) of(ir) <b>feigned</b>(hr) lips.(gh)
	}

	\input{psalter/16/7}
	
	\repant{ant/inclina_domine.gabc}
	
	
	\veant{6}{viii. i.}
	\skiplines{1}\gregorioscore{ant/dominus_firmamentum.gabc}
	
	\greannotation{\veformat{Ps. 17}}
	\greannotation{\veformat{viii. i.}}
	
	\skiplines{1}\gabcsnippet{
		(c3) I(e) will(f:?) love(hr) thee,() O() Lord,() my ()strength;() the() Lord() is() my() firmament,() and(h) <b>my</b>(i) defense(hr) <sp>*</sp>(:) my(hr) Savior,() my() God,() and() might,() in() whom() will() I() trust:() my() buckler,() the() horn() of() my() salva--()tion,(h) <b>and</b>(g) my(h) re(f)fuge.(er)
	}
	
	\input{psalter/17/8}
	
	\repant{ant/dominus_firmamentum.gabc}
	
	
	\gresetinitiallines{0}
	\skiplines{1}\gabcsnippet{
		(c3) <sp>v</sp> At(h) mid(h)night(h) will(h) I(h) rise(h) to(h) give(h) thanks(h) un(h)to(f) thee.(g)
		<sp>r</sp>(::) Be(h)cause(h) of(h) thy(h) right(h)eous(h) judg(h)ments.(f)
	}
	\gresetinitiallines{1}
	
	\instruct{Move the \greenribbon to this page, and turn to the \whiteribbon for the lessons.}
	
\vesection{In the Third Nocturn}

	\veant{7}{iv. i}
	\gregorioscore{ant/preceptum_domini.gabc}
	
	\greannotation{\veformat{Ps. 18}}
	\greannotation{\veformat{vi. i.}}
	\skiplines{1}\gabcsnippet{
		(c4) The(h) hea(g:?)vens(hr) declare() the(g) <b>glo</b>(h)ry(j) of(i) God(hr) <sp>*</sp>(:) and(hr) the() firmament() shew(h)<b>eth</b>(g) the(h) work(ih) of(gvFE) his(er) hands.()
	}
	
	\input{psalter/18/4}
	
	\repant{ant/preceptum_domini.gabc}
	
	
	\veant{8}{iv. viii}
	\skiplines{1}\gregorioscore{ant/impleat_dominus.gabc}
	
	\greannotation{\veformat{Ps. 19}}
	\greannotation{\veformat{iv. viii.}}
	\skiplines{1}\gabcsnippet{
		(c4) The(h) Lord(g:?) hear(hr) thee() in() the(h) <b>day</b>(g) of(h) trou(i)ble(hr) <sp>*</sp>(:) the(hr) Name() of() the() God() of() Jacob() de(h)<b>fend</b>(gi) thee.(hr)
	}
	
	\input{psalter/19/4-8}
	
	\repant{ant/impleat_dominus.gabc}
	
	
	\veant{9}{viii. i}
	\skiplines{1}\gregorioscore{ant/domine_in_virtute.gabc}
	
	\greannotation{\veformat{Ps. 20}}
	\greannotation{\veformat{viii. i.}}
	\skiplines{1}\gabcsnippet{
		(c4) The(g) King(h:?) shall(jr) rejoice() in() thy(j) <b>strength</b>,(k) O(jr) Lord() <sp>*</sp>(:) exceedingly(jr) glad() shall() he() be() of(j) <b>thy</b>(i) sal(j)va(h)tion.(gr)
	}
	
	\input{psalter/20/8}
	
	\repant{ant/domine_in_virtute.gabc}
	
	\gresetinitiallines{0}
	\gabcsnippet{
		(c3) <sp>v</sp> Be(h) thou(h) ex(h)al(h)ted,(h) O(h) Lord,(h) in(h) thine(h) own(f) strength.(g)
		<sp>r</sp>(::) We(h) will(h) sing,(h) and(h) praise(h) thy(h) pow(h)er.(f)
	}
	\gresetinitiallines{1}
	
	\instruct{Turn to the \whiteribbon for the lessons.}