\begin{multicols}{2}
	O ye angels of the \textbf{Lord}, bless ye the Lord * O ye \textbf{hea}vens, bless ye the Lord.
	
	O ye waters that be above the firma\textbf{ment}, bless ye the Lord * O all ye powers of \textbf{the} Lord, bless ye the Lord.
	
	O ye sun and \textbf{moon}, bless ye the Lord * O ye stars of \textbf{hea}ven, bless ye the Lord.
	
	O ye showers and \textbf{dew}, bless ye the Lord * O ye winds \textbf{of} God, bless ye the Lord.
	
	O ye fire and \textbf{heat}, bless ye the Lord * O ye winter and \textbf{sum}mer, bless ye the Lord.
	
	O ye dews and \textbf{frosts}, bless ye the Lord * O ye frost \textbf{and} cold, bless ye the Lord.
	
	O ye ice and \textbf{snow}, bless ye the Lord * O ye nights \textbf{and} days, bless ye the Lord.
	
	O ye light and dark\textbf{ness}, bless ye the Lord * O ye lightnings \textbf{and} clouds, bless ye the Lord.
	
	O let \textbf{the} earth bless the Lord * yea, let it praise him, and magni\textbf{fy} him forever.
	
	O ye mountains and \textbf{hills}, bless ye the Lord * O all ye green things upon \textbf{the} earth, bless ye the Lord.
	
	O ye \textbf{wells}, bless ye the Lord * O ye seas \textbf{and} floods, bless ye the Lord.
	
	O ye whales, and all that move in the wa\textbf{ters}, bless ye the Lord * O all ye fowls of \textbf{the} air, bless ye the Lord.
	
	O all ye beasts and cat\textbf{tle}, bless ye the Lord * O ye children \textbf{of} man, bless ye the Lord.
	
	O let Is\textbf{ra}el bless the Lord * praise him and magni\textbf{fy} him forever.
	
	O ye priests of the \textbf{Lord}, bless ye the Lord * O ye servants of \textbf{the} Lord, bless ye the Lord.
	
	O ye spirits and souls of the righ\textbf{teous}, bless ye the Lord * O ye holy and humble men \textbf{of} heart, bless ye the Lord.
	
	O Ananias, Azarias, and Misa\textbf{el}, bless ye the Lord * praise him, and magni\textbf{fy} him forever.
	
	Let us bless the Father, and the Son, with the \textbf{Ho}ly Spirit * let us praise him, and magni\textbf{fy} him forever.
	
	Blessed art thou, O Lord, in the firma\textbf{ment} of heaven * and worthy to be praised, and glorious, and highly ex\textbf{al}ted forever.
\end{multicols}