\begin{multicols}{2}
	His seed shall be \textbf{migh}ty u\textbf{pon} earth * the generation of the faithful \textbf{shall} be \textbf{bles}sed.
	
	Riches and plenteousness shall \textbf{be} in \textbf{his} house * and his righteousness en\textbf{dur}eth for\textbf{ev}er.
	
	Unto the godly there ariseth up \textbf{light} in the \textbf{dark}ness * he is merciful, \textbf{lov}ing, and \textbf{right}eous.
	
	A good man is merci\textbf{ful}, and \textbf{lend}eth * and will guide his \textbf{words} with dis\textbf{cre}tion.
	
	For he shall \textbf{ne}ver \textbf{be} moved * and the righteous shall be had in ever\textbf{last}ing re\textbf{mem}brance.
	
	He will not be afraid of any \textbf{ev}il \textbf{ti}dings * for his heart standeth fast, and be\textbf{liev}eth \textbf{in} the Lord.
	
	His heart is e\textbf{stab}lished, and will \textbf{not} shrink * until he sees his desire u\textbf{pon} his \textbf{en}emies.
	
	He hath dispersed abroad, and \textbf{giv}en \textbf{to} the poor * and his righteousness remaineth forever; his horn shall be ex\textbf{al}ted with \textbf{hon}or.
	
	The ungodly shall see it, and \textbf{it} shall \textbf{grieve} him * he shall gnash with his teeth, and consume away; the desire of the un\textbf{god}ly shall \textbf{per}ish.
	
	Glory be to the \textbf{Fa}ther, and \textbf{to} the Son * and to the \textbf{Ho}ly \textbf{Spir}it.
	
	As it was in the beginning, is now, and \textbf{ev}er \textbf{shall} be * world with\textbf{out} end. \textbf{A}men.
\end{multicols}